### 2019-02-01 Seneca.tex
moving to new repo

\begin{figure}[t] \centering 
\includegraphics[scale=0.08]{Seneca}
\caption{The architecture of Seneca. 
User specifies hyperparameter options in the configuration file and provides lambda function. Seneca automatically package, deploy and optimize lambda function on AWS before completing grid search process and selecting best hyperparameter setting.
\label{fig:seneca}}
% \vspace{-0.2in}
\end{figure}

To facilitate model optimization on serverless architecture, we have developed a cloud service, namely Seneca. The Seneca service pipeline consists of

### 2019-02-01 abstract.tex
moving to new repo

The involvement of manual operations and domain expertise makes traditional model optimization process expensive, time-consuming and not guaranteed the optimal solution. The emergence of serverless computing offers the potential to optimize models in an auto-scaling and micro-billing fashion. In this paper, we present Seneca -- a framework for machine learning model optimization on serverless computing platform. Its automated pipeline consists of packaging, deployment, serverless function optimization and hyperparameter tuning, which provides a cost-effective, high-performing and reliable model optimization service. We evaluate Seneca by performance, cost and latency analysis on multiple regression and classification applications. The result demonstrates Seneca streamlines model deployment and optimization in agile and economical fashion.

### 2019-02-01 intro.tex
moving to new repo

Serverless~\cite{ref:serverless} computing is a rising function-based (also known as Funtions-as-a-Service~\cite{ref:faas}) programming and deployment paradigm on top of cloud infrastructure, in which programmers manifest business logic without concerning provisioning servers by modular functions that are triggered by incoming events and return computation results in serialized format like XML or JSON. Such events include HTTP requests from clients, possibly proxied by API Gateway, or communications between cloud services based on heterogeneous protocols. Depending on the supported runtimes from cloud vendors, functions could be written in various high-level languages (i.e. NodeJS, Python, Java, etc.) and take advantage of serverless SDK to interact with other cloud services. Until recently, the leading serverless platform, Amazon Web Services(AWS) Lambda, expands language support by custom runtime~\cite{ref:customruntime} where software engineers can implement functions by any programming languages.

Primarily, there are four evolutionary advantages that serverless architecture brings to cloud computing. First and foremost, it raises the abstraction layer from virtual machines to function containers~\cite{ref:container} that abstracts away the responsibilities of infrastructure management from DevOps~\cite{ref:devops} personnel to the cloud provider, in terms of scaling, patching, provisioning, error-handling and terminating underlying bare metal servers or clusters. Such shift allows more agile development life cycle and more product-oriented programming iteration. Secondly, the event-driven and paralleled container runtime of serverless function provides more fine-grained computational resource isolation and usage. Hence, serverless architecture makes cloud operation more secure and energy-efficient compared to traditional virtual machine instance runtime. Thirdly, serverless architecture decomposes monolithic application code base even further from microservices~\cite{ref:microservices} into granular functions, which are easier to be created, maintained and refactored by team or individual programmer. Furthermore, Function-as-a-Service applications could be autoscaled independently with respect to modular functions depending on the volume of request. This capability also contributes to the energy efficiency and eliminating throttling bottlenecks. Lastly, serverless computing provides "Pay-per-execution" pricing model~\cite{ref:pricing}. In a real world case study~\cite{ref:serverless_econ}, the server operational cost on serverless platform could be reduced dramatically, given a relatively lower amount of Transactions Per Second (TPS). Based on these four advantages, serverless architecture appropriately serves mid-size stateless application under certain TPS threshold better than virtual machine based clusters. According to these merits, the stateless, event-driven and embarrassingly parallel tasks are potentially cost-effective with lower latency by running on serverless framework.

### 2019-02-01 results.tex
moving to new repo

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|} \hline
\textbf{Application}& \textbf{Description}\\
\hline
Prophet& Time series decomposition and prediction\\ 
\hline
Multi-Regression& Multiple linear regression/prediction of time series\\
\hline
XGBoost& Regression and classification by gradient boosting\\
\hline
SVC & Classification based on support vector machine\\
\hline
Neural Network& Classification by layered artificial neural network\\
\hline
\end{tabular}}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
\vspace{-0.2in}
\end{table}

In this section,
we evaluate Seneca in terms of performance, monetary cost, and hyperparameter tuning time (latency), 
using machine learning applications that we ported to Seneca (i.e. that we implemented
as lambda functions). 
We first overview these applications and our empirical methodology. 
We then present our experimental results.

\subsection{Benchmark Applications and Training/Testing  Datasets}
The machine learning applications that we use to evaluate Seneca 
are shown in Table~\ref{tab:bmarks}, each with 
a brief description.
Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
%logorithm
of Payton Manning's wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
The dataset exhibits both seasonality and a holiday effect (e.g. around the super bowl games). 
We use the first 6 years as the training set and the last 2 years as the testing set.
We use a cross-validation horizon (sliding window) of 1-year, 
and a period (sliding pace) 
of 180 days.  As such, Seneca performs three cross-validations for each 2-year testing range.

%%The hyperparameters that Prophet expects are 
%%\textcolor{blue}{Describe what these are in a couple of sentences.}
%%In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
%%the application or that are defined by the application developer) for each application.  
%%The default parameters for this application are
%%\textcolor{blue}{Describe them here.}
%%The application computes mean square error of
%%\textcolor{blue}{finish this here.}

Prophet expects multiple hyperparameters: \textit{growth} specifies linear or logistic trend model growth; \textit{prior scale} indicates the strength of the 
sparse prior probability~\cite{ref:sparse_prior}. 
There are three prior scale hyperparameters for change point, holidays, and seasonality. 
Since Prophet uses a Fourier sum to estimate seasonality, 
the \textit{fourier order} is the number of terms in the partial Fourier 
sum. \textit{Seasonality mode} indicates that the effect of seasonality is either 
multiplicative or additive. Finally, the width of uncertainty intervals 
can be set using the hyperparameter \textit{interval width}.

% \textcolor{blue}{Describe what these are in a couple of sentences.}
In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for this Prophet are listed in the table~\ref{tab:prophet_para}. For each cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and $n$ is the number of data points. The application returns the average MSE across cross validations. 
%Using a the model trained by default parameter setting, this average MSE metric is 0.284.

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{
\begin{tabular}{|l|l|l|} 
\hline
\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
\hline
grow & linear & [linear, logistic] \\
\hline
changepoint prior scale & 0.05 & [0.05, 0.5] \\
\hline
holidays prior scale & 10 & [1, 5, 10] \\
\hline
seasonality prior scale & 0.5 & [0.1, 0.5] \\
\hline
fourier order & 10 & [5, 10, 15, 20] \\
\hline
seasonality mode & additive & [additive, multiplicative] \\
\hline
interval width & 0.8 & [0.5, 0.8] \\
\hline
\end{tabular}}
\caption{Default hyperparameters for Prophet. The default value and tuning options are listed. 
\label{tab:prophet_para}}
\vspace{-0.2in}
\end{table}

Multi-Regression is a regression application 
developed by the authors of 
an IoT project~\cite{iot-cpu} that
predicts outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures (e.g. for use in 
precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

A hyperparameter configuration for this application is a subset of input SBC time series.
Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
For this application,
we assume the default parameterization is the set of all $N$ input time series (8 in this case).
The test dataset for this application is a time series of the outdoor temperature (ground truth) 
over the same period.  The application makes predictions for each of these outdoor temperatures
using the model constructed from the training set
and computes the mean square error across predicted and ground truth value pairs.

XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
performs both regression and classification. We consider it a regression application and
a classification application in this evaluation.  
Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
Neural network~\cite{ref:neural_network} is a machine learning framework that learns 
and make decisions from patterns in an input dataset. For this application, 
we use a feedforward multilayer perceptron model~\cite{ref:feedforward_nn} 
for the classification task.

For these applications (XGBoost, SVC, and Neural Network), 
we use a labeled dataset for training, testing, and evaluation from a separate
project (name and citation ommitted for blind review).
The dataset contains
measurements of individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) 
taken by a fruit sorting and grading device (using a large number of sensors).  
The measurements (i.e. features)
include size, shape, weight, color, diameter, flatness, among other characteristics,
for each fruit.  The label indicates which field each fruit was harvested from.  
The applications train a model on a random subset of the data.  
They then use this model to predict the field
from which each fruit originates. They compute classification accuracy score as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the prediction class, $Y_i$ is the true class, $n$ is the number of samples and 1(x) is the indicator function. XGBoost also computes MSE for its regression task on the same datasets. The dataset has been filtered to remove correlated features (those with an absolute value of the Pearson correlation coefficient greater than 0.8) and outliers. 
%The dataset has also been balanced by downsampling one target whose number 
%greatly exceeds other ones. 
The resulting dataset contains 33926 rows (individual fruit) distributed evenly across 5 targets, and each row has 18 features.

%The dataset is from a Compac packline machine~\cite{ref:compac} that sorts and grades fruit using a large number of 
%measurements (i.e. feature measurements including size, shape, weight, color, diameter, flatness, etc.).  The labels identify the field from which fruit was harvested.
%The dataset is filtered to remove correlated features (those with an absolute value of the Pearson correlation 
%coefficient greater than 0.8).

%Seneca downloads the dataset from AWS S3 for each function invocation.
%It then randomly indexes the data set and splits it into two.  
For these applications (XGBoost, SVC, and Neural Network), 
Seneca splits the dataset and uses 80\% and 20\% for testing.
For Neural Network and XGBoost, we also consider other splits
that requires less data for training: \textcolor{blue}{list them here once we finish
the additional results}. 
%This setup also means that each Seneca function
%considers a different training and testing set during hyperparameter tuning.

%todo in the future -- for a complete tuning, use the same testing and training sets
%run this multiple times (for the same test/train datasets) and report the average and stdev in the latency (and memory?) results.
%todo in the future -- repeat the above using different test/train datasets, but keep 
%them the same for all functions in a single tuning run.  Compare the MSE/accuracy and
%the configurations that are selected, analyze how they change (if they do)

\subsection{Empirical Methodology}
To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
For tuning performance, we use mean squared error (MSE) for regression tasks 
and percentage accuracy for
classification tasks. The default configuration that we 
consider for each application is described above.
We report results for the default, the best (Seneca's recommendation), 
and the worst performing configurations.  Seneca considers all possible combinations 
of the hyperparameter settings specified in the configuration, uses them
to train, test, and evaluate models for each. 
The default results represents a configuration that a novice or first time 
user might employ when using these applications
as a "black box".  The worst performing scenario shows how bad the results can be
when parameters are poorly tuned.  Finally, the best configuration 
is the one that results from tuning they hyperparameters for the test/train split
that Seneca considers.

We deploy Seneca on Amazon Web Services (AWS) Lambda and extract
execution time and memory use from AWS CloudWatch logs.  
We then compute monetary cost
using the AWS Lambda pricing model~\cite{ref:pricing}.
%awslambdapricing: https://aws.amazon.com/lambda/pricing/
Each function downloads the training and testing dataset 
of the application from AWS Simple Storage Service (S3) upon function invocation. 
We do not consider the cost of dataset storage in our cost computations (it is very small).

We also experiment with different memory configurations for Seneca functions in AWS Lambda.  
We evaluate
the performance and cost of allocating the maximum memory for each and for automatically optimizing 
memory use using Seneca. We assume that all combinations hyperparameter settings use the 
same maximum amount of memory across functions; we 
have verified that this assumption holds for the applications and datasets that
we consider herein.
We plan to consider applications for which hyperparameter settings require 
different maximum amounts of memory as part of future work.

\subsection{Tuning Performance}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
& Prophet & Multi-Regression & XGBoost\\
\hline
\# of Combinations & 384 & 255 & 768\\
\hline
\hline
Default MSE & 0.284 & 11.446 & 0.119 \\
\hline
Worst MSE & 1.266 & 43.752 & 8.069 \\
\hline
Best MSE (Seneca) & 0.220 & 9.621 & 0.049 \\
\hline
%percent difference between default and best 26.07%, 15.94%, 67.30%
%percent difference between worst and best 82.63%, 78.01%, 95.52%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.4]{mse}
\end{tabular}
\caption{Combination count and MSE for the default, 
best (Seneca's recommendation), 
and worst hyperparameter configurations for the three regression applications. 
For the MSE  values (rows 3-5), lower is better.
\label{tab:mse}}
\end{table}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{box_plot_mse}
\caption{The box plot of MSE from the three regression applications 
across the hyperparameter tuning search space. 
The red notch shows the MSE from the default configuration. 
The colored diamonds are outliers beyond two interquartile ranges. 
Lower MSE values are better.
\label{fig:box_plot_mse}}
\vspace{-0.2in}
\end{figure}

We first evaluate Seneca using the three regression applications: 
Prophet, Multi-Regression, and XGBoost (regression task). 
Table ~\ref{tab:mse} shows the size of the hyperparameter search space (number of configurations
considered) and the mean squared error (MSE)
for each of the regression applications that we consider (columns 3-5).
The first row of data is 
 the number of hyperparameter configurations that Seneca considers in search space of each. 
The last three rows show the MSE for the default, worst, and best performing 
hyperparameter configuation reported by Seneca (lower is better).  
Seneca reduces MSE by 26\%, 16\%, and 67\%, for Prophet, Multi-Regression, and XGBoost,
respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 96\%, respectively.

Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better)
for these applications 
for the entire hyperparameter 
search space. The central rectangle covers the interquartile range (IQR), 
which is defined as the range of data 
points from first quartile to third quartile (Q3 - Q1). 
The upper whisker extends to the last datum less 
than \texttt{$(Q3 + 2 * IQR)$} and the lower whisker extends to the first datum greater 
than \texttt{$(Q1 - 2 * IQR)$}. The data points beyond the whiskers are considered outliers 
and are plotted as colored diamonds. The red notch identifies the MSE that results from training 
the model using the default settings of hyperparameter. 
The difference between red notch of lowest data 
point is the improvement brought about by the use of Seneca. 
The red notch marks the MSE of the default hyperparameterization.
Each is located near the 
From the location of red notch, we can see the MSE metrics 
first quartile value indicating that there is significant 
potential room for improvement in MSE. The box plot also illustrates 
that the best MSE of Prophet and multivariate regression are among the outliers, 
indicating that a comprehensive search is critical to finding the best configurations. 
%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}

%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance %%%%%%%%%%%%%%%%%%%%%%%%%
We next empirically evaluate the tuning performance of Seneca for the three
classification applications: XGBoost (classification), SVC, and Neural Network.
Figure~\ref{fig:accuracy} presents the accuracy percentage (higher is better) 
reported by each application (3 left-most columns) 
for the default, worst, and best hyperparameter tuning 
configurations (data rows 2-4) reported by Seneca.  
The first row of the table
reports the number of configurations that Seneca considers in its search space.
Seneca increases accuracy by 84\%, 84\%, and 80\%, for XGBoost (classification), 
SVC, and Neural Network applications,
respectively, for the datasets and training methodologies that we consider.
Verses the worst case, Seneca improves accuracy by 86\%, 86\%, and 85\%, respectively.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
& XGBoost & SVC & Neural Network\\
\hline
\# of Combinations & 768 & 512 & 432\\
\hline
\hline
Default MSE&2.42\%&3.93\%&6.51\%\\
\hline
Worst MSE&0.00\%&2.04\%&1.72\%\\
\hline
Best MSE (Seneca) &86.07\%&87.76\%&86.34\%\\
\hline
%percent difference between default and best 83.65%, 83.84%, 79.83%
%percent difference between worst and best 86.07%, 85.73%, 84.63%
%\begin{figure}[t] \centering 
%\includegraphics[scale=0.38]{accuracy}
\end{tabular}
\caption{Combination count and accuracy reported for the 
default, best (Seneca's recommendation), and worst hyperparameter configurations for 
the three classification applications.  
For the accuracy  values (rows 3-5), higher is better.
\label{fig:accuracy}}
%\vspace{-0.2in}
%\end{figure}
\end{table}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{box_plot_accuracy}
\caption{The box plot of accuracy metric 
from the classification applications for the entire hyperparameter tuning search space. 
The red notch indicates the accuracy metric from the trained model using the default configuration. 
The colorful diamonds are outliers beyond two interquartile ranges. Higher accuracy values are better.
\label{fig:box_plot_accuracy}}
% \vspace{-0.2in}
\end{figure}

Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
for the entire hyperparameter search space for each classification
application.  The central rectangle covers from first quartile to third quartile 
(Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. 
The red notch indicates the accuracy metric from the model trained using the default 
settings and colored diamonds show outliers beyond the whiskers.
For both types of applications (regression and classification), Seneca significantly
improves tuning performance over the default and worst case configurations for the 
datasets and training methodologies that we consider.

\subsection{Cost Analysis}

We next analyze the monetary cost introduced by Seneca. 
We consider two scenarios for its implementation.
First, we configure each lambda function to use the maximum amount
of memory allowed by AWS Lambda (3008 MB).  Second, we employ Seneca's memory optimization,
which automatically detects and configures the amount of memory needed by each function.
Because memory impacts both cost and execution time (total latency of Seneca 
hyperparameter tuning), we present empirically evaluate both 
in this subsection.  For each, we only include XGBoost once since its 
performance profile is the same
regardless of whether we are using regression or classification.

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 13 & 7 & 3 & 15 & 14 \\
\hline
Cost of Tuning (\$) &0.406 & 0.220 & 0.075 & 0.213 & 0.161 \\
\hline
\end{tabular}
\caption{Monetary cost of using Seneca for hyperparameter 
tuning when configured to use the maximum amount of memory(3008MB) 
possible for each function invocation. 
\label{tab:cost_max_memory}}
\vspace{-0.2in}
\end{table}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& Prophet & MR & XGBoost & SVC & NN\\
\hline
\hline
Exec time (minutes)& 33 & 17 & 9 & 17 & 14 \\
\hline
Cost of Tuning (\$) &0.325 & 0.120 & 0.043 & 0.141 & 0.130 \\
\hline
Cost of optimization (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
\hline
Total Cost (\$) &0.358 & 0.134 & 0.045 & 0.151 & 0.138 \\
\hline
\end{tabular}
\caption{Seneca  Memory  Optimization:  The  monetary  cost  of 
using Seneca for hyperparameter tuning when the amount of memory  
used  for  each  function  invocation  is  automatically
inferred and set by Seneca.
\label{tab:cost_optimized}}
\vspace{-0.2in}
\end{table}

Tables~\ref{tab:cost_max_memory} and~\ref{tab:cost_optimized} show the results with and without 
the Seneca memory optimization, respectively. In both tables, the five columns identify the 
benchmark applications and the first row is the total execution time in minutes for 
Seneca's hyperparameter tuning for the corresponding application.  
The second row shows the total monetary cost of tuning each application using Seneca;
for Table~\ref{tab:cost_max_memory} (unoptimized) this is the Total Cost of using Seneca.

To perform the memory optimization (Table~\ref{tab:cost_optimized}), 
Seneca requires additional runs of the application
and as such, introduces additional cost.  This cost is shown for each application in 
the third row.  Total Cost is the sum of rows 2 and 3 in this table and is the 
total cost of using Seneca with its memory optimization.

By reducing the amount of memory used, Seneca reduces total cost.  
However by doing so, Seneca also 
increases the total time it requires to perform hyperparameter tuning (Exec time in minutes 
in row 1 of both tables) for some applications.  
On average, the Seneca memory optimization increases latency by 73\% across applications.
By reducing memory use however, Seneca reduces the monetary cost by 83\% across applications 
even with the added overhead of optimization.

%%%%%%%%%%%%% everything below this point is commented out %%%%%%%%%%%%%%

% \textcolor{blue}{It would be good here in the Seneca case to also run the applications in the minumum amount of memory discovered by Seneca (ie if we were to run Seneca ahead of time, taking the max memory used by any of the functions per application) -- to show what Seneca is missing.  this assumes you are doing the memory optimization WHILE you are doing the tuning -- if you are not, you can leave this out, but we need to remind the reader at this point how the memory optimization is done by Seneca (we should do this in this paragraph, either way).}

% \textcolor{blue}{Comments: The minimum amount of memory is the "max memory used" value. I tried that out and the execution time increases dramatically at the minimum memory case. I will explore the idea of simultaneous optimization and tuning later}

% \textcolor{red}{state what the columns and rows are; then write up some analysis on what the table data is showing and why. provide analysis for both tables and summarize the key differences between them.}

%The results of maximum memory scenario are shown in Figure~\ref{fig:cost_max_memory}. The max memory used and billed duration are reported by AWS CloudWatch and averaged throughout whole search space for each application. Figure ~\ref{fig:cost_optimized} demonstrates the results of optimized memory scenario. The total cost stems from function optimization and hyperparameter tuning. As a comparison of two scenarios, Figure~\ref{fig:cost_analysis} illustrates the total cost of optimized memory scenario is lower than maximum memory scenario in each application respectively.

\ignore{ %%%%%%%%%% all of this data already appears in the tables above! %%%%%%%%%%%%%
\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{Cost_analysis}
\caption{ The cost analysis of Seneca with (Opt) and without (No Opt) the use of its memory optimization. 
By reducing the memory use of each, Seneca reduces the monetary cost of hyperparameter tuning by \textcolor{blue}{X\% on average, across these applications.  *compute and Fill this X in*.}
\textcolor{blue}{Change the legend as follows: change "Tuning at Max Memory" to "No Opt"; change "Function Optimization" to "Opt cost"; change "Tuning" to "Opt". If you can put legend in this order: Opt, Opt cost, No Opt} 
\label{fig:cost_analysis}}
\vspace{-0.2in}
\end{figure}

\begin{figure}[t] \centering 
\includegraphics[scale=0.36]{Latency_analysis}
\caption{Latency of Seneca with (Opt) and without (No Opt) memory optimization, for each application. As Seneca reduces memory use (and cost), it also extends the execution time of the functions (and thus total tuning time, i.e., the latency of Seneca) by Y\% on average across applications \textcolor{blue}{compute and fill in Y here.}
\textcolor{blue}{Change the legend as follows: change "Optimized Memory" to "Opt"; change "Maximum Memory" to "No Opt"; Make sure that Opt stays green and change No Opt to be red (same as above graph)} 
\label{fig:latency_analysis}}
\vspace{-0.2in}
\end{figure}

Figure~\ref{fig:cost_analysis} presents the breakdown in the monetary cost of 
using Seneca (performing hyperparameter tuning) with and without its automatic memory optimization.  
We plot bar graphs for each application across the x-axis; the y-axis is monetary cost in US dollars. The stacked column is the total cost of tuning by Seneca Memory Optimization, and the green and red segments represent the cost of tuning and function optimization respectively. The red column at the right-hand side of each application is the total cost of tuning by using lambda function at maximum memory. For computation intensive applications like Prophet, they generate higher costs, which depend on the duration and memory usage on AWS Lambda. %The difference between two costs

\textcolor{red}{Add analysis here on what the columns are showing -- discuss any anomalies (ie why is prophet optimization cost more than the others; why mult-regression difference is greater than the others). provide a summary for that states the average difference between each pair of bars across applications.}

By reducing the amount of memory used, Seneca reduces its cost.  However by doing so, Seneca also 
increases the total time it requires to perform hyperparameter tuning (latency) as shown 
in Figure~\ref{fig:latency_analysis} (due to the memory constraints place on execution).  The x-axis shows two bars per application, one with memory optimization (Opt) and one without (No Opt).  The y-axis is 
Seneca's total latency, on average, to perform hyperparameter tuning. 
On average, the Seneca memory optimization increases latency by X\% on average across applications.
\textcolor{red}{Compute and fill in X here.}
\textcolor{blue}{Add analysis here to discuss why the performance difference is different for different
applications (some more sensitive to memory restrictions and why), and anything else you can pull out that is interesting in these numbers.}

%With respect to the latency, maximum memory scenario has lower execution time than optimized memory scenario due to the additional computational power attached to allocated memory. However, this latency discrepancy narrows down as max memory used increases, especially in memory-bound applications like neural network. This observation proves our previous argument about disproportional increase of computational power along allocated memory. In such case, Seneca is able to find the sweet spot of allocated memory and completes hyperparameter tuning at a lower cost without sacrificing latency and performance.

}

### 2019-02-01 results.tex
minor

@@
 
-% \textcolor{blue}{Describe what these are in a couple of sentences.}
 In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
@@
 The application returns the average MSE across cross validations.
-%Using a the model trained by default parameter setting, this average MSE metric is 0.284.
 
@@
 we use a feedforward multilayer perceptron model~\cite{ref:feedforward_nn} 
-for the classification task.
+for the classification task. The hyperparameter space and default settings that Seneca uses for these three applications are show in Table~\ref{tab:defaults}.
+%Chandra is working on adding this table now, from:
+%https://github.com/Heronalps/Seneca/blob/tuning/config/neural_network/config.py
+%https://github.com/Heronalps/Seneca/blob/tuning/config/xgboost/config.py
+%https://github.com/Heronalps/Seneca/blob/tuning/config/svc/config.py
 
@@
 XGBoost also computes MSE for its regression task on the same datasets.
-The dataset has been filtered to remove correlated features (those with an absolute value of the Pearson correlation coefficient greater than 0.8) and outliers.
+The dataset has been filtered to remove correlated features (those with an absolute value of the
+Pearson correlation coefficient greater than 0.8) and outliers. 
 %The dataset has also been balanced by downsampling one target whose number 
@@
 user might employ when using these applications
-as a "black box".  The worst performing scenario shows how bad the results can be
+as a ``black box''.  The worst performing scenario shows how bad the results can be
 when parameters are poorly tuned.  Finally, the best configuration 

### 2019-02-01 results.tex
need diamoinds below whiskers

@@
 
-In this section,
-we evaluate Seneca in terms of performance, monetary cost, and hyperparameter tuning time (latency), 
-using machine learning applications that we ported to Seneca (i.e. that we implemented
-as lambda functions). 
-We first overview these applications and our empirical methodology. 
-We then present our experimental results.
+In this section, we evaluate Seneca in terms of performance, monetary cost,
+and hyperparameter tuning time (latency), using machine learning applications
+that we ported to Seneca (i.e. that we implemented as lambda functions).  We
+first overview these applications and our empirical methodology.  We then
+present our experimental results.
 
 \subsection{Benchmark Applications and Training/Testing  Datasets}
-The machine learning applications that we use to evaluate Seneca 
-are shown in Table~\ref{tab:bmarks}, each with 
-a brief description.
-Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
+
+The machine learning applications that we use to evaluate Seneca are shown in
+Table~\ref{tab:bmarks}, each with a brief description.
+Prophet~\cite{ref:prophet} is a time series analysis library built and
+maintained by Facebook and the open-source community. The input dataset is a
+time series of view counts
 %logorithm
 of Payton Manning's wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016.
-The dataset exhibits both seasonality and a holiday effect (e.g. around the super bowl games). 
-We use the first 6 years as the training set and the last 2 years as the testing set.
-We use a cross-validation horizon (sliding window) of 1-year, 
-and a period (sliding pace) 
-of 180 days.  As such, Seneca performs three cross-validations for each 2-year testing range.
+The dataset exhibits both seasonality and a holiday effect (e.g. around the
+super bowl games).  We use the first 6 years as the training set and the last
+2 years as the testing set.  We use a cross-validation horizon (sliding
+window) of 1-year, and a period (sliding pace) of 180 days.  As such, Seneca
+performs three cross-validations for each 2-year testing range.
 
@@
 
-Prophet expects multiple hyperparameters: \textit{growth} specifies linear or logistic trend model growth; \textit{prior scale} indicates the strength of the 
-sparse prior probability~\cite{ref:sparse_prior}. 
-There are three prior scale hyperparameters for change point, holidays, and seasonality. 
-Since Prophet uses a Fourier sum to estimate seasonality, 
-the \textit{fourier order} is the number of terms in the partial Fourier 
-sum. \textit{Seasonality mode} indicates that the effect of seasonality is either 
-multiplicative or additive. Finally, the width of uncertainty intervals 
-can be set using the hyperparameter \textit{interval width}.
+Prophet accepts the following hyperparameters: 
+\textit{growth} specifies linear or
+logistic trend model growth; \textit{prior scale} indicates the strength of
+the sparse prior probability~\cite{ref:sparse_prior}.  There are three prior
+scale hyperparameters for change point, holidays, and seasonality.  Since
+Prophet uses a Fourier sum to estimate seasonality, the \textit{fourier order}
+is the number of terms in the partial Fourier sum. \textit{Seasonality mode}
+indicates that the effect of seasonality is either multiplicative or additive.
+Finally, the width of uncertainty intervals can be set using the
+hyperparameter \textit{interval width}.
 
-In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
-the application or that are defined by the application developer) for each application.  
-The default parameters and tuning options for this Prophet are listed in the table~\ref{tab:prophet_para}.
-For each cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and $n$ is the number of data points.
-The application returns the average MSE across cross validations.
+In the results that follow, we evaluate \textit{default} parameteterizations
+(that come with the application or that are defined by the application
+developer) for each application.  The default parameters and tuning options
+for this Prophet are listed in the table~\ref{tab:prophet_para}. For each
+cross validation, the application computes mean square error (MSE) as
+$\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground
+truth, $Y_i$ is model prediction and $n$ is the number of data points. The
+application returns the average MSE across cross validations.
 
@@
 
-Multi-Regression is a regression application 
-developed by the authors of 
-an IoT project~\cite{iot-cpu} that
-predicts outdoor temperature from the processor 
-temperature of single board computers (SBCs).  
-The technique uses multiple linear regression models computed from time
-series of processor temperature measurements,
-to predict outdoor microclimate temperatures (e.g. for use in 
-precision agriculture applications such as irrigation control and frost protection).
-The training dataset consists of eight input time series (one per SBC, each containing 
-5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.
+Multi-Regression is a regression application developed by the authors of an
+IoT project~\cite{iot-cpu} that predicts outdoor temperature from the
+processor temperature of single board computers (SBCs).  The technique uses
+multiple linear regression models computed from time series of processor
+temperature measurements, to predict outdoor microclimate temperatures (e.g.
+for use in precision agriculture applications such as irrigation control and
+frost protection).  The training dataset consists of eight input time series
+(one per SBC, each containing 5-minute measurements) from April 5th, 2018 to
+Dec. 10th, 2018.  In addition, for each regression there is a single ``ground
+truth'' time series of measurements taken from a temperature sensor.
 
-A hyperparameter configuration for this application is a subset of input SBC time series.
-Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
-For this application,
-we assume the default parameterization is the set of all $N$ input time series (8 in this case).
-The test dataset for this application is a time series of the outdoor temperature (ground truth) 
-over the same period.  The application makes predictions for each of these outdoor temperatures
-using the model constructed from the training set
-and computes the mean square error across predicted and ground truth value pairs.
+A hyperparameter configuration for this application is a subset of input SBC
+time series.  That is, the ``best'' regression (in terms of lowest regression
+error) comes from some subset of  the SBC series when used as explanatory
+variables for a regression of the ground truth series.  Seneca considers all
+\texttt{$2^N - 1$} potential subsets (for $N$ SBC time series).  For this
+application, we assume the default parameterization is the set of all $N$
+input SBC time series (8 in this case) as explanatory variables.  The test
+dataset for this application is a time series of the outdoor temperature
+(ground truth) over the same period.  The application makes predictions for
+each of these outdoor temperatures using the model constructed from the
+training set and computes the mean square error across predicted and ground
+truth value pairs.
 
-XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
-performs both regression and classification. We consider it a regression application and
-a classification application in this evaluation.  
-Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
-based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
-Neural network~\cite{ref:neural_network} is a machine learning framework that learns 
-and make decisions from patterns in an input dataset. For this application, 
-we use a feedforward multilayer perceptron model~\cite{ref:feedforward_nn} 
-for the classification task. The hyperparameter space and default settings that Seneca uses for these three applications are show in Table~\ref{tab:defaults}.
+XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient
+boosting, which performs both regression and classification. We consider it a
+regression application and a classification application in this evaluation.
+Support vector classification (SVC)~\cite{ref:svc} is a classification
+algorithm based on support vector machine and implemented by
+libsvm~\cite{ref:libsvm} library.  Neural network~\cite{ref:neural_network} is
+a machine learning framework that learns and make decisions from patterns in
+an input dataset. For this application, we use a feedforward multilayer
+perceptron model~\cite{ref:feedforward_nn} for the classification task. The
+hyperparameter space and default settings that Seneca uses for these three
+applications are show in Table~\ref{tab:defaults}.
 %Chandra is working on adding this table now, from:
@@
 
-For these applications (XGBoost, SVC, and Neural Network), 
-we use a labeled dataset for training, testing, and evaluation from a separate
-project (name and citation ommitted for blind review).
-The dataset contains
-measurements of individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) 
-taken by a fruit sorting and grading device (using a large number of sensors).  
-The measurements (i.e. features)
-include size, shape, weight, color, diameter, flatness, among other characteristics,
-for each fruit.  The label indicates which field each fruit was harvested from.  
-The applications train a model on a random subset of the data.  
-They then use this model to predict the field
-from which each fruit originates.
-They compute classification accuracy score as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the prediction class, $Y_i$ is the true class, $n$ is the number of samples and 1(x) is the indicator function.
-XGBoost also computes MSE for its regression task on the same datasets.
-The dataset has been filtered to remove correlated features (those with an absolute value of the
-Pearson correlation coefficient greater than 0.8) and outliers. 
+For these applications (XGBoost, SVC, and Neural Network), we use a labeled
+dataset for training, testing, and evaluation from a separate project (name
+and citation ommitted for blind review).  The dataset contains measurements of
+individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a
+fruit sorting and grading device (using a large number of sensors).  The
+measurements (i.e. features) include size, shape, weight, color, diameter,
+flatness, among other characteristics, for each fruit.  The label indicates
+which field each fruit was harvested from.  The applications train a model on
+a random subset of the data.  They then use this model to predict the field
+from which each fruit originates. They compute classification accuracy score
+as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
+prediction class, $Y_i$ is the true class, $n$ is the number of samples and
+1(x) is the indicator function. XGBoost also computes MSE for its regression
+task on the same datasets. The dataset has been filtered to remove correlated
+features (those with an absolute value of the Pearson correlation coefficient
+greater than 0.8) and outliers. 
 %The dataset has also been balanced by downsampling one target whose number
 %greatly exceeds other ones. 
-The resulting dataset contains 33926 rows (individual fruit) distributed evenly across 5 targets, and each row has 18 features.
+The resulting dataset contains 33926 rows (individual fruit) distributed
+evenly across 5 targets, and each row has 18 features.
 
@@
 \subsection{Empirical Methodology}
-To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
-For tuning performance, we use mean squared error (MSE) for regression tasks 
-and percentage accuracy for
-classification tasks. The default configuration that we 
-consider for each application is described above.
-We report results for the default, the best (Seneca's recommendation), 
-and the worst performing configurations.  Seneca considers all possible combinations 
-of the hyperparameter settings specified in the configuration, uses them
-to train, test, and evaluate models for each. 
-The default results represents a configuration that a novice or first time 
-user might employ when using these applications
-as a ``black box''.  The worst performing scenario shows how bad the results can be
-when parameters are poorly tuned.  Finally, the best configuration 
-is the one that results from tuning they hyperparameters for the test/train split
-that Seneca considers.
 
-We deploy Seneca on Amazon Web Services (AWS) Lambda and extract
-execution time and memory use from AWS CloudWatch logs.  
-We then compute monetary cost
+To evaluate Seneca, we measure tuning performance, application execution time,
+and monetary cost.  For tuning performance, we use mean squared error (MSE)
+for regression tasks and percentage accuracy for classification tasks. The
+default configuration that we consider for each application is described
+above.  We report results for the default, the best (Seneca's recommendation),
+and the worst performing configurations.  Seneca considers all possible
+combinations of the hyperparameter settings specified in the configuration,
+uses them to train, test, and evaluate models for each.  The default results
+represents a configuration that a novice or first time user might employ when
+using these applications as a ``black box''.  The worst performing scenario
+shows how bad the results can be when parameters are poorly tuned.  Finally,
+the best configuration is the one that results from tuning they
+hyperparameters for the test/train split that Seneca considers.
+
+We deploy Seneca on Amazon Web Services (AWS) Lambda and extract execution
+time and memory use from AWS CloudWatch logs.  We then compute monetary cost
 using the AWS Lambda pricing model~\cite{ref:pricing}.
 %awslambdapricing: https://aws.amazon.com/lambda/pricing/
-Each function downloads the training and testing dataset 
-of the application from AWS Simple Storage Service (S3) upon function invocation. 
-We do not consider the cost of dataset storage in our cost computations (it is very small).
+Each function downloads the training and testing dataset of the application
+from AWS Simple Storage Service (S3) upon function invocation.  We do not
+consider the cost of dataset storage in our cost computations (it is very
+small).
 
-We also experiment with different memory configurations for Seneca functions in AWS Lambda.  
-We evaluate
-the performance and cost of allocating the maximum memory for each and for automatically optimizing 
-memory use using Seneca. We assume that all combinations hyperparameter settings use the 
-same maximum amount of memory across functions; we 
-have verified that this assumption holds for the applications and datasets that
-we consider herein.
-We plan to consider applications for which hyperparameter settings require 
-different maximum amounts of memory as part of future work.
+We also experiment with different memory configurations for Seneca functions
+in AWS Lambda.  The pricing model for AWS Lambda charges the account under
+which a computation executes based on the product of its execution time and
+the size of the memory the account owner chooses to configure.  If the
+application exceeded the configured memory, it is terminated.  
+%Thus, the cost
+%optimal configuration is one in which the allocated memory is just large
+%enough to run the application, and no larger, assuming the size of the memory
+%does not affect execution runtime.  
+Seneca includes an probing
+mechanism that attempts to ``learn'' this memory size for a given
+application that minimizes its ecxecution cost.  Note that because AWS Lambda
+does not provide a way to control the speed of the processor that ultimately
+executes each Lambnda function, memory size is the only available cost tuning
+parameter.
+
+We evaluate the performance and cost of allocating the maximum memory versus
+Seneca's automatic memory size optimizer. To do so, we assume that all
+combinations hyperparameter settings use the same maximum amount of memory
+across all function executions. We have verified that this assumption holds
+for the applications and datasets that we consider herein however we plan to
+consider applications for which hyperparameter settings require different
+maximum amounts of memory as part of future work.
 
@@
 
-We first evaluate Seneca using the three regression applications: 
-Prophet, Multi-Regression, and XGBoost (regression task). 
-Table ~\ref{tab:mse} shows the size of the hyperparameter search space (number of configurations
-considered) and the mean squared error (MSE)
-for each of the regression applications that we consider (columns 3-5).
-The first row of data is 
- the number of hyperparameter configurations that Seneca considers in search space of each. 
-The last three rows show the MSE for the default, worst, and best performing 
-hyperparameter configuation reported by Seneca (lower is better).  
-Seneca reduces MSE by 26\%, 16\%, and 67\%, for Prophet, Multi-Regression, and XGBoost,
-respectively, for the datasets and training methodologies that we consider.
-Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 96\%, respectively.
+We first evaluate Seneca using the three regression applications: Prophet,
+Multi-Regression, and XGBoost (regression task).  Table ~\ref{tab:mse} shows
+the size of the hyperparameter search space (number of configurations
+considered) and the mean squared error (MSE) for each of the regression
+applications that we consider (columns 3-5).  The first row of data is the
+number of hyperparameter configurations that Seneca considers in search space
+of each.  The last three rows show the MSE for the default, worst, and best
+performing hyperparameter configuation reported by Seneca (lower is better).
+Seneca reduces MSE by 26\%, 16\%, and 67\%, for Prophet, Multi-Regression, and
+XGBoost, respectively, for the datasets and training methodologies that we
+consider.  Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 96\%,
+respectively.
 
@@
 for these applications 
-for the entire hyperparameter 
-search space. The central rectangle covers the interquartile range (IQR), 
+for the entire hyperparameter search space. The central rectangle covers the interquartile range (IQR), 
 which is defined as the range of data 
@@
 potential room for improvement in MSE. The box plot also illustrates 
-that the best MSE of Prophet and multivariate regression are among the outliers, 
-indicating that a comprehensive search is critical to finding the best configurations. 
+that low MSE hyperparametrizations are often rare in the hyperparameter space.
+Note that for Prophet and Multi-regression, the number of parameterizations that
+yield an MSE lie below the low whisker is small and that the best MSE is
+always more than $2 * IQR$ below the Q1 quartile.  Thus a comprehensive
+exploration of the hyperparameter space is warranted from the perspective of
+minimizing the MSE.
+
+%of Prophet and multivariate regression are among the outliers, 
+%indicating that a comprehensive search is critical to finding the best configurations.
+
 %\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}

### 2019-02-01 results.tex
MZ- Update MSE and ACCU numbers

--- 2019-02-01 results.tex
@@
 the application or that are defined by the application developer) for each application.  
-The default parameters and tuning options for this Prophet are listed in the table~\ref{tab:prophet_para}.
-For each cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and $n$ is the number of data points.
-The application returns the average MSE across cross validations.
-%Using a the model trained by default parameter setting, this average MSE metric is 0.284.
+The default parameters and tuning options for this application are listed in the table~\ref{tab:prophet_para}.
+For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points.
+Then the application returns the average MSE of all cross validation.
+Based on the model trained by default parameter setting, this average MSE metric is 0.284.
 
@@
 \end{tabular}}
-\caption{Default hyperparameters for Prophet. The default value and tuning options are listed. 
+\caption{The selected configurable hyperparameters of Prophet. The default value and tuning options are listed. 
 \label{tab:prophet_para}}
@@
 Multi-Regression is a regression application 
-developed by the authors of 
-an IoT project~\cite{iot-cpu} that
-predicts outdoor temperature from the processor 
+from an IoT project~\cite{iot-cpu} that was developed by the authors
+to predict outdoor temperature from the processor 
 temperature of single board computers (SBCs).  
@@
 For these applications (XGBoost, SVC, and Neural Network), 
-we use a labeled dataset for training, testing, and evaluation from a separate
-project (name and citation ommitted for blind review).
-The dataset contains
-measurements of individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) 
+we use a labeled dataset for training, testing, and evaluation from 
+this project~\cite{iot-cpu}. The dataset contains
+measurements from individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) 
 taken by a fruit sorting and grading device (using a large number of sensors).  
@@
 include size, shape, weight, color, diameter, flatness, among other characteristics,
-for each fruit.  The label indicates which field each fruit was harvested from.  
+for each fruit.  The label indicates which field the fruit was harvested from.  
 The applications train a model on a random subset of the data.  
 They then use this model to predict the field
+%%<<<<<<< HEAD
+%%from which each fruit originates.  They compute classification accuracy 
+%%as \textcolor{blue}{finish this.}.  XGBoost also computes MSE for its regression task
+%%on the same datasets.  The dataset has been filtered authors to remove correlated 
+%%features (those with an absolute value of the Pearson correlation coefficient greater than 0.8).  
+%%The resulting dataset contains 218150 rows (individual fruit) each with 19 features. 
 from which each fruit originates.
-They compute classification accuracy score as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the prediction class, $Y_i$ is the true class, $n$ is the number of samples and 1(x) is the indicator function.
+They compute classification accuracy score as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the prediction class, $Y_i$ is the true class, n is the number of samples and 1(x) is the indicator function.
 XGBoost also computes MSE for its regression task on the same datasets.
-The dataset has been filtered to remove correlated features (those with an absolute value of the Pearson correlation coefficient greater than 0.8) and outliers.
-%The dataset has also been balanced by downsampling one target whose number 
-%greatly exceeds other ones. 
-The resulting dataset contains 33926 rows (individual fruit) distributed evenly across 5 targets, and each row has 18 features.
+The dataset has been filtered to remove correlated features (those with an absolute value of the Pearson correlation coefficient greater than 0.8).
+The dataset has also been balanced by downsampling one target whose number greatly exceeds other ones.
+The resulting dataset contains 33926 rows (individual fruit) distributed evenly to 5 targets and each row has 18 features.
 
@@
 %It then randomly indexes the data set and splits it into two.  
-For these applications (XGBoost, SVC, and Neural Network), 
-Seneca splits the dataset and uses 80\% and 20\% for testing.
-For Neural Network and XGBoost, we also consider other splits
-that requires less data for training: \textcolor{blue}{list them here once we finish
-the additional results}. 
+For these applications (XGBoost, SVC, and Neural Network), we consider three split scenarios for training and testing: 80\%-20\%, 20\%-80\% and 0.1\%-99.9\%.
+As the proportion of training data decreases, the performance of classifier degrades accordingly and we argue that Seneca is able to eke out improvement even with very limited training data.
+%\textcolor{blue}{list them here once we finish the additional results} 
 %This setup also means that each Seneca function
@@
 consider for each application is described above.
-We report results for the default, the best (Seneca's recommendation), 
-and the worst performing configurations.  Seneca considers all possible combinations 
-of the hyperparameter settings specified in the configuration, uses them
-to train, test, and evaluate models for each. 
-The default results represents a configuration that a novice or first time 
+We report results for the default, best (Seneca's recommendation), 
+and worst performing configurations.  Seneca computes all possible combinations 
+of the hyperparameter settings specified in the configuration to extract each of these results.
+The default results represents those that a novice or first time 
 user might employ when using these applications
 as a "black box".  The worst performing scenario shows how bad the results can be
-when parameters are poorly tuned.  Finally, the best configuration 
-is the one that results from tuning they hyperparameters for the test/train split
-that Seneca considers.
+when parameters are poorly tuned.  Finally, the best is the upper bound on what is possible from 
+tuning the hyperparameters (e.g. using expert knowledge or Seneca).
 
 We deploy Seneca on Amazon Web Services (AWS) Lambda and extract
-execution time and memory use from AWS CloudWatch logs.  
-We then compute monetary cost
+execution time and memory use from AWS CloudWatch logs.  We then compute monetary cost
 using the AWS Lambda pricing model~\cite{ref:pricing}.
@@
 same maximum amount of memory across functions; we 
-have verified that this assumption holds for the applications and datasets that
-we consider herein.
+have verified that this assumption holds for the applications and datasets we consider.
 We plan to consider applications for which hyperparameter settings require 
@@
 \hline
-Worst MSE & 1.266 & 43.752 & 8.069 \\
+Worst MSE & 1.266 & 43.752 & 8.98 \\
 \hline
-Best MSE (Seneca) & 0.220 & 9.621 & 0.049 \\
+Best MSE (Seneca) & 0.220 & 9.621 & 0.044 \\
 \hline
@@
 \end{tabular}
-\caption{Combination count and MSE for the default, 
-best (Seneca's recommendation), 
-and worst hyperparameter configurations for the three regression applications. 
+\caption{Combination count and MSE for the default, best (Seneca's recommendation), and worst hyperparameter configurations for the three regression applications. 
 For the MSE  values (rows 3-5), lower is better.
@@
 \begin{figure}[t] \centering 
-\includegraphics[scale=0.36]{box_plot_mse}
-\caption{The box plot of MSE from the three regression applications 
-across the hyperparameter tuning search space. 
-The red notch shows the MSE from the default configuration. 
+\includegraphics[scale=0.36]{box_plot_mse_2}
+\caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space.
+The red notch shows the MSE from the default settings.
 The colored diamonds are outliers beyond two interquartile ranges.
@@
 The first row of data is 
- the number of hyperparameter configurations that Seneca considers in search space of each. 
+ the number of hyperparameter configurations in the search space of each. 
 The last three rows show the MSE for the default, worst, and best performing 
 hyperparameter configuation reported by Seneca (lower is better).  
-Seneca reduces MSE by 26\%, 16\%, and 67\%, for Prophet, Multi-Regression, and XGBoost,
+Note that Seneca's recommendation is the best performing configuration.
+Seneca reduces MSE by 26\%, 16\%, and 63\%, for Prophet, Multi-Regression, and XGBoost,
 respectively, for the datasets and training methodologies that we consider.
-Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 96\%, respectively.
+Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 99\%, respectively.
 
@@
 and are plotted as colored diamonds. The red notch identifies the MSE that results from training 
-the model using the default settings of hyperparameter. 
-The difference between red notch of lowest data 
-point is the improvement brought about by the use of Seneca. 
-The red notch marks the MSE of the default hyperparameterization.
-Each is located near the 
-From the location of red notch, we can see the MSE metrics 
-first quartile value indicating that there is significant 
-potential room for improvement in MSE. The box plot also illustrates 
-that the best MSE of Prophet and multivariate regression are among the outliers, 
-indicating that a comprehensive search is critical to finding the best configurations. 
+the model using the default settings of hyperparameter. The difference between red notch of lowest data 
+point is improvement brought about through the use of Seneca.
+From the location of red notch, we can see the MSE metrics from default configuration in three applications are close to the first quartile value, meaning the potential room for improvement is about 75\% over the range of MSE metric.
+The box plot also illustrates that the best MSE of Prophet and multivariate regression are among outliers, where a comprehensive search is very critical to find the best configurations.
 %\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}
@@
 classification applications: XGBoost (classification), SVC, and Neural Network.
-Figure~\ref{fig:accuracy} presents the accuracy percentage (higher is better) 
-reported by each application (3 left-most columns) 
-for the default, worst, and best hyperparameter tuning 
-configurations (data rows 2-4) reported by Seneca.  
-The first row of the table
-reports the number of configurations that Seneca considers in its search space.
-Seneca increases accuracy by 84\%, 84\%, and 80\%, for XGBoost (classification), 
+Table~\ref{tab:accuracy} presents the accuracy percentage (higher is better) 
+reported by each application (3 right-most columns) 
+for the default, worst, and best hyperparameter tuning configurations under three training and testing split scenarios reported by Seneca.  
+In the 80/20 percent split case, Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost (classification), 
 SVC, and Neural Network applications,
-respectively, for the datasets and training methodologies that we consider.
-Verses the worst case, Seneca improves accuracy by 86\%, 86\%, and 85\%, respectively.
+respectively.
+Verses the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%, respectively.
 
@@
 \hline
-& XGBoost & SVC & Neural Network\\
-\hline
-\# of Combinations & 768 & 512 & 432\\
+\textbf{80\%-20\%} & XGBoost & SVC & Neural Network\\
 \hline
 \hline
-Default MSE&2.42\%&3.93\%&6.51\%\\
+Default Accuracy & 95.70\% & 21.77\% & 84.23\%\\
 \hline
-Worst MSE&0.00\%&2.04\%&1.72\%\\
+Worst Accuracy&0.00\%&7.53\% & 19.19\%\\
 \hline
-Best MSE (Seneca) &86.07\%&87.76\%&86.34\%\\
+Best Accuracy (Seneca) &99.13\% & 83.29\% & 84.76\%\\
 \hline
+\hline
+\textbf{20\%-80\%} & XGBoost & SVC & Neural Network\\
+\hline
+Default Accuracy & 95.07\% & 21.31\% & 55.44\%\\
+\hline
+Worst Accuracy&0.00\% & 9.42\% & 19.55\%\\
+\hline
+Best Accuracy (Seneca) & 98.68\% & 43.61\% & 60.89\%\\
+\hline
+\hline
+\textbf{0.1\%-99.9\%} & XGBoost & SVC & Neural Network\\
+\hline
+Default Accuracy & 86.37\% & 20.02\% & 20.00\%\\
+\hline
+Worst Accuracy & 0.00\% & 19.99\% & 19.79\%\\
+\hline
+Best Accuracy (Seneca) & 89.14\% & 55.79\% & 29.99\%\\
+\hline
+
 %percent difference between default and best 83.65%, 83.84%, 79.83%
@@
 \end{tabular}
-\caption{Combination count and accuracy reported for the 
+\caption{The Accuracy reported for the 
 default, best (Seneca's recommendation), and worst hyperparameter configurations for 
-the three classification applications.  
-For the accuracy  values (rows 3-5), higher is better.
-\label{fig:accuracy}}
+the three classification applications under three train/test split scenarios.  
+For the accuracy values in the table, higher is better.
+\label{tab:accuracy}}
 %\vspace{-0.2in}
@@
 \includegraphics[scale=0.36]{box_plot_accuracy}
-\caption{The box plot of accuracy metric 
-from the classification applications for the entire hyperparameter tuning search space. 
-The red notch indicates the accuracy metric from the trained model using the default configuration. 
-The colorful diamonds are outliers beyond two interquartile ranges. Higher accuracy values are better.
+\caption{The box plot of accuracy metric from three classification applications for the entire hyperparameter tuning search space.
+The red notch indicates the accuracy metric from the trained model using default settings.
+The colorful diamonds are outliers beyond two interquartile ranges.
+Higher accuracy values are better.
 \label{fig:box_plot_accuracy}}
@@
 for the entire hyperparameter search space for each classification
-application.  The central rectangle covers from first quartile to third quartile 
-(Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. 
-The red notch indicates the accuracy metric from the model trained using the default 
-settings and colored diamonds show outliers beyond the whiskers.
+application.
+The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}.
+The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
 For both types of applications (regression and classification), Seneca significantly
 improves tuning performance over the default and worst case configurations for the 
-datasets and training methodologies that we consider.
+datasets and training methodologies we consider.
 
@@
 First, we configure each lambda function to use the maximum amount
-of memory allowed by AWS Lambda (3008 MB).  Second, we employ Seneca's memory optimization,
+of memory allowed by AWS Lambda (3008 MB).  Second, we employ Seneca's memory optimization 
 which automatically detects and configures the amount of memory needed by each function.
-Because memory impacts both cost and execution time (total latency of Seneca 
-hyperparameter tuning), we present empirically evaluate both 
+Because memory impacts both cost and execution time (total latency of Seneca hyperparameter tuning), 
+we present empirically evaluate both 
 in this subsection.  For each, we only include XGBoost once since its 
@@
 \hline
-Exec time (minutes)& 13 & 7 & 3 & 15 & 14 \\
+Exec time (minutes)& 24.96 & 4.18 & 17.48 & 0.91 & 2.49 \\
 \hline
-Cost of Tuning (\$) &0.406 & 0.220 & 0.075 & 0.213 & 0.161 \\
+Cost of Tuning (\$) & 0.722 & 0.121 & 0.5 & 0.023 & 0.072 \\
 \hline
 \end{tabular}
-\caption{Monetary cost of using Seneca for hyperparameter 
-tuning when configured to use the maximum amount of memory(3008MB) 
-possible for each function invocation. 
+\caption{ Monetary cost of using Seneca for hyperparameter tuning when configured to use the maximum amount of memory (3008 MB) possible for each function invocation. 
 \label{tab:cost_max_memory}}
@@
 \hline
-Exec time (minutes)& 33 & 17 & 9 & 17 & 14 \\
+Exec time (minutes)& 38.7 & 8.72 & 29.07 & 0.91 & 3.17 \\
 \hline
-Cost of Tuning (\$) &0.325 & 0.120 & 0.043 & 0.141 & 0.130 \\
+Cost of Tuning (\$) &0.62 & 0.086 & 0.354 & 0.007 & 0.056 \\
 \hline
@@
 \hline
-Total Cost (\$) &0.358 & 0.134 & 0.045 & 0.151 & 0.138 \\
+Total Cost (\$) &0.653 & 0.1 & 0.357 & 0.016 & 0.064 \\
 \hline
 \end{tabular}
-\caption{Seneca  Memory  Optimization:  The  monetary  cost  of 
-using Seneca for hyperparameter tuning when the amount of memory  
-used  for  each  function  invocation  is  automatically
-inferred and set by Seneca.
+\caption{ Seneca  Memory  Optimization:  The  monetary  cost  of using Seneca for hyperparameter tuning when the amount of memory  used  for  each  function  invocation  is  automatically inferred and set by Seneca.
 \label{tab:cost_optimized}}
@@
 Seneca's hyperparameter tuning for the corresponding application.  
-The second row shows the total monetary cost of tuning each application using Seneca;
-for Table~\ref{tab:cost_max_memory} (unoptimized) this is the Total Cost of using Seneca.
-
-To perform the memory optimization (Table~\ref{tab:cost_optimized}), 
-Seneca requires additional runs of the application
-and as such, introduces additional cost.  This cost is shown for each application in 
-the third row.  Total Cost is the sum of rows 2 and 3 in this table and is the 
-total cost of using Seneca with its memory optimization.
-
-By reducing the amount of memory used, Seneca reduces total cost.  
-However by doing so, Seneca also 
-increases the total time it requires to perform hyperparameter tuning (Exec time in minutes 
-in row 1 of both tables) for some applications.  
-On average, the Seneca memory optimization increases latency by 73\% across applications.
-By reducing memory use however, Seneca reduces the monetary cost by 83\% across applications 
-even with the added overhead of optimization.
-
-%%%%%%%%%%%%% everything below this point is commented out %%%%%%%%%%%%%%
+In table~\ref{tab:cost_max_memory}, the second row is total cost of tuning when Seneca's 
+lambda functions are configured to use the maximum amount of memory (3008 MB), whereas table~\ref{tab:cost_optimized} demonstrates the additional cost of optimization in the third row 
+and total cost on fourth row.
+% \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}
 
@@
 
-\ignore{ %%%%%%%%%% all of this data already appears in the tables above! %%%%%%%%%%%%%
 \begin{figure}[t] \centering 
-\includegraphics[scale=0.36]{Cost_analysis}
+\includegraphics[scale=0.36]{Cost_analysis_2}
 \caption{ The cost analysis of Seneca with (Opt) and without (No Opt) the use of its memory optimization. 
@@
 \begin{figure}[t] \centering 
-\includegraphics[scale=0.36]{Latency_analysis}
+\includegraphics[scale=0.36]{Latency_analysis_2}
 \caption{Latency of Seneca with (Opt) and without (No Opt) memory optimization, for each application.
@@
 In such case, Seneca is able to find the sweet spot of allocated memory and completes hyperparameter tuning at a lower cost without sacrificing latency and performance.
-
-}

### 2019-02-02 results.tex
rich makes a pass at the results section

@@
 \label{tab:bmarks}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}
@@
 \label{tab:prophet_para}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}
@@
 over the same period.  The application makes predictions for each of these outdoor temperatures
-using the model constructed from the training set
-and computes the mean square error across predicted and ground truth value pairs.
+using the regression coefficients constructed from the training set
+and computes the mean square error between predicted and ground truth value pairs.
 
@@
 
-For these applications (XGBoost, SVC, and Neural Network), 
-we use a labeled dataset for training, testing, and evaluation from 
-this project~\cite{iot-cpu}. The dataset contains
-measurements from individual citrus fruit (e.g. oranges, mandarins, lemons, etc.) 
-taken by a fruit sorting and grading device (using a large number of sensors).  
-The measurements (i.e. features)
-include size, shape, weight, color, diameter, flatness, among other characteristics,
-for each fruit.  The label indicates which field the fruit was harvested from.  
-The applications train a model on a random subset of the data.  
-They then use this model to predict the field
-%%<<<<<<< HEAD
-%%from which each fruit originates.  They compute classification accuracy 
-%%as \textcolor{blue}{finish this.}.  XGBoost also computes MSE for its regression task
-%%on the same datasets.  The dataset has been filtered authors to remove correlated 
-%%features (those with an absolute value of the Pearson correlation coefficient greater than 0.8).  
-%%The resulting dataset contains 218150 rows (individual fruit) each with 19 features. 
-from which each fruit originates.
-They compute classification accuracy score as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the prediction class, $Y_i$ is the true class, n is the number of samples and 1(x) is the indicator function.
-XGBoost also computes MSE for its regression task on the same datasets.
-The dataset has been filtered to remove correlated features (those with an absolute value of the Pearson correlation coefficient greater than 0.8).
-The dataset has also been balanced by downsampling one target whose number greatly exceeds other ones.
-The resulting dataset contains 33926 rows (individual fruit) distributed evenly to 5 targets and each row has 18 features.
+For these applications (XGBoost, SVC, and Neural Network), we use a labeled
+dataset for training, testing, and evaluation from this
+project~\cite{iot-cpu}. The dataset contains measurements from individual
+citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a fruit sorting
+and grading device (using a large number of sensors).  The measurements (i.e.
+features) include size, shape, weight, color, diameter, flatness, among other
+characteristics, for each fruit.  The label indicates which field the fruit
+was harvested from.  The applications train a model on a random subset of the
+data.  They then use this model to predict the field
+%%<<<<<<< HEAD %from which each fruit originates.  They compute classification
+%accuracy %as \textcolor{blue}{finish this.}.  XGBoost also computes MSE for
+%its regression task %on the same datasets.  The dataset has been filtered
+%authors to remove correlated %features (those with an absolute value of the
+%Pearson correlation coefficient greater than 0.8).  %The resulting dataset
+%contains 218150 rows (individual fruit) each with 19 features. 
+from which each fruit originates. They compute classification accuracy score
+as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
+prediction class, $Y_i$ is the true class, n is the number of samples and 1(x)
+is the indicator function. XGBoost also computes MSE for its regression task
+on the same datasets. The dataset has been filtered to remove correlated
+features (those with an absolute value of the Pearson correlation coefficient
+greater than 0.8). The dataset has also been balanced by downsampling one
+target whose number greatly exceeds other ones. The resulting dataset contains
+33926 rows (individual fruit) distributed evenly to 5 targets and each row has
+18 features.
 
@@
 %It then randomly indexes the data set and splits it into two.
-For these applications (XGBoost, SVC, and Neural Network), we consider three split scenarios for training and testing: 80\%-20\%, 20\%-80\% and 0.1\%-99.9\%.
-As the proportion of training data decreases, the performance of classifier degrades accordingly and we argue that Seneca is able to eke out improvement even with very limited training data.
+
+For these applications (XGBoost, SVC, and Neural Network), we consider three
+split scenarios for training and testing: 80\%-20\%, 20\%-80\% and
+0.1\%-99.9\%. As the proportion of training data decreases, the performance of
+classifier degrades accordingly.  However we note that using the optimized
+hyperparameters generated by Seneca, these calssifiers are able to achieve
+accuracy levels similar to those generated from the default parameters, but
+with significantly less training data.
+
+% and we argue that Seneca is able to eke out
+%improvement even with very limited training data.
+
 %\textcolor{blue}{list them here once we finish the additional results} 
@@
 \subsection{Empirical Methodology}
-To evaluate Seneca, we measure tuning performance, application execution time, and monetary cost.
-For tuning performance, we use mean squared error (MSE) for regression tasks 
-and percentage accuracy for
-classification tasks. The default configuration that we 
-consider for each application is described above.
-We report results for the default, best (Seneca's recommendation), 
-and worst performing configurations.  Seneca computes all possible combinations 
-of the hyperparameter settings specified in the configuration to extract each of these results.
-The default results represents those that a novice or first time 
-user might employ when using these applications
-as a "black box".  The worst performing scenario shows how bad the results can be
-when parameters are poorly tuned.  Finally, the best is the upper bound on what is possible from 
+
+To evaluate Seneca, we measure tuning performance, application execution time,
+and monetary cost.  For tuning performance, we use mean squared error (MSE)
+for regression tasks and percentage accuracy for classification tasks. The
+default configuration that we consider for each application is described
+above.  We report results for the default, best (Seneca's recommendation), and
+worst performing configurations.  Seneca computes all possible combinations of
+the hyperparameter settings specified in the configuration to extract each of
+these results.  The default results represents those that a novice or first
+time user might employ when using these applications as a ``black box.''  The
+worst performing scenario shows how bad the results can be when parameters are
+poorly tuned.  Finally, the best is the upper bound on what is possible from
 tuning the hyperparameters (e.g. using expert knowledge or Seneca).
 
-We deploy Seneca on Amazon Web Services (AWS) Lambda and extract
-execution time and memory use from AWS CloudWatch logs.  We then compute monetary cost
+To evaluate the cost savings introduced by Seneca,
+it on Amazon Web Services (AWS) Lambda~\cite{XXXaws-lambdaXXX} and extract
+execution time and memory use from AWS CloudWatch~\cite{XXXcloudwatchCXXX} logs.  
+We then compute monetary cost
 using the AWS Lambda pricing model~\cite{ref:pricing}.
@@
 
-We also experiment with different memory configurations for Seneca functions in AWS Lambda.  
-We evaluate
-the performance and cost of allocating the maximum memory for each and for automatically optimizing 
-memory use using Seneca. We assume that all combinations hyperparameter settings use the 
-same maximum amount of memory across functions; we 
-have verified that this assumption holds for the applications and datasets we consider.
-We plan to consider applications for which hyperparameter settings require 
-different maximum amounts of memory as part of future work.
+%We also experiment with different memory configurations for Seneca functions
+%in AWS Lambda.  
+We also investigate Seneca's automatic memory optimization capabilities.  To
+do so we compare the execution performance and cost of the benchmarks using
+the maximum allocatable memory size to the performance and cost when run with
+Seneca's automatically determined memory size.  Note that this comparison
+assume that the memory size used by each benchmark does not depend on
+hyperparameter settings.  We have verified that this assumption holds for the
+benchmarks and datasets we consider and plan to consider applications for
+which hyperparameter settings require different maximum amounts of memory as
+part of future work.
 
-\subsection{Tuning Performance}
+\subsection{Application Efficacy}
+
+We begin by evaluating Seneca's effect on application efficacy.
+That is, we detail the effect on the quality of the output generated by each
+application when Seneca determines the hyperparameter settings.
 
@@
 \label{fig:box_plot_mse}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{figure}
 
-We first evaluate Seneca using the three regression applications: 
-Prophet, Multi-Regression, and XGBoost (regression task). 
-Table ~\ref{tab:mse} shows the size of the hyperparameter search space (number of configurations
-considered) and the mean squared error (MSE)
-for each of the regression applications that we consider (columns 3-5).
-The first row of data is 
- the number of hyperparameter configurations in the search space of each. 
-The last three rows show the MSE for the default, worst, and best performing 
-hyperparameter configuation reported by Seneca (lower is better).  
-Note that Seneca's recommendation is the best performing configuration.
+%using the three regression applications: 
+%Prophet, Multi-Regression, and XGBoost (regression task). 
+Table~\ref{tab:mse} shows the effect of Seneca on the quality of the
+regressions generated by Prophet, Multi-regression, and XGBoost (when used as
+a regression algorithm). The first row of the table indicates the number of
+different hyperparameter settings Senica considered.  Rows 3 through 5 show
+the MSE generated by the default hytperparameter settings, the best (lowest
+MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
+for each regression algorithm and data set.
+
+%s mentioned previously, the table shows regression
+%quality in terms of MSE. 
+%
+%size of the hyperparameter search space (number of configurations
+%considered) and the mean squared error (MSE)
+%for each of the regression applications that we consider (columns 3-5).
+%The first row of data is 
+% the number of hyperparameter configurations in the search space of each. 
+%The last three rows show the MSE for the default, worst, and best performing 
+%hyperparameter configuation reported by Seneca (lower is better).
+
+%Note that Seneca's recommendation is the best performing configuration.
+Compared to the default hyperparameter settings,
 Seneca reduces MSE by 26\%, 16\%, and 63\%, for Prophet, Multi-Regression, and XGBoost,
@@
 
-Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better)
-for these applications 
-for the entire hyperparameter 
-search space. The central rectangle covers the interquartile range (IQR), 
-which is defined as the range of data 
-points from first quartile to third quartile (Q3 - Q1). 
-The upper whisker extends to the last datum less 
-than \texttt{$(Q3 + 2 * IQR)$} and the lower whisker extends to the first datum greater 
-than \texttt{$(Q1 - 2 * IQR)$}. The data points beyond the whiskers are considered outliers 
-and are plotted as colored diamonds. The red notch identifies the MSE that results from training 
-the model using the default settings of hyperparameter. The difference between red notch of lowest data 
-point is improvement brought about through the use of Seneca.
-From the location of red notch, we can see the MSE metrics from default configuration in three applications are close to the first quartile value, meaning the potential room for improvement is about 75\% over the range of MSE metric.
-The box plot also illustrates that the best MSE of Prophet and multivariate regression are among outliers, where a comprehensive search is very critical to find the best configurations.
-%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE for the range of configurations and how they change across applications. Include any insights that the boxplots add.}
+Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better) for
+these applications for the entire hyperparameter search space. The central
+rectangle covers the interquartile range (IQR), which is defined as the range
+of data points from first quartile to third quartile (Q3 - Q1).  The upper
+whisker extends to the last datum less than \texttt{$(Q3 + 2 * IQR)$} and the
+lower whisker extends to the first datum greater than \texttt{$(Q1 - 2 *
+IQR)$}. The data points beyond the whiskers are considered outliers and are
+plotted as colored diamonds. The red notch identifies the MSE that results
+from training the model using the default settings of hyperparameter. The
+difference between red notch of lowest data point is improvement brought about
+through the use of Seneca. From the location of red notch, we can see the MSE
+metrics from default configuration in three applications are close to the
+first quartile value in all three cases (slightly greater that Q1 for Prophet
+and Multi-regression and slight less for XGBoost).  However Seneca's MSE
+performance is congruent with the end of the lower whisker.  Overall, however,
+the quality of the application's output (for a given data set) is dramatically
+affected by hyperparameter settings.  Perdictably the default settings are
+near the ``good'' end of the spectrum, but as both Table~\ref{tab:mse} and
+Figure~\ref{fig:box_plot_mse} indicate, Seneca is able to find
+parameterization that improves output quality over the default settings
+in each case.
+%Thus for Prophet
+%and Multi-Regression, Seneca 
+%, meaning the potential room for improvement is about 75\%
+%over the range of MSE metric. The box plot also illustrates that the best MSE
+%of Prophet and multivariate regression are among outliers, where a
+%comprehensive search is very critical to find the best configurations. 
+%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE
+%for the range of configurations and how they change across applications.
+%Include any insights that the boxplots add.}
 
-%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance %%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 We next empirically evaluate the tuning performance of Seneca for the three
-classification applications: XGBoost (classification), SVC, and Neural Network.
-Table~\ref{tab:accuracy} presents the accuracy percentage (higher is better) 
-reported by each application (3 right-most columns) 
-for the default, worst, and best hyperparameter tuning configurations under three training and testing split scenarios reported by Seneca.  
-In the 80/20 percent split case, Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost (classification), 
-SVC, and Neural Network applications,
+classification applications: XGBoost (classification), SVC, and Neural
+Network.  Table~\ref{tab:accuracy} presents the accuracy percentage (higher is
+better) reported by each application (3 right-most columns) for the default,
+worst, and best hyperparameter tuning configurations under three training and
+testing split scenarios reported by Seneca.  In the 80/20 percent split case,
+Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost
+(classification), SVC, and Neural Network applications, respectively.  Verses
+the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%,
 respectively.
-Verses the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%, respectively.
 
@@
 \centering
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|l|c|c|c|}
 \hline
@@
 \hline
-\hline
-\textbf{20\%-80\%} & XGBoost & SVC & Neural Network\\
-\hline
-Default Accuracy & 95.07\% & 21.31\% & 55.44\%\\
-\hline
-Worst Accuracy&0.00\% & 9.42\% & 19.55\%\\
-\hline
-Best Accuracy (Seneca) & 98.68\% & 43.61\% & 60.89\%\\
-\hline
-\hline
-\textbf{0.1\%-99.9\%} & XGBoost & SVC & Neural Network\\
-\hline
-Default Accuracy & 86.37\% & 20.02\% & 20.00\%\\
-\hline
-Worst Accuracy & 0.00\% & 19.99\% & 19.79\%\\
-\hline
-Best Accuracy (Seneca) & 89.14\% & 55.79\% & 29.99\%\\
-\hline
+%\hline
+%\hline
+%\textbf{20\%-80\%} & XGBoost & SVC & Neural Network\\
+%\hline
+%Default Accuracy & 95.07\% & 21.31\% & 55.44\%\\
+%\hline
+%Worst Accuracy&0.00\% & 9.42\% & 19.55\%\\
+%\hline
+%Best Accuracy (Seneca) & 98.68\% & 43.61\% & 60.89\%\\
+%\hline
+%\hline
+%\textbf{0.1\%-99.9\%} & XGBoost & SVC & Neural Network\\
+%\hline
+%Default Accuracy & 86.37\% & 20.02\% & 20.00\%\\
+%\hline
+%Worst Accuracy & 0.00\% & 19.99\% & 19.79\%\\
+%\hline
+%Best Accuracy (Seneca) & 89.14\% & 55.79\% & 29.99\%\\
+%\hline
 
@@
 default, best (Seneca's recommendation), and worst hyperparameter configurations for 
-the three classification applications under three train/test split scenarios.  
+the three classification applications using 80\% of the data to train and 20\%
+of the data as a test set. 
+%under three train/test split scenarios.  
 For the accuracy values in the table, higher is better.
@@
 
+The 80-20 case represents the typical usage of these classification
+applications.  Often, when evaluating the accuracy of a specific classifier,
+the user uses the 80-20 split ``rule'' when measuring accuracy.  In this case,
+Seneca's improvement over the default parameterizations varies from less than
+1\% for the Neural Network application (column 4 for 80-20), to 61.5\% for SVC
+(best versus default in column 3 for 80-20 in the table).
+
 Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
@@
 For both types of applications (regression and classification), Seneca significantly
-improves tuning performance over the default and worst case configurations for the 
-datasets and training methodologies we consider.
+improves tuning performance over the default and worst case configurations for 
+XGBoost and SVC while generating only a slight improvement over default for
+Neural Network.
 
@@
 
-We next analyze the monetary cost introduced by Seneca. 
-We consider two scenarios for its implementation.
-First, we configure each lambda function to use the maximum amount
-of memory allowed by AWS Lambda (3008 MB).  Second, we employ Seneca's memory optimization 
-which automatically detects and configures the amount of memory needed by each function.
-Because memory impacts both cost and execution time (total latency of Seneca hyperparameter tuning), 
-we present empirically evaluate both 
-in this subsection.  For each, we only include XGBoost once since its 
-performance profile is the same
-regardless of whether we are using regression or classification.
+We next analyze the monetary cost effects introduced by Seneca.  To do so, we
+use Seneca to find the hyperparameterization that optimizes application output
+quality (lowest MSE for regression, highest accuracy for classification).
+However note that trying all possible hyperparameterizations incurs a cost.
+Further, because Seneca uses AWS Lambda, the amount of memory it uses during
+tuning affects this cost.
+
+Thus we compare two Seneca execution configurations.  In the first
+we configure each lambda function to
+use the maximum amount of memory allowed by AWS Lambda (3008 MB) for all
+executions.
+Second, we
+employ Seneca's memory optimization which automatically detects and configures
+the amount of memory needed by each function.  This optimization requires
+Seneca to ``probe'' to determine the best memory size to use.  The
+cost of these probes
+(denoted ``Optimizer Cost'') must be taken intio account as well.
+%Because memory impacts both
+%cost and execution time (total latency of Seneca hyperparameter tuning), we
+%present empirically evaluate both in this subsection.  
+Note that XGBoost's performance profile is identical when used for reghression
+or classification so we include its measurements only once in the following
+analysis.
+%For each, we only
+%include XGBoost once since its performance profile is the same regardless of
+%whether we are using regression or classification.
 
@@
 \centering
-\begin{tabular}{|c|c|c|c|c|c|}
+\begin{tabular}{|l|c|c|c|c|c|}
 \hline
@@
 \hline
-Cost of Tuning (\$) & 0.722 & 0.121 & 0.5 & 0.023 & 0.072 \\
+Seneca Cost (\$) & 0.722 & 0.121 & 0.5 & 0.023 & 0.072 \\
 \hline
 \end{tabular}
-\caption{ Monetary cost of using Seneca for hyperparameter tuning when configured to use the maximum amount of memory (3008 MB) possible for each function invocation. 
+\caption{Monetary cost of using Seneca for hyperparameter tuning when configured to use the maximum amount of memory (3008 MB) possible for each function invocation. 
 \label{tab:cost_max_memory}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}
@@
 \hline
-Cost of Tuning (\$) &0.62 & 0.086 & 0.354 & 0.007 & 0.056 \\
+Optimizer Cost (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
 \hline
-Cost of optimization (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
+Seneca Cost (\$) &0.62 & 0.086 & 0.354 & 0.007 & 0.056 \\
 \hline
@@
 \hline
+\hline
+Savings (\$) & 0.07 & \$0.02 & 0.15 & 0.007 & 0.008\\
+\hline
+Savings (\%) & 10\% & 17\% & 30\% & 30\% & 11\%\\
+\hline
 \end{tabular}
-\caption{ Seneca  Memory  Optimization:  The  monetary  cost  of using Seneca for hyperparameter tuning when the amount of memory  used  for  each  function  invocation  is  automatically inferred and set by Seneca.
+\caption{Seneca  Memory  Optimization:  The  monetary  cost  of using Seneca for hyperparameter tuning when the amount of memory  used  for  each  function  invocation  is  automatically inferred and set by Seneca.
 \label{tab:cost_optimized}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}
@@
 Seneca's hyperparameter tuning for the corresponding application.  
-In table~\ref{tab:cost_max_memory}, the second row is total cost of tuning when Seneca's 
-lambda functions are configured to use the maximum amount of memory (3008 MB), whereas table~\ref{tab:cost_optimized} demonstrates the additional cost of optimization in the third row 
-and total cost on fourth row.
+In Table~\ref{tab:cost_max_memory}, the second row is total cost of tuning when Seneca's 
+lambda functions are configured to use the maximum amount of memory (3008 MB). 
+Table~\ref{tab:cost_optimized} shows the cost of the memory optimizer in the
+second row, Seneca's cost using the optimization in the third row, and total cost on fourth row.
+Finally, in the fifth and six rows of Table~\ref{tab:cost_optimized} we show the
+savings that memory optimization introduces over using the maximum memory in
+dollar cost and as a percentage respectively.
+
+These tables illustrate two important cost features of Seneca.  First, using
+AWS Lambda, full hyperparameter space exploration is not expensive in 
+\textit{absolute} dollar cost terms.  Even using the maximum memory available
+for almost 25 minutes of execution time (cf Prophet in Table~\ref{XXX}), the
+total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
+optimizations produce a significant percentage savings which, over repeated
+executions, is important.
+
+Note also that Seneca's memory/cost optimzation
+introduces at an execution time penalty (relative to the maximum memory
+execution) for some of the applications.  That is, the
+execution times for all applications except SVC increase when Seneca chooses
+a memory size.  Thus while Seneca is finding the best application output
+quality and optimizing the cost of producing that output, it is doing so at
+the expense of execution performance (time to solution).    
+The source of this execution performance penalty is not clear.  We hypothesize
+that when requesting a large memory for AWS Lambda, Amazon chooses a machine
+that also has fast processors so the Lambda functions execute more quickly.
+If this supposition is true, then the AWS Lambda pricing model correctly
+weights the cost of additional memory (in light of the reduced execution time)
+because the large-memory executions are still more expensive.
+However regardless of the cause, the Seneca memory optimizer 
+provides a way to trade off time to solution for cost when the highest
+possible application output quality is desired.
 % \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}
@@
 
-% \textcolor{red}{state what the columns and rows are; then write up some analysis on what the table data is showing and why.
-provide analysis for both tables and summarize the key differences between them.}
+%\begin{figure}[t] \centering 
+%\includegraphics[scale=0.36]{Cost_analysis_2}
+%\caption{The cost analysis of Seneca automatics memory optimization. 
+%By reducing the memory use of each, Seneca reduces the monetary cost of hyperparameter tuning by 
+%an average of 20\% over using the maximum memory allocatable.\label{fig:cost_analysis}}
+%\vspace{-0.2in}
+%\end{figure}
 
-%The results of maximum memory scenario are shown in Figure~\ref{fig:cost_max_memory}.
-The max memory used and billed duration are reported by AWS CloudWatch and averaged throughout whole search space for each application.
-Figure ~\ref{fig:cost_optimized} demonstrates the results of optimized memory scenario.
-The total cost stems from function optimization and hyperparameter tuning.
-As a comparison of two scenarios, Figure~\ref{fig:cost_analysis} illustrates the total cost of optimized memory scenario is lower than maximum memory scenario in each application respectively.
+%\begin{figure}[t] \centering 
+%\includegraphics[scale=0.36]{Latency_analysis_2}
+%\caption{Latency of Seneca with (Opt) and without (No Opt) memory optimization, for each application.
+As Seneca reduces memory use (and cost), it also extends the execution time of the functions (and thus total tuning time, i.e., the latency of Seneca) by Y\% on average across applications \textcolor{blue}{compute and fill in Y here.}
+%\textcolor{blue}{Change the legend as follows: change "Optimized Memory" to "Opt"; change "Maximum Memory" to "No Opt"; Make sure that Opt stays green and change No Opt to be red (same as above graph)}
+%\label{fig:latency_analysis}}
+%\vspace{-0.2in}
+%\end{figure}
 
-\begin{figure}[t] \centering 
-\includegraphics[scale=0.36]{Cost_analysis_2}
-\caption{ The cost analysis of Seneca with (Opt) and without (No Opt) the use of its memory optimization. 
-By reducing the memory use of each, Seneca reduces the monetary cost of hyperparameter tuning by \textcolor{blue}{X\% on average, across these applications.  *compute and Fill this X in*.}
-\textcolor{blue}{Change the legend as follows: change "Tuning at Max Memory" to "No Opt"; change "Function Optimization" to "Opt cost"; change "Tuning" to "Opt".
-If you can put legend in this order: Opt, Opt cost, No Opt}
-\label{fig:cost_analysis}}
-\vspace{-0.2in}
-\end{figure}
+%Figure~\ref{fig:cost_analysis} presents the breakdown in the monetary cost of
+%using Seneca (performing hyperparameter tuning) with and without its automatic
+%memory optimization.  We plot bar graphs for each application across the
+%x-axis; the y-axis is monetary cost in US dollars. The stacked column is the
+%total cost of tuning by Seneca Memory Optimization, and the green and red
+%segments represent the cost of tuning and function optimization respectively.
+%The red column at the right-hand side of each application is the total cost of
+%tuning by using lambda function at maximum memory. For computation intensive
+%applications like Prophet, they generate higher costs, which depend on the
+%duration and memory usage on AWS Lambda. %The difference between two costs
 
-\begin{figure}[t] \centering 
-\includegraphics[scale=0.36]{Latency_analysis_2}
-\caption{Latency of Seneca with (Opt) and without (No Opt) memory optimization, for each application.
-As Seneca reduces memory use (and cost), it also extends the execution time of the functions (and thus total tuning time, i.e., the latency of Seneca) by Y\% on average across applications \textcolor{blue}{compute and fill in Y here.}
-\textcolor{blue}{Change the legend as follows: change "Optimized Memory" to "Opt"; change "Maximum Memory" to "No Opt"; Make sure that Opt stays green and change No Opt to be red (same as above graph)}
-\label{fig:latency_analysis}}
-\vspace{-0.2in}
-\end{figure}
+%\textcolor{red}{Add analysis here on what the columns are showing -- discuss
+%any anomalies (ie why is prophet optimization cost more than the others; why
+%mult-regression difference is greater than the others). provide a summary for
+%that states the average difference between each pair of bars across
+%applications.}
 
-Figure~\ref{fig:cost_analysis} presents the breakdown in the monetary cost of 
-using Seneca (performing hyperparameter tuning) with and without its automatic memory optimization.  
-We plot bar graphs for each application across the x-axis; the y-axis is monetary cost in US dollars.
-The stacked column is the total cost of tuning by Seneca Memory Optimization, and the green and red segments represent the cost of tuning and function optimization respectively.
-The red column at the right-hand side of each application is the total cost of tuning by using lambda function at maximum memory.
-For computation intensive applications like Prophet, they generate higher costs, which depend on the duration and memory usage on AWS Lambda.
-%The difference between two costs
-
-\textcolor{red}{Add analysis here on what the columns are showing -- discuss any anomalies (ie why is prophet optimization cost more than the others; why mult-regression difference is greater than the others).
-provide a summary for that states the average difference between each pair of bars across applications.}
-
-By reducing the amount of memory used, Seneca reduces its cost.  However by doing so, Seneca also 
-increases the total time it requires to perform hyperparameter tuning (latency) as shown 
-in Figure~\ref{fig:latency_analysis} (due to the memory constraints place on execution).
-The x-axis shows two bars per application, one with memory optimization (Opt) and one without (No Opt).
-The y-axis is
-Seneca's total latency, on average, to perform hyperparameter tuning. 
-On average, the Seneca memory optimization increases latency by X\% on average across applications.
-\textcolor{red}{Compute and fill in X here.}
-\textcolor{blue}{Add analysis here to discuss why the performance difference is different for different
-applications (some more sensitive to memory restrictions and why), and anything else you can pull out that is interesting in these numbers.}
-
-%With respect to the latency, maximum memory scenario has lower execution time than optimized memory scenario due to the additional computational power attached to allocated memory.
-However, this latency discrepancy narrows down as max memory used increases, especially in memory-bound applications like neural network.
-This observation proves our previous argument about disproportional increase of computational power along allocated memory.
-In such case, Seneca is able to find the sweet spot of allocated memory and completes hyperparameter tuning at a lower cost without sacrificing latency and performance.
+%By reducing the amount of memory used, Seneca reduces its cost.  However by
+%doing so, Seneca also increases the total time it requires to perform
+%hyperparameter tuning (latency) as shown in Figure~\ref{fig:latency_analysis}
+%(due to the memory constraints place on execution).  The x-axis shows two bars
+%per application, one with memory optimization (Opt) and one without (No Opt).
+%The y-axis is Seneca's total latency, on average, to perform hyperparameter
+%tuning.  On average, the Seneca memory optimization increases latency by X\%
+%on average across applications.  \textcolor{red}{Compute and fill in X here.}
+%\textcolor{blue}{Add analysis here to discuss why the performance difference
+%is different for different applications (some more sensitive to memory
+%restrictions and why), and anything else you can pull out that is interesting
+%in these numbers.}

### 2019-02-02 Seneca.tex
mz - Add background, Seneca, related_work

@@
 
-To facilitate model optimization on serverless architecture, we have developed a cloud service, namely Seneca. The Seneca service pipeline consists of
+To facilitate model optimization on serverless architecture, we have developed Seneca, a framework of  hyperparameter tuning for machine learning algorithm on AWS Lambda.
+The automated Seneca pipeline consists of packaging, deployment, serverless function optimization and hyperparameter tuning.
+Figure~\ref{fig:seneca} portrays the architecture of Seneca: the upper right front are three inputs from users: configuration file, specified model, and lambda function.
+Configuration file is where users specify all hyperparameter options and used by Seneca to create search space.
+Specified model is the implementation library of training and testing for certain machine learning model and provides clearly defined methods.
+Lambda function is the function handler that executes on AWS lambda.
+It downloads the dataset from S3 bucket, splits it by desired training and testing ratio, trains the specified model and returns the testing score.
+
+\subsection{Packaging and Deployment}
+
+After receiving these three inputs, Seneca launches a docker container that simulates the runtime of AWS Lambda.
+The container will compress the lambda function with all required libraries from specified model in a zip package and upload to S3 bucket.
+Using S3 bucket as an intermediate storage is to avoid the size limitation (10MB) of deployment package directly transported to AWS Lambda.
+Once uploaded to S3 bucket, docker container will deploy the deployment package to AWS lambda by AWS Command line Interface~\cite{ref:awscli} for Lambda.
+
+\subsection{Allocated memory optimization}
+
+Seneca has a component of optimizer that allows user to optimize allocated memory of lambda function.
+The mechanism of optimizer is based on our hypothesis of disproportional increase of computational power bound to allocated memory of lambda function.
+In other words, additional computational power brought by extra allocated memory reduces the billed duration and possibly overall cost as well.
+Seneca optimizer tries to find this "sweet-spot" of allocated memory leading to lowest compute charge.
+
+Instead of exhaustively searching for all 46 possible memory configurations of lambda function, we designed a heuristic that complete the task faster and more economically.
+The detailed heuristic is outlined in the Algorithm~\ref{algo:optimizer}.
+Seneca optimizer first probes function by a user-defined payload to obtain the memory used by function as start point.
+It also defines two double-end queues (deque) to store a certain number (N) of historical allocated memory and compute charge data.
+While the current allocated memory is less than or equal to 3008 MB, optimizer keeps probing function and calculated compute charge by current allocated memory and billed duration.
+Two exit conditions are established in the heuristic: first, compute charge monotonically increases in the whole length of deque; second, the increase slope is greater than a threshold.
+Once optimizer find both conditions hold, it will pop the left-most value from allocated memory deque and configure the lambda function at such memory.
+After repetitive experiments, we find the setting of N = 5 and slope = 1 has the highest possibility to find the lowest compute charge.
+
+\begin{algorithm}[]
+\SetAlgoLined
+\KwData{Typical payload}
+\KwResult{Optimal allocated memory}
+Find memory used by payload as start point\;
+Define deques for struct of allocated memory \& compute charge\;
+ \While{allocated memory $\leq$ 3008 MB}{
+
+  \eIf{compute charge monotonically increase in deque \& slope $\geq$ 1}{
+   Popleft from deque\;
+   Configure allocated memory of function\; 
+   Exit\;
+   }{
+   Increase allocated memory by 64 MB\;
+   Probe lambda function\;
+   Append new struct to deque\;
+  }
+ }
+ \caption{Seneca Optimizer Heuristic}
+ \label{algo:optimizer}
+\end{algorithm}
+
+\subsection{Tuning process}
+
+In order to invoke lambda function concurrently, Seneca integrates with Celery~\cite{ref:celery}.
+Celery is an asynchronous task queue based on distributed message passing.
+Celery workers are working processes that pick up tasks from the queue, execute tasks and store the asynchronous result at backend (Redis~\cite{ref:redis} in our case).
+Based on user-defined configuration file, Seneca creates a list of payloads that contains values of hyperparameters and the whole list covers the entire Cartesian product search space.
+Every payload launches a Celery task, on which a worker executes by triggering lambda function and insert a new record of the returned evaluation score and corresponding hyperparameter setting to backend database.
+
+After the comprehensive searching, Seneca will extract all records within search space and select the best result.
+Up to users' specification, Seneca returns either hyperparameter setting or a serialized model trained by this setting.

### 2019-02-02 background.tex
mz - Add background, Seneca, related_work

As an emerging programming diagram and architecture, serverless computing is built and developed by plentiful of platforms, like AWS, Azure and Google Cloud, where the implementation is still at exploratory stage. Likewise, the rapid development of machine learning research introduces various approaches and strategies to model optimization, like hyperparameter tuning. In this section, we provide background on AWS Lambda service and hyperparameter tuning which we build upon and extend in this paper.

\subsection{AWS Lambda CPU power}

On AWS Lambda platform, every function has configuration information associated with it. One of them is the allocated memory that ranges from 128 MB to 3008 MB at increment of 64 MB. As a conventional practice, it has been announced in the official documentation~\cite{ref:lambdalimits} that AWS Lambda allocates CPU power proportional to the memory by using the same ratio as a general purpose Amazon EC2 instance type. For example, allocating 1024 MB to lambda function makes it as twice computationally powerful as allocating 512 MB. Moreover, according to AWS Lambda pricing model, the cost of lambda function is calculated by allocated memory multiplied by billed duration, namely \textit{compute charge} in GB-second.

To verify such claim, we conduct an experiment of proportional increase of CPU power along with memory. We implement and deploy a CPU-bound lambda function that multiplies two 3-D matrices. In the experiment, the host configures the function at all 46 possible allocated memory amount, triggers the function at each point and records the billed duration of execution. Figure~\ref{fig:memory} demonstrates the relationship between allocated memory (x-axis) and reciprocal of billed duration (y-axis) that represents computing power (because billed duration is inversely correlated to the CPU power). Figure ~\ref{fig:compute_charge} illustrates the relationship between memory size (x-axis) and compute charge (y-axis). We observe that the CPU power plateaued after 1600 MB. Correspondingly, the compute charge slides down from 128 MB to 1600 MB and until then increases linearly.

Based on the above experimentation, we hypothesize the increase of CPU power is disproportional to the increase of allocated memory after a certain point. The trade-off between allocated memory and billed duration makes it possible to find a optimal (lowest) compute charge among all memory configurations. This assumption helps us build the function optimizer in the proposed framework.

\begin{figure}[t] \centering 
\includegraphics[scale=0.5]{memory}
\caption{The relationship between allocated memory and reciprocal of billed duration that represents the computing power.
\label{fig:memory}}
% \vspace{-0.2in}
\end{figure}

\begin{figure}[t] \centering 
\includegraphics[scale=0.5]{compute_charge}
\caption{The relationship between allocated memory and compute charge.
\label{fig:compute_charge}}
% \vspace{-0.2in}
\end{figure}

\subsection{Hyperparameter tuning}

Hyperparameters are a set of values that put constraints on the machine learning model in order to govern the learning process. As a critical phase of model optimization, hyperparameter tuning is the searching process for the best performing parameter setting, like number of iteration or initial weights, for machine learning algorithms. Usually hyperparameter tuning is able to increase the accuracy and reduce the loss at a certain amount depending on the searching process. The exhaustive search space is the Cartesian product of all hyperparameter options and cross validation score (i.e. accuracy or mean square error) is used to evaluate different settings. Since such searching process is embarrassingly parallel, it has the potential to execute on serverless platform (i.e. AWS Lambda) in a cost-effective and low-latency fashion.

### 2019-02-02 related_work.tex
mz - Add background, Seneca, related_work

In this section, we overview related works and research contributions focusing on serverless computing and model optimization.

With respect to serverless architecture, the benefit and drawback of such has been well researched by~\cite{ref:onesteptwostep}, in which the authors conduct a case study to show Lambda function can be more expensive than EC2 instances.~\cite{ref:baldini2017} points out serveral open research questions, including the boundaries and statelessness of serverless. Furthermore, we were inspired by ~\cite{ref:matrix} to experiment on disproportional CPU power with matrix multiplication application.

On the tooling of serverless, the serverless framework~\cite{ref:serverless_framework} contributes on automated packaging and deployment of serverless function on multi-cloud circumstance. Serverless framework uses Cloudformation~\cite{ref:cloudformation} to package and deploy lambda function that generate additional cost, whereas Seneca uses local docker container with no extra cost. Cloud infrastructure provisioning framework terraform~\cite{ref:terraform} also provides automated deployment to serverless platform, but it can not simulate the AWS Lamdba runtime to create deployment package. In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous Integration and delivery pipeline for serverless architecture, but it again generates extra cost.

Automated hyperparameter optimization has been researched and developed in numerous projects. Google Vizier~\cite{ref:vizier} provides a service of black-box optimization. Optunity~\cite{ref:claesen2014hyperparameter} proposes a Python library for hyperparameter tuning. This could be considered as precursory work of Hyperopt~\cite{ref:hyperopt}, which is a more advanced Python library for serial and parallel hyperparameter optimization over awkward search space. Hyperas ~\cite{ref:hyperas} adds another abstraction layer to hyperopt and facilitates the hyperparameter tuning for Keras ~\cite{ref:keras}. However, none of above work ports hyperparameter tuning tasks to serverless platform and evaluates the tuning performance, cost and latency. To the best of our knowledge, Seneca is the first framework contributing in this aspect.

### 2019-02-02 results.tex
mz - Add background, Seneca, related_work

@@
 
-For these applications (XGBoost, SVC, and Neural Network), we consider three
-split scenarios for training and testing: 80\%-20\%, 20\%-80\% and
-0.1\%-99.9\%. As the proportion of training data decreases, the performance of
-classifier degrades accordingly.  However we note that using the optimized
-hyperparameters generated by Seneca, these calssifiers are able to achieve
-accuracy levels similar to those generated from the default parameters, but
-with significantly less training data.
+% For these applications (XGBoost, SVC, and Neural Network), we consider three
+% split scenarios for training and testing: 80\%-20\%, 20\%-80\% and
+% 0.1\%-99.9\%. As the proportion of training data decreases, the performance of
+% classifier degrades accordingly. However we note that using the optimized
+% hyperparameters generated by Seneca, these classifiers are able to achieve
+% accuracy levels similar to those generated from the default parameters, but
+% with significantly less training data.
 
@@
 To evaluate the cost savings introduced by Seneca,
-it on Amazon Web Services (AWS) Lambda~\cite{XXXaws-lambdaXXX} and extract
-execution time and memory use from AWS CloudWatch~\cite{XXXcloudwatchCXXX} logs.  
+it on Amazon Web Services (AWS) Lambda~\cite{ref:awslambda} and extract
+execution time and memory use from AWS CloudWatch~\cite{ref:awscloudwatch} logs.  
 We then compute monetary cost
@@
 Each function downloads the training and testing dataset 
-of the application from AWS Simple Storage Service (S3) upon function invocation. 
+of the application from AWS Simple Storage Service (S3)~\cite{ref:awss3} upon function invocation. 
 We do not consider the cost of dataset storage in our cost computations (it is very small).
@@
 \begin{figure}[t] \centering 
-\includegraphics[scale=0.36]{box_plot_accuracy}
+\vspace{-0.2in}
+\includegraphics[scale=0.36]{box_plot_Accuracy_20}
 \caption{The box plot of accuracy metric from three classification applications for the entire hyperparameter tuning search space.
@@
 \label{fig:box_plot_accuracy}}
-% \vspace{-0.2in}
+\vspace{-0.1in}
 \end{figure}
@@
 \textit{absolute} dollar cost terms.  Even using the maximum memory available
-for almost 25 minutes of execution time (cf Prophet in Table~\ref{XXX}), the
+for almost 25 minutes of execution time (cf Prophet in Table~\ref{tab:cost_max_memory}), the
 total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
@@
 
-Note also that Seneca's memory/cost optimzation
+Note also that Seneca's memory/cost optimization
 introduces at an execution time penalty (relative to the maximum memory
@@
 the expense of execution performance (time to solution).
-The source of this execution performance penalty is not clear.  We hypothesize
-that when requesting a large memory for AWS Lambda, Amazon chooses a machine
-that also has fast processors so the Lambda functions execute more quickly.
-If this supposition is true, then the AWS Lambda pricing model correctly
-weights the cost of additional memory (in light of the reduced execution time)
-because the large-memory executions are still more expensive.
-However regardless of the cause, the Seneca memory optimizer 
-provides a way to trade off time to solution for cost when the highest
-possible application output quality is desired.
+Such penalty is expected due to the proportional CPU power to allocated memory.
+However, Seneca optimizer is able to find the optimal memory configuration to minimize such penalty.
+In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has the same execution time (0.91 minutes).
+% The source of this execution performance penalty is not clear.  We hypothesize
+% that when requesting a large memory for AWS Lambda, Amazon chooses a machine
+% that also has fast processors so the Lambda functions execute more quickly.
+% If this supposition is true, then the AWS Lambda pricing model correctly
+% weights the cost of additional memory (in light of the reduced execution time)
+% because the large-memory executions are still more expensive.
+%However regardless of the cause, 
+Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.
+% \textcolor{blue}{AWS announces the proportional CPU power to memory which is the source of penalty}
 % \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}

### 2019-02-02 Seneca.tex
chandras pass

--- 2019-02-01 Seneca.tex
@@
 
-To facilitate model optimization on serverless architecture, we have developed a cloud service, namely Seneca. The Seneca service pipeline consists of
+To facilitate model optimization on serverless architecture, we have developed Seneca, 
+a framework for tuning the hyperparameters for machine learning applications 
+in AWS Lambda. 
+The Seneca pipeline consists of packaging, deployment, serverless 
+function optimization, and hyperparameter tuning. Figure~\ref{fig:seneca} 
+shows the architecture of Seneca.  In the the upper-right-front, we
+show the three inputs that Seneca expects from its users: a hyperparameter
+configuration file, a dataset URL, and the path to 
+the machine learning application.
+The configuration file
+specifies the range of values for each hyperparameter that the 
+application expects.  Seneca uses this configuration to construct
+the hyperparameter search space.  The dataset URL is a link to a
+valid dataset stored in S3.
+
+Seneca automatically builds and deploys a AWS Lambda application
+from the machine learning application specified.
+To do so, Seneca launches a docker container that mirrors the
+AWS Lambda execution environment, checks and installs
+the machine learning application and any libraries it requires,
+and compresses the application and uploads it to S3 (avoiding
+the AWS Lambda handler size restriction of 10MB).
+Seneca constructs an AWS Lambda handler from a template
+that when executed will download and uncompress the application,
+download the dataset and split it into a training and testing set,
+and construct, test, and evaluate a model using the application
+and a set of hyperparameter values passed in by Seneca as arguments.
+The handler returns a testing score.
+Upon completion of this process, the container deploys the handler
+to AWS Lambda using the
+AWS Command line Interface~\cite{ref:awscli}.
+
+\subsection{Optimizing Memory Use}
+
+The AWS Lambda pricing model is determined by the execution duration 
+and memory. The cost of a function instance is referred to as 
+\texttt{compute charge}, and is calculated as the amont of 
+allocated memory multiplied by the
+billed duration (execution time rounded up to the 
+nearest 100ms)~\cite{awspricing}.
+%https://aws.amazon.com/lambda/pricing/
+To ensure that we keep the cost of Seneca as low as possible, we investigate
+the impact of this pricing model on application execution and use
+our findings to optimize cost.
+
+Currently, allocated memory for a Lambda function can be set
+between 128MB and 3008MB using increments of 64MB.
+AWS documentation~\cite{ref:lambdalimits} states that Lambda 
+allocates CPU to functions in way that is proportional to allocated memory size,
+in the same way as is done for general purpose Amazon EC2 instance types.
+
+\begin{figure}[t] \centering 
+\includegraphics[scale=0.5]{memory}
+\caption{The relationship between allocated memory and reciprocal of billed duration, which represents compute power for a compute-bound Lambda function.
+\label{fig:memory}}
+% \vspace{-0.2in}
+\end{figure}
+
+\begin{figure}[t] \centering 
+\includegraphics[scale=0.5]{compute_charge}
+\caption{The relationship between allocated memory and compute charge for a compute-bound Lambda function.
+\label{fig:compute_charge}}
+% \vspace{-0.2in}
+\end{figure}
+
+To verify such claim, we conduct an experiment in which
+we increase of CPU power and memory for a compute-bound 
+AWS Lambda function (a microbenchmark that performs 3-D matrix multiply~\cite{ref:matrix}).
+We configure function instances to use the 46 possible allocated 
+memory increments, invoke them, and record the billed duration and memory
+use of each.
+Figure~\ref{fig:memory} shows the relationship between allocated memory (x-axis) and reciprocal of billed duration (y-axis). 
+Figure ~\ref{fig:compute_charge} shows the relationship between memory 
+size (x-axis) and compute charge (y-axis). 
+We observe that for this simple benchmark,
+the CPU power plateaus after 1600 MB. 
+Correspondingly, the compute charge declines from 128 MB to 1600 MB 
+and then increases linearly.
+
+These findings show that CPU does not proportionally increase with
+an increase in allocated memory.  We use this relationship within
+Seneca to optimize its cost (compute charge) via an extension
+that enables it to automatically identify the appropriate
+setting for allocated memory for each application.
+However, instead of exhaustively testing all 46 possible 
+memory configurations (increasing its cost), 
+Seneca employs the heuristic outlined in
+Algorithm~\ref{algo:optimizer}.
+
+The Seneca optimizer first configures and invokes the function using 
+a user-defined payload.  From this run, Seneca obtains the memory 
+used by function (reported by AWS Cloudwatch), 
+which it uses as its starting point.
+Seneca then defines two double-end queues 
+(deque) of length N, to store 
+allocated memory and compute charge data of different
+invocations. While the current 
+allocated memory is less than or equal to 3008 MB, 
+the optimizer continues reconfigures and invokes the function 
+using the next increment for memory allocation.  It 
+calculates the compute charge for each invocation 
+using current allocated memory and billed duration.
+
+We employ two exit conditions.  The first is when the 
+compute charge monotonically increases across the length of deque. 
+The second is when the increase in slope is greater than a threshold. 
+Once the optimizer finds that both conditions hold, 
+it pops the left-most value from deque and configures 
+the function to use that value for allocated memory for all future invocations.
+After extensive experimentation, we find that 
+N=5 and a slope threshold of 1 work well in most cases.
+These values can be changed by users of the system however.
+In addition, this optimization can be turned on or off via a command line
+flag when starting Seneca.
+
+\begin{algorithm}[]
+\SetAlgoLined
+\KwData{Typical payload}
+\KwResult{Optimal allocated memory}
+Find memory used by payload as start point\;
+Define deques for struct of allocated memory \& compute charge\;
+ \While{allocated memory $\leq$ 3008 MB}{
+
+  \eIf{compute charge monotonically increase in deque \& slope $\geq$ 1}{
+   Popleft from deque\;
+   Configure allocated memory of function\; 
+   Exit\;
+   }{
+   Increase allocated memory by 64 MB\;
+   Probe lambda function\;
+   Append new struct to deque\;
+  }
+ }
+ \caption{Seneca Optimizer Heuristic}
+ \label{algo:optimizer}
+\end{algorithm}
+
+\subsection{Tuning Process}
+
+For current function invocation, Seneca integrates 
+Celery~\cite{ref:celery}. Celery is an asynchronous task queue 
+that uses distributed message passing. Celery workers are processes 
+that take tasks from the queue, execute tasks, and store the
+result in a database (we use Redis~\cite{ref:redis} in our prototype).
+
+Based on the configuration file, Seneca creates a list of 
+payloads (function arguments) that contains values of 
+hyperparameters.  The complete list contains all combinations of parameter
+settings.  Seneca places the list on the queue and celery 
+workers invoke the Lambda handler of the application, passing in the
+payload to the handler to use for model construction.  Upon function
+termination, the work records the evaluation score (and serialized model)
+in the database with the hyperparameter configuration from the payload.
+When the queue is drained and all workers have completed, Seneca
+extracts and reports the best score and configuration from the database.

### 2019-02-02 intro.tex
mz - Add background, Seneca, related_work
chandras pass

@@
-Serverless~\cite{ref:serverless} computing is a rising function-based (also known as Funtions-as-a-Service~\cite{ref:faas}) programming and deployment paradigm on top of cloud infrastructure, in which programmers manifest business logic without concerning provisioning servers by modular functions that are triggered by incoming events and return computation results in serialized format like XML or JSON.
+The scale and elasticity of cloud computing systems have 
+fueled remarkable innovation and unprecedented commercial 
+investment.  Cloud users ``rent'' virtualized resources (while sharing
+the underlying physical resources) on a pay-per-use basis
+in exchange for availability guarantees specified via service level
+agreements (SLAs). Uniquely, cloud systems can be configured 
+to add and remove resources and services,
+automatically and on-demand, based on load 
+or as required by executing applications.
+
+To date however, cloud use has been limited to large-scale 
+implementations of enterprise services, such as
+object storage, databases, queuing systems, and web and application servers.
+The reason for this is that it is very
+challenging, even for expert users, to configure complex
+distributed systems for application use, 
+and to leverage the elasticity (auto-scaling) that
+clouds offer. To address this challenge, cloud providers 
+have started to offer cloud programming and execution environments
+under the moniker of \textit{serverless} 
+computing~\cite{xxx,yyy,zzz}.  Serverless
+systems automatically configure, manage, and scale applications
+to significantly simplify and broaden participation in (by less expert
+users) the use of cloud systems.
+%xxx: http://shivaram.org/publications/pywren-socc17.pdf
+%yyy: http://cidrdb.org/cidr2019/papers/p119-hellerstein-cidr19.pdf
+%zzz: L. Wang, M. Li, Y. Zhang, T. Ristenpart, and M. Swift. “Peek- ing Behind the Curtains of Serverless Platforms”. In: USENIX ATC. Boston, MA: USENIX Association, 2018
+
+Using the serverless model, applications developers upload 
+arbitrary computations in high level languages
+as stateless functions to these cloud-hosted services, along with a
+specification conditions under which each
+function should be triggered.  Functions are invoked (triggered)
+automatically by the cloud in response to updates to other cloud services
+(e.g. storage, queues, notification services, among others). They
+communicate, persist, and access data only 
+via their inputs or shared, remote storage.  
+As a result, serverless applications are inherently elastic and can 
+implement highly concurrent and parallel tasks.
+In public clouds, users pay a small fee for the resources their 
+functions use during execution, resulting in very low cost cloud use.
+Although now available from all public cloud providers and as open 
+source for private cloud systems, 
+AWS Lambda~\cite{awslambda} was the first and is now the 
+most popular and most advanced serverless public cloud service 
+available today.
+%awslambda: https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf
+
+In this work, we investigate the efficacy of using AWS Lambda
+for tuning machine learning applications.
+To date, Lambda has not be heavily used for training and evaluating
+machine learning models because of a concern that 
+doing so will result in high overhead (i.e. be costly) because
+of the stateless nature of serverless functions~\cite{ref:onesteptwostep}.
+At the same time, identifying the ``best'' configuration for advanced
+machine learning models is challenging given the large number of configuration
+options, i.e., hyperparameters, typical of models today.
+Hyperparameters governs the learning process of machine learning applications.
+Given that parameter sweeps are embarrassingly parallel, we believe
+that such tuning is a good fit for the serverless model.
+To investigate this potential, its overhead, and to simplify the 
+use of Lambda for training, testing, and evaluation machine learning models, 
+we design and develop a new system and toolset called \textit{Seneca}.
+
+Specifically, Seneca implements, packages, and deploys 
+machine learning applications as stateless functions to AWS Lambda.
+It then orchestrates exhaustive evaluation of hyperparameter settings
+to identify the best performing model (for a given dataset) by
+comparing the error and accuracy across models.  Users present
+Seneca with their application, a range of values for 
+each hyperparameter (or the default can be used), and a dataset.
+Seneca produces, tests, and evaluates models for all combinations 
+of hyperparameters and returns to the user, 
+the set of parameters (or the model itself) that produces
+the best cross-validation score (e.g. lowest squared error or highest
+accuracy).
+
+We deploy Seneca on AWS Lambda and evaluate its tuning performance, cost,
+and memory use for six machine learning applications and datasets. We 
+find that Seneca is effective for quickly training these
+models and identifying the best performing hyperparameter setting for 
+these applications. We also find 
+Seneca to be very low cost and able to automatically 
+identify the 
+best memory configuration for each application further lowering its 
+by 10-30\%.
+We intend to make Seneca and the applications available as open source
+when/if this paper is accepted for publication.  In the sections
+that follow, we overview our design and implementation of Seneca and then
+present our empirical methodology and results.
+
+\ignore{
+Recent work~\cite{ref:onesteptwostep} argues however that AWS Lambda
+
+Serverless~\cite{ref:serverless} computing is a rising function-based (also known as Functions-as-a-Service~\cite{ref:faas}) programming and deployment paradigm on top of cloud infrastructure, in which programmers manifest business logic without concerning provisioning servers by modular functions that are triggered by incoming events and return computation results in serialized format like XML or JSON.
 Such events include HTTP requests from clients, possibly proxied by API Gateway, or communications between cloud services based on heterogeneous protocols.
@@
 In a real world case study~\cite{ref:serverless_econ}, the server operational cost on serverless platform could be reduced dramatically, given a relatively lower amount of Transactions Per Second (TPS).
-Based on these four advantages, serverless architecture appropriately serves mid-size stateless application under certain TPS threshold better than virtual machine based clusters.
 According to these merits, the stateless, event-driven and embarrassingly parallel tasks are potentially cost-effective with lower latency by running on serverless framework.
+}

### 2019-02-02 related_work.tex
chandras pass

@@
-In this section, we overview related works and research contributions focusing on serverless computing and model optimization.
+In this section, we overview related work. We discuss contributions that focus
+on serverless computing and machine learning model optimization.
 
-With respect to serverless architecture, the benefit and drawback of such has been well researched by~\cite{ref:onesteptwostep}, in which the authors conduct a case study to show Lambda function can be more expensive than EC2 instances.~\cite{ref:baldini2017} points out serveral open research questions, including the boundaries and statelessness of serverless.
-Furthermore, we were inspired by ~\cite{ref:matrix} to experiment on disproportional CPU power with matrix multiplication application.
+Multiple researchers have investigated the efficacy and overhead of the
+serverless programming model and implementations.
+the benefit and drawback of such has been well researched by
+The authors in \cite{ref:onesteptwostep} evaluates the cost and performance of using
+serverless for data-intensive computing.  They identify some key weaknesses in AWS
+Lambda for this application domain including the inability to effectively train models.
+Our work show that it is possible for a subset of machine learning applications to 
+train models in a cost effective ways.
+\cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
+including whether or not functions should be stateless. 
+%please also discuss and cite these papers - you may need a second paragraph
+%http://www.cs.ucsb.edu/~ckrintz/papers/ic2e18.pdf
+%http://shivaram.org/publications/pywren-socc17.pdf
+%S.
+Fouladi, R.
+S.
+Wahby, B.
+Shacklett, K.
+V.
+Balasubramaniam, W.
+Zeng, R.
+Bhalerao, A.
+Sivaraman, G.
+Porter, and K., Winstein.
+“Encoding, Fast and Slow: Low-Latency Video Pro- cessing Using Thousands of Tiny Threads”.
+In: NSDI.
+Boston, MA: USENIX Association, 2017, pp.
+363–376.
+%A.
+Klimovic, Y.
+Wang, C.
+Kozyrakis, P.
+Stuedi, J.
+Pfefferle, and A.
+Trivedi.
+“Understanding Ephemeral Storage for Serverless Analytics”.
+In: USENIX ATC.
+Boston, MA: USENIX Associa- tion, 2018, pp.
+789–794.
+%. Wang, M. Li, Y. Zhang, T. Ristenpart, and M. Swift. “Peek- ing Behind the Curtains of Serverless Platforms”. In: USENIX ATC. Boston, MA: USENIX Association, 2018, pp. 133–146.
 
-On the tooling of serverless, the serverless framework~\cite{ref:serverless_framework} contributes on automated packaging and deployment of serverless function on multi-cloud circumstance.
-Serverless framework uses Cloudformation~\cite{ref:cloudformation} to package and deploy lambda function that generate additional cost, whereas Seneca uses local docker container with no extra cost.
-Cloud infrastructure provisioning framework terraform~\cite{ref:terraform} also provides automated deployment to serverless platform, but it can not simulate the AWS Lamdba runtime to create deployment package.
-In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous Integration and delivery pipeline for serverless architecture, but it again generates extra cost.
+The serverless framework~\cite{ref:serverless_framework} contributes an 
+automated packaging and deployment toolseet for serverless functions across clouds. 
+The serverless framework uses Cloudformation~\cite{ref:cloudformation} to package and deploy Lambda function, which introduces additional cost. Seneca uses local docker container to avoid this cost
+and overhead. The cloud infrastructure provisioning framework Terraform~\cite{ref:terraform} 
+also provides automated deployment of functions to serverless platforms, but it does not simulate the AWS Lamdba runtime to create the deployment package (doing so on a non-Linux system will result in Lambda errors and failures at execution time).
+In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous integration and delivery pipeline for serverless architectures, but it also introduces monetary cost overhead
+to do so.
 
-Automated hyperparameter optimization has been researched and developed in numerous projects.
-Google Vizier~\cite{ref:vizier} provides a service of black-box optimization.
-Optunity~\cite{ref:claesen2014hyperparameter} proposes a Python library for hyperparameter tuning.
-This could be considered as precursory work of Hyperopt~\cite{ref:hyperopt}, which is a more advanced Python library for serial and parallel hyperparameter optimization over awkward search space.
-Hyperas ~\cite{ref:hyperas} adds another abstraction layer to hyperopt and facilitates the hyperparameter tuning for Keras ~\cite{ref:keras}.
-However, none of above work ports hyperparameter tuning tasks to serverless platform and evaluates the tuning performance, cost and latency.
-To the best of our knowledge, Seneca is the first framework contributing in this aspect.
+Automated hyperparameter optimization has been researched and developed 
+in numerous projects. Google Vizier~\cite{ref:vizier} provides a service for 
+black-box optimization. Optunity~\cite{ref:claesen2014hyperparameter} 
+proposes a Python library for hyperparameter tuning. 
+This can be considered as precursory work of Hyperopt~\cite{ref:hyperopt}, 
+which is a more advanced Python library for serial and parallel hyperparameter 
+optimization over awkward search space. Hyperas ~\cite{ref:hyperas} adds another 
+abstraction layer to hyperopt and facilitates the hyperparameter tuning for 
+Keras ~\cite{ref:keras}. However, no extant work of which we are aware leverages
+serverless to perform hyperparameter tuning in parallel.

### 2019-02-02 results.tex
chandras pass

@@
 \centering
-\scriptsize
-\resizebox{\columnwidth}{!}{
+%\scriptsize
+%\resizebox{\columnwidth}{!}{
 \begin{tabular}{|l|l|} \hline
@@
 \hline
-\end{tabular}}
+\end{tabular}
+%}
 \caption{Machine learning applications used as benchmarks
@@
 
-%%The hyperparameters that Prophet expects are 
-%%\textcolor{blue}{Describe what these are in a couple of sentences.}
-%%In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
-%%the application or that are defined by the application developer) for each application.  
-%%The default parameters for this application are
-%%\textcolor{blue}{Describe them here.}
-%%The application computes mean square error of
-%%\textcolor{blue}{finish this here.}
-
 Prophet expects multiple hyperparameters: \textit{growth} specifies linear or logistic trend model growth; \textit{prior scale} indicates the strength of the 
@@
 multiplicative or additive. Finally, the width of uncertainty intervals 
-can be set using the hyperparameter \textit{interval width}.
+is set using \textit{interval width}.
 
-% \textcolor{blue}{Describe what these are in a couple of sentences.}
 In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
@@
 \centering
-\scriptsize
-\resizebox{\columnwidth}{!}{
+%\scriptsize
+%\resizebox{\columnwidth}{!}{
 \begin{tabular}{|l|l|l|} 
@@
 \hline
-\end{tabular}}
-\caption{The selected configurable hyperparameters of Prophet. The default value and tuning options are listed. 
+\end{tabular}
+%}
+\caption{The hyperparameters that Seneca considers for Prophet. 
+The default value and tuning options are listed. 
 \label{tab:prophet_para}}
+%\vspace{-0.2in}
+\end{table}
+
+\begin{table}[t]
+\centering
+%\scriptsize
+\input{hparams-xgboost-tab}
+\caption{The hyperparameters that Seneca considers for XGBoost. 
+The default value and tuning options are listed. 
+\label{tab:xgboost_para}}
+%\vspace{-0.2in}
+\end{table}
+
+\begin{table}[t]
+\centering
+%\scriptsize
+\input{hparams-svc-tab}
+\caption{The hyperparameters that Seneca considers for SVC. 
+The default value and tuning options are listed. 
+\label{tab:svc_para}}
+%\vspace{-0.2in}
+\end{table}
+
+\begin{table}[t]
+\centering
+%\scriptsize
+\input{hparams-nn-tab}
+\caption{The hyperparameters that Seneca considers for NN.
+The default value and tuning options are listed. 
+\label{tab:nn_para}}
 %\vspace{-0.2in}
@@
 a classification application in this evaluation.  
+The hyperparmeters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{xgboostparams}.
+%xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
 Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
 based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
+The hyperparmeters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{xvcparams}.
+%xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
 Neural network~\cite{ref:neural_network} is a machine learning framework that learns 
@@
 for the classification task.
+The hyperparmeters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{nnparams}.
+%nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html
 
@@
 data.  They then use this model to predict the field
-%%<<<<<<< HEAD %from which each fruit originates.  They compute classification
-%accuracy %as \textcolor{blue}{finish this.}.  XGBoost also computes MSE for
-%its regression task %on the same datasets.  The dataset has been filtered
-%authors to remove correlated %features (those with an absolute value of the
-%Pearson correlation coefficient greater than 0.8).  %The resulting dataset
-%contains 218150 rows (individual fruit) each with 19 features. 
 from which each fruit originates. They compute classification accuracy score

### 2019-02-02 Seneca.tex
chandras pass

@@
 and a set of hyperparameter values passed in by Seneca as arguments.
+Users can specify the train/test split that should be used by Seneca; the
+default is 80\%/20\% for classification tasks.
 The handler returns a testing score. 
@@
 
-For current function invocation, Seneca integrates 
+For parallel function invocation, Seneca integrates 
 Celery~\cite{ref:celery}. Celery is an asynchronous task queue 
 that uses distributed message passing. Celery workers are processes 
-that take tasks from the queue, execute tasks, and store the
-result in a database (we use Redis~\cite{ref:redis} in our prototype).
+that take tasks from the queue, execute the tasks with the auguments specified, 
+and store the result that is returned 
+in a database (we use Redis~\cite{ref:redis} in our prototype).
 
@@
 payloads (function arguments) that contains values of 
-hyperparameters.  The complete list contains all combinations of parameter
+hyperparameters.  The complete list contains all combinations of the
+specified parameter
 settings.  Seneca places the list on the queue and celery 
 workers invoke the Lambda handler of the application, passing in the
-payload to the handler to use for model construction.  Upon function
+payload (hyperparameter values) to the handler to use for model construction.  
+Upon function
 termination, the work records the evaluation score (and serialized model)
@@
 When the queue is drained and all workers have completed, Seneca
-extracts and reports the best score and configuration from the database.
+extracts and reports the best score, configuration, and model from the database.
+Users can then evaluate the prediction power of the models (using Seneca if desired) 
+for other datasets (to amortize the time/cost of Seneca) without retraining.
+
+We assume that the dataset supplied to Seneca by the user
+is representative of datasets on which the 
+resulting model will be use.  In addition, we use prediction error as the 
+score (i.e., mean squared error for regression and accuracy percentage for classification) 
+instead of $R^2$, which describes explanatory power, to avoid overfitting.
+As part of future work, we are considering using multiple datasets and a ranges
+of hyperparameter values (versus lists) to preclude the need for users to specify
+them and to consider a wider range of possible values.

### 2019-02-02 intro.tex
chandras pass

@@
 options, i.e., hyperparameters, typical of models today.
-Hyperparameters governs the learning process of machine learning applications.
+Hyperparameters govern the learning process of machine learning applications.
 Given that parameter sweeps are embarrassingly parallel, we believe
@@
 to identify the best performing model (for a given dataset) by
-comparing the error and accuracy across models.  Users present
-Seneca with their application, a range of values for 
-each hyperparameter (or the default can be used), and a dataset.
+comparing the error and accuracy across models.  We consider
+prediction accuracy (as opposed to explanatory power) as the
+scoring metric (mean squared error for regression 
+and accuracy percent for classification), to avoid overfitting.
+Users present Seneca with their application, a range of values for 
+each hyperparameter (or the default can be used), and a representative dataset.
 Seneca produces, tests, and evaluates models for all combinations 
-of hyperparameters and returns to the user, 
+of hyperparameters and returns to the user
 the set of parameters (or the model itself) that produces
 the best cross-validation score (e.g. lowest squared error or highest
-accuracy).
+accuracy) for the dataset. Users can employ this model for other datasets
+(with Seneca if desired) without retraining the model to amortize the cost
+of Seneca further.
 
@@
 by 10-30\%.
+As such, Seneca greatly simplifies model construction and comparison and 
+does so with very low latency and at very low cost.
 We intend to make Seneca and the applications available as open source

### 2019-02-02 results.tex
chandras pass

@@
 \hline
-Neural Network& Classification by layered artificial neural network\\
+NN& Classification by layered artificial neural network\\
 \hline
@@
 \label{tab:bmarks}}
-%\vspace{-0.2in}
+\vspace{-0.2in}
 \end{table}
@@
 In this section,
-we evaluate Seneca in terms of performance, monetary cost, and hyperparameter tuning time (latency), 
-using machine learning applications that we ported to Seneca (i.e. that we implemented
-as lambda functions). 
+we evaluate Seneca in terms of performance, monetary cost, 
+and hyperparameter tuning time (latency), 
+for different machine learning applications.
 We first overview these applications and our empirical methodology. 
 We then present our experimental results.
+
+\begin{table}[t]
+\centering
+\scriptsize
+%\resizebox{\columnwidth}{!}{
+\begin{tabular}{|l|l|l|} 
+\hline
+\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
+\hline
+grow & linear & [linear, logistic] \\
+\hline
+changepoint prior scale & 0.05 & [0.05, 0.5] \\
+\hline
+holidays prior scale & 10 & [1, 5, 10] \\
+\hline
+seasonality prior scale & 0.5 & [0.1, 0.5] \\
+\hline
+fourier order & 10 & [5, 10, 15, 20] \\
+\hline
+seasonality mode & additive & [additive, multiplicative] \\
+\hline
+interval width & 0.8 & [0.5, 0.8] \\
+\hline
+\end{tabular}
+%}
+\caption{The hyperparameters that Seneca considers for Prophet. 
+The default value and tuning options are listed. 
+\label{tab:prophet_para}}
+\vspace{-0.2in}
+\end{table}
+
+\begin{table}[t]
+\centering
+\scriptsize
+\input{hparams-xgboost-tab}
+\caption{The hyperparameters that Seneca considers for XGBoost. 
+The default value and tuning options are listed. 
+\label{tab:xgboost_para}}
+\vspace{-0.2in}
+\end{table}
+
+\begin{table}[t]
+\centering
+\scriptsize
+\input{hparams-svc-tab}
+\caption{The hyperparameters that Seneca considers for SVC. 
+The default value and tuning options are listed. 
+\label{tab:svc_para}}
+\vspace{-0.2in}
+\end{table}
+
+\begin{table}[t]
+\centering
+\scriptsize
+\input{hparams-nn-tab}
+\caption{The hyperparameters that Seneca considers for NN.
+The default value and tuning options are listed. 
+\label{tab:nn_para}}
+\vspace{-0.2in}
+\end{table}
 
@@
 the application or that are defined by the application developer) for each application.  
-The default parameters and tuning options for this application are listed in the table~\ref{tab:prophet_para}.
+The default parameters and tuning options for Prophet are listed in the table~\ref{tab:prophet_para}.
 For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points.
@@
 Based on the model trained by default parameter setting, this average MSE metric is 0.284.
-
-\begin{table}[t]
-\centering
-%\scriptsize
-%\resizebox{\columnwidth}{!}{
-\begin{tabular}{|l|l|l|} 
-\hline
-\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
-\hline
-grow & linear & [linear, logistic] \\
-\hline
-changepoint prior scale & 0.05 & [0.05, 0.5] \\
-\hline
-holidays prior scale & 10 & [1, 5, 10] \\
-\hline
-seasonality prior scale & 0.5 & [0.1, 0.5] \\
-\hline
-fourier order & 10 & [5, 10, 15, 20] \\
-\hline
-seasonality mode & additive & [additive, multiplicative] \\
-\hline
-interval width & 0.8 & [0.5, 0.8] \\
-\hline
-\end{tabular}
-%}
-\caption{The hyperparameters that Seneca considers for Prophet. 
-The default value and tuning options are listed. 
-\label{tab:prophet_para}}
-%\vspace{-0.2in}
-\end{table}
-
-\begin{table}[t]
-\centering
-%\scriptsize
-\input{hparams-xgboost-tab}
-\caption{The hyperparameters that Seneca considers for XGBoost. 
-The default value and tuning options are listed. 
-\label{tab:xgboost_para}}
-%\vspace{-0.2in}
-\end{table}
-
-\begin{table}[t]
-\centering
-%\scriptsize
-\input{hparams-svc-tab}
-\caption{The hyperparameters that Seneca considers for SVC. 
-The default value and tuning options are listed. 
-\label{tab:svc_para}}
-%\vspace{-0.2in}
-\end{table}
-
-\begin{table}[t]
-\centering
-%\scriptsize
-\input{hparams-nn-tab}
-\caption{The hyperparameters that Seneca considers for NN.
-The default value and tuning options are listed. 
-\label{tab:nn_para}}
-%\vspace{-0.2in}
-\end{table}
 
@@
 series of processor temperature measurements,
-to predict outdoor microclimate temperatures (e.g. for use in 
-precision agriculture applications such as irrigation control and frost protection).
+to predict outdoor microclimate temperatures without using a temperature sensor.
+%(e.g. for use in 
+%precision agriculture applications such as irrigation control and frost protection).
 The training dataset consists of eight input time series (one per SBC, each containing 
@@
 For this application,
-we assume the default parameterization is the set of all $N$ input time series (8 in this case).
+we assume the default parameterization is the full set of input time series (8 in this case).
 The test dataset for this application is a time series of the outdoor temperature (ground truth) 
@@
 based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
-The hyperparmeters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{xvcparams}.
+The hyperparmeters and their defaults that Seneca uses for SVC are listed in Table~\ref{tab:svc_para}. A description of each hyperparameter can be found at~\cite{xvcparams}.
 %xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
-Neural network~\cite{ref:neural_network} is a machine learning framework that learns 
+Neural network (NN)~\cite{ref:neural_network} is a machine learning framework that learns 
 and make decisions from patterns in an input dataset. For this application, 
@@
 for the classification task.
-The hyperparmeters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{nnparams}.
+The hyperparmeters and their defaults that Seneca uses for NN are listed in Table~\ref{tab:nn_para}. A description of each hyperparameter can be found at~\cite{nnparams}.
 %nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html
 
-For these applications (XGBoost, SVC, and Neural Network), we use a labeled
+For these applications (XGBoost, SVC, and NN), we use a labeled
 dataset for training, testing, and evaluation from this
@@
 characteristics, for each fruit.  The label indicates which field the fruit
-was harvested from.  The applications train a model on a random subset of the
+was harvested from.  The applications train a model on a subset of the
 data.  They then use this model to predict the field
-from which each fruit originates. They compute classification accuracy score
+from which each fruit originates. For this study we use the same random 80\%
+subset of the dataset as the training dataset.  We use the remaining 20\% as the
+testing dataset.
+
+These applications compute classification accuracy score
 as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
-prediction class, $Y_i$ is the true class, n is the number of samples and 1(x)
+prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
 is the indicator function. XGBoost also computes MSE for its regression task
@@
 %Seneca downloads the dataset from AWS S3 for each function invocation.
-%It then randomly indexes the data set and splits it into two.
+%It then randomly indexes the dataset and splits it into two.
 
-% For these applications (XGBoost, SVC, and Neural Network), we consider three
+% For these applications (XGBoost, SVC, and NN), we consider three
 % split scenarios for training and testing: 80\%-20\%, 20\%-80\% and
@@
 and monetary cost.  For tuning performance, we use mean squared error (MSE)
-for regression tasks and percentage accuracy for classification tasks. The
-default configuration that we consider for each application is described
+for regression tasks and percentage accuracy for classification tasks (i.e. we score
+model prediction accuracy and not explanatory power).  Because we use the name 
+total number of hyperparameters for each model, the penalty function in terms of 
+Bayesian Information Criteria, is the same. Thus, we can compare models using
+this score.
+
+The default configuration that we consider for each application is described
 above.  We report results for the default, best (Seneca's recommendation), and
@@
 poorly tuned.  Finally, the best is the upper bound on what is possible from
-tuning the hyperparameters (e.g. using expert knowledge or Seneca).
+tuning the hyperparameters for the values and dataset specified 
+(e.g. using expert knowledge or Seneca).
 
-To evaluate the cost savings introduced by Seneca,
-it on Amazon Web Services (AWS) Lambda~\cite{ref:awslambda} and extract
+To evaluate the cost savings introduced by Seneca, we deploy the applications
+on Amazon Web Services (AWS) Lambda~\cite{ref:awslambda} and extract
 execution time and memory use from AWS CloudWatch~\cite{ref:awscloudwatch} logs.  
@@
 \label{tab:mse}}
+\vspace{-0.2in}
 \end{table}
@@
 \begin{figure}[t] \centering 
+\vspace{-0.2in}
 \includegraphics[scale=0.36]{box_plot_mse_2}
+\vspace{-0.2in}
 \caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space.
@@
 \label{fig:box_plot_mse}}
-%\vspace{-0.2in}
+\vspace{-0.2in}
 \end{figure}
@@
 MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
-for each regression algorithm and data set.
+for each regression algorithm and dataset.
 
@@
 performance is congruent with the end of the lower whisker.  Overall, however,
-the quality of the application's output (for a given data set) is dramatically
+the quality of the application's output (for a given dataset) is dramatically
 affected by hyperparameter settings.  Perdictably the default settings are
@@
 We next empirically evaluate the tuning performance of Seneca for the three
-classification applications: XGBoost (classification), SVC, and Neural
-Network.  Table~\ref{tab:accuracy} presents the accuracy percentage (higher is
+classification applications: XGBoost (classification), SVC, and NN.
+Table~\ref{tab:accuracy} presents the accuracy percentage (higher is
 better) reported by each application (3 right-most columns) for the default,
-worst, and best hyperparameter tuning configurations under three training and
-testing split scenarios reported by Seneca.  In the 80/20 percent split case,
+worst, and best hyperparameter tuning configurations reported by Seneca.
+using an 80/20 (train/test) percent split,
 Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost
-(classification), SVC, and Neural Network applications, respectively.  Verses
+(classification), SVC, and NN applications, respectively.  Verses
 the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%,
@@
 \hline
-\textbf{80\%-20\%} & XGBoost & SVC & Neural Network\\
+\textbf{80\%-20\%} & XGBoost & SVC & NN\\
 \hline
@@
 %\hline
-%\textbf{20\%-80\%} & XGBoost & SVC & Neural Network\\
+%\textbf{20\%-80\%} & XGBoost & SVC & NN\\
 %\hline
@@
 %\hline
-%\textbf{0.1\%-99.9\%} & XGBoost & SVC & Neural Network\\
+%\textbf{0.1\%-99.9\%} & XGBoost & SVC & NN\\
 %\hline
@@
 \label{tab:accuracy}}
-%\vspace{-0.2in}
+\vspace{-0.2in}
 %\end{figure}
@@
 
+The 80-20 case represents the typical usage of these classification
+applications.  Often, when evaluating the accuracy of a specific classifier,
+the user uses the 80-20 split ``rule'' when measuring accuracy.  In this case,
+Seneca's improvement over the default parameterizations varies from less than
+1\% for the Neural Network (NN) application (column 4 for 80-20), to 61.5\% for SVC
+(best versus default in column 3 for 80-20 in the table).
+
 \begin{figure}[t] \centering 
-\vspace{-0.2in}
 \includegraphics[scale=0.36]{box_plot_Accuracy_20}
+\vspace{-0.4in}
 \caption{The box plot of accuracy metric from three classification applications for the entire hyperparameter tuning search space.
@@
 
-The 80-20 case represents the typical usage of these classification
-applications.  Often, when evaluating the accuracy of a specific classifier,
-the user uses the 80-20 split ``rule'' when measuring accuracy.  In this case,
-Seneca's improvement over the default parameterizations varies from less than
-1\% for the Neural Network application (column 4 for 80-20), to 61.5\% for SVC
-(best versus default in column 3 for 80-20 in the table).
-
 Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
@@
 improves tuning performance over the default and worst case configurations for 
-XGBoost and SVC while generating only a slight improvement over default for
-Neural Network.
+XGBoost and SVC while generating only a small improvement over default for NN.
 
@@
 \label{tab:cost_max_memory}}
-%\vspace{-0.2in}
+\vspace{-0.2in}
 \end{table}
@@
 \label{tab:cost_optimized}}
-%\vspace{-0.2in}
+\vspace{-0.2in}
 \end{table}

### 2019-02-02 Seneca.tex
mz - Add more paper discussion to related work

--- 2019-02-02 Seneca.tex
@@
 billed duration (execution time rounded up to the 
-nearest 100ms)~\cite{awspricing}.
+nearest 100ms)~\cite{ref:pricing}.
 %https://aws.amazon.com/lambda/pricing/

### 2019-02-02 intro.tex
mz - Add more paper discussion to related work

--- 2019-02-02 intro.tex
@@
 under the moniker of \textit{serverless} 
-computing~\cite{xxx,yyy,zzz}.  Serverless
+computing~\cite{ref:jonas2017occupy, ref:onesteptwostep, ref:peeking}.  Serverless
 systems automatically configure, manage, and scale applications
@@
 source for private cloud systems, 
-AWS Lambda~\cite{awslambda} was the first and is now the 
+AWS Lambda~\cite{ref:awslambdadg} was the first and is now the 
 most popular and most advanced serverless public cloud service 

### 2019-02-02 related_work.tex
mz - Add more paper discussion to related work

@@
 \cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
-including whether or not functions should be stateless. 
+including whether or not functions should be stateless. PyWren~\cite{ref:jonas2017occupy} provides us 
+a new perspective of stateless function being a natural fit for distributed computing models, because it 
+abstract away cluster management overhead from running embarrassingly parallel jobs. ExCamera~\cite{ref:encoding}
+ exemplifies a framework running general-purpose parallel tasks (encoding 4K video) on commercial serverless platform 
+by multithreading. An empirical measurement study has been conducted in~\cite{ref:peeking} across AWS Lambda, 
+Azure Functions and Google Cloud Functions to discuss the resource utilization and performance isolation efficiency of 
+three platforms. Besides efficacy and efficiency, there are challenges serverless architecture are facing in terms of 
+application monitoring and distributed storage. GammaRay~\cite{ref:lin2018tracking} proposes a cloud service that extracts
+causal dependencies across serverless functions and cloud services without programmer intervention. Such monitoring and 
+debugging tool simplifies the development and maintenance of serverless applications. Pocket~\cite{ref:ephemeral} provides 
+an elastic and economical distributed data store for severless analytic applications. We expect more contributions to toolchain 
+and distributed storage of serverless in upcoming years.
+
 %please also discuss and cite these papers - you may need a second paragraph
@@
 The serverless framework~\cite{ref:serverless_framework} contributes an 
-automated packaging and deployment toolseet for serverless functions across clouds. 
+automated packaging and deployment toolset for serverless functions across clouds. 
 The serverless framework uses Cloudformation~\cite{ref:cloudformation} to package and deploy Lambda function, which introduces additional cost. Seneca uses local docker container to avoid this cost

### 2019-02-02 results.tex
mz - Add more paper discussion to related work

--- 2019-02-02 results.tex
@@
 a classification application in this evaluation.  
-The hyperparmeters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{xgboostparams}.
+The hyperparmeters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{ref:xgboostparams}.
 %xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
@@
 based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
-The hyperparmeters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{xvcparams}.
+The hyperparmeters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{ref:svcparams}.
 %xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
@@
 for the classification task.
-The hyperparmeters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{nnparams}.
+The hyperparmeters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{ref:nnparams}.
 %nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html

### 2019-02-02 abstract.tex

@@
-The involvement of manual operations and domain expertise makes traditional model optimization process expensive, time-consuming and not guaranteed the optimal solution.
+The goal of our work is to simplify and expedite the 
+construction and evaluation of machine learning models 
+using autoscaled cloud computing systems and services.
+To enable this, we develop an open source system, called Seneca, that leverages
+the serverless programming model and its implementation in Amazon Web Services
+(AWS) Lambda.  
+Seneca takes a machine learning application, dataset, and a list of 
+possible hyperparameter options.  It automatically constructs an AWS Lambda
+handler that invokes the application, ingresses and splits the dataset into training
+and testing portions, and constructs, tests, and evaluates (i.e. scores) a machine
+learning model for a given set of hyperparameter values.  Seneca orchestrates
+this execution in parallel for all possible combinations of the hyperparameters specified.
+It then returns the configuration (and model) that results in the best score 
+to the user.
+
+We present the design and implementation of Seneca and introduce an extension to the
+system that automaticallly optimizes memory use by the functions.  
+Our empirical evaluation using
+multiple machine learning applications for regression and classification (using
+the models for prediction and not explanatory value), shows that Seneca is able to quickly
+identify the best performing model,
+for the datasets and algorithms that we study. 
+Moreover, our memory optimization reduces the cost of using
+Seneca by 10-30\% for the applications studied.
+
+%The involvement of manual operations and domain expertise makes traditional model optimization process expensive, time-consuming and not guaranteed the optimal solution.
 The emergence of serverless computing offers the potential to optimize models in an auto-scaling and micro-billing fashion.

### 2019-02-02 conclusion.tex

In this paper, we present Seneca, a new framework for simplifying and expediting
the training and testing of machine learning models in terms of their prediction 
power using very low cost cloud computing services.
Specifically, Seneca leverages the AWS Lambda serverless cloud service for autoscaled
(elastic) and parallel execution of hyperparameter search and selection for machine learning
applications.  
Users provide Seneca with the application code and libraries, 1+ datasets, and the list 
of possible hyperparameter settings.  Seneca uses this 
information to automatically construct an AWS Lambda function that
that invokes the application, imports and splits the dataset into training
and testing datasets, and constructs, tests, and evaluates (i.e. scores) a machine
learning model for a particular configuration of hyperparameter settings.  
Seneca orchestrates parallel execution of these functions for all possible 
combinations of hyperparameter values specified and returns the best scoring model
and configuration to the user (for future use on other datasets).

We present the design, implementation, and cost optimization for Seneca.
The optimization automaticallly optimizes function memory use to reduce the cost
of AWS Lambda use.  Our empirical evaluation using
multiple applications for regression and classification (using
the models for prediction and not explanitory value), shows that Seneca is able to quickly
identify the best performing model for the applications and datasets that we consider.  
We also show that Seneca memory optimization reduces the cost of using
Seneca by 10-30\% for the applications studied.

### 2019-02-02 results.tex

--- 2019-02-02 results.tex
@@
 based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
-The hyperparmeters and their defaults that Seneca uses for SVC are listed in Table~\ref{tab:svc_para}. A description of each hyperparameter can be found at~\cite{xvcparams}.
+The hyperparmeters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{ref:svcparams}.
 %xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
@@
 for the classification task.
-The hyperparmeters and their defaults that Seneca uses for NN are listed in Table~\ref{tab:nn_para}. A description of each hyperparameter can be found at~\cite{nnparams}.
+The hyperparmeters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{ref:nnparams}.
 %nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html

### 2019-02-02 Seneca.tex
chandras pass

@@
 of hyperparameter values (versus lists) to preclude the need for users to specify
-them and to consider a wider range of possible values.
+them and to consider a wider range of values.

### 2019-02-02 conclusion.tex
chandras pass

@@
-In this paper, we present Seneca, a new framework for simplifying and expediting
-the training and testing of machine learning models in terms of their prediction 
-power using very low cost cloud computing services.
-Specifically, Seneca leverages the AWS Lambda serverless cloud service for autoscaled
-(elastic) and parallel execution of hyperparameter search and selection for machine learning
-applications.  
+We present a new framework, called Seneca, for simplifying and expediting
+the training and testing of machine learning models
+using low cost cloud services.
+Specifically, Seneca leverages the AWS Lambda for autoscaled
+(elastic) and parallel execution of hyperparameter search 
+and selection for machine learning models.  
 Users provide Seneca with the application code and libraries, 1+ datasets, and the list 
-of possible hyperparameter settings.  Seneca uses this 
-information to automatically construct an AWS Lambda function that
-that invokes the application, imports and splits the dataset into training
-and testing datasets, and constructs, tests, and evaluates (i.e. scores) a machine
-learning model for a particular configuration of hyperparameter settings.  
-Seneca orchestrates parallel execution of these functions for all possible 
+of possible hyperparameter settings.  
+%Seneca uses this 
+%information to automatically construct models using parallel functions in AWS Lambda. 
+%an AWS Lambda function that
+%that invokes the application, imports and splits the dataset into training
+%and testing datasets, and constructs, tests, and evaluates (i.e. scores) a machine
+%learning model for a particular configuration of hyperparameter settings.  
+Seneca uses this information to orchestrate parallel execution of these functions for all possible 
 combinations of hyperparameter values specified and returns the best scoring model

### 2019-02-02 related_work.tex
chandras pass

--- 2019-02-02 related_work.tex
@@
 Multiple researchers have investigated the efficacy and overhead of the
-serverless programming model and implementations.
-the benefit and drawback of such has been well researched by
+serverless programming model and 
+implementations~\cite{ref:baldini2017,ref:jonas2017occupy,ref:onesteptwostep,ref:lin2018tracking}.
 The authors in \cite{ref:onesteptwostep} evaluates the cost and performance of using
@@
 Lambda for this application domain including the inability to effectively train models.
-Our work show that it is possible for a subset of machine learning applications to 
-train models in a cost effective ways.
-\cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
-including whether or not functions should be stateless. 
+Our work show that it is possible for the subset of machine learning applications that we 
+consider, to train models in a cost effective ways.
+
+%\cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
+%including whether or not functions should be stateless. PyWren~\cite{ref:jonas2017occupy} provides us 
+a new perspective of stateless function being a natural fit for distributed computing models, because it 
+abstracts away cluster management overhead and is ideal for embarrassingly parallel jobs. 
+ExCamera~\cite{ref:encoding} presents a 
+framework for running general-purpose parallel tasks (encoding 4K video) 
+on a commercial serverless platform using multithreading. 
+An empirical comparison of resource utilization and performance isolation
+is provided in~\cite{ref:peeking} for AWS Lambda, 
+Azure Functions, and Google Cloud Functions.
+%to discuss the resource utilization and performance isolation efficiency of 
+%three platforms. Besides efficacy and efficiency, there are challenges serverless architecture are facing in terms of 
+%application monitoring and distributed storage. GammaRay~\cite{ref:lin2018tracking} proposes a cloud service that extracts
+%causal dependencies across serverless functions and cloud services without programmer intervention. Such monitoring and 
+%debugging tool simplifies the development and maintenance of serverless applications. Pocket~\cite{ref:ephemeral} provides 
+%an elastic and economical distributed data store for severless analytic applications. We expect more contributions to toolchain 
+%and distributed storage of serverless in upcoming years.
+
 %please also discuss and cite these papers - you may need a second paragraph

### 2019-02-02 results.tex
chandras pass

@@
 \includegraphics[scale=0.36]{box_plot_mse_2}
-\vspace{-0.2in}
+\vspace{-0.4in}
 \caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space.
@@
 regressions generated by Prophet, Multi-regression, and XGBoost (when used as
-a regression algorithm). The first row of the table indicates the number of
+a regression algorithm). The first row indicates the number of
 different hyperparameter settings Senica considered.  Rows 3 through 5 show
-the MSE generated by the default hytperparameter settings, the best (lowest
+the MSE generated by the default hyperparameter settings, the best (lowest
 MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
@@
 Seneca's improvement over the default parameterizations varies from less than
-1\% for the Neural Network (NN) application (column 4 for 80-20), to 61.5\% for SVC
-(best versus default in column 3 for 80-20 in the table).
+1\% for the Neural Network (NN) application (column 4), to 61.5\% for SVC
+(best versus default in column 3).
 

### 2019-02-02 Seneca.tex
mz - update Seneca.png

@@
 and memory. The cost of a function instance is referred to as 
-\texttt{compute charge}, and is calculated as the amont of 
+\texttt{compute charge}, and is calculated as the amount of 
 allocated memory multiplied by the
@@
 we increase of CPU power and memory for a compute-bound 
-AWS Lambda function (a microbenchmark that performs 3-D matrix multiply~\cite{ref:matrix}).
+AWS Lambda function (a microbenchmark that performs 3-D matrix multiplication~\cite{ref:matrix}).
 We configure function instances to use the 46 possible allocated 
@@
 Find memory used by payload as start point\;
-Define deques for struct of allocated memory \& compute charge\;
+Define deques for allocated memory \& compute charge\;
  \While{allocated memory $\leq$ 3008 MB}{
@@
   \eIf{compute charge monotonically increase in deque \& slope $\geq$ 1}{
-   Popleft from deque\;
+   Popleft from deques\;
    Configure allocated memory of function\; 
@@
    Probe lambda function\;
-   Append new struct to deque\;
+   Append allocated memory and compute charge to deques\;
   }

### 2019-02-03 related_work.tex
mz - small tweaks and typos

@@
 serverless programming model and 
-implementations~\cite{ref:baldini2017,ref:jonas2017occupy,ref:onesteptwostep,ref:lin2018tracking}.
+implementations~\cite{ref:jonas2017occupy,ref:onesteptwostep, ref:baldini2017,ref:lin2018tracking}.
 The authors in \cite{ref:onesteptwostep} evaluates the cost and performance of using
@@
 %\cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
-%including whether or not functions should be stateless. PyWren~\cite{ref:jonas2017occupy} provides us 
+including whether or not functions should be stateless. PyWren~\cite{ref:jonas2017occupy} provides us 
 a new perspective of stateless function being a natural fit for distributed computing models, because it 
@@
 which is a more advanced Python library for serial and parallel hyperparameter 
-optimization over awkward search space. Hyperas ~\cite{ref:hyperas} adds another 
+optimization over awkward search space. Hyperas~\cite{ref:hyperas} adds another 
 abstraction layer to hyperopt and facilitates the hyperparameter tuning for 
-Keras ~\cite{ref:keras}. However, no extant work of which we are aware leverages
+Keras~\cite{ref:keras}. However, no extant work of which we are aware leverages
 serverless to perform hyperparameter tuning in parallel.

### 2019-02-03 results.tex
mz - update Seneca.png
mz - small tweaks and typos

@@
 \label{tab:xgboost_para}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}
@@
 for regression tasks and percentage accuracy for classification tasks (i.e. we score
-model prediction accuracy and not explanatory power).  Because we use the name 
+model prediction accuracy and not explanatory power).  Because we use the same 
 total number of hyperparameters for each model, the penalty function in terms of 
@@
 first quartile value in all three cases (slightly greater that Q1 for Prophet
-and Multi-regression and slight less for XGBoost).  However Seneca's MSE
+and Multi-regression and slight less for XGBoost). However, Seneca's MSE
 performance is congruent with the end of the lower whisker.  Overall, however,
@@
 %present empirically evaluate both in this subsection.  
-Note that XGBoost's performance profile is identical when used for reghression
+Note that XGBoost's performance profile is identical when used for regression
 or classification so we include its measurements only once in the following
@@
 \label{tab:cost_max_memory}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}

### 2019-02-03 Seneca.tex
A number of minor fixes to improve clarity and some spelling fixes.

@@
 Seneca constructs an AWS Lambda handler from a template
-that when executed will download and uncompress the application,
+that, when executed, will download and uncompress the application,
 download the dataset and split it into a training and testing set,
@@
 
-To verify such claim, we conduct an experiment in which
+To verify that assertion, we conduct an experiment in which
 we increase of CPU power and memory for a compute-bound 
@@
 However, instead of exhaustively testing all 46 possible 
-memory configurations (increasing its cost), 
+memory configurations, which might be costly,  
 Seneca employs the heuristic outlined in
@@
 is representative of datasets on which the 
-resulting model will be use.  In addition, we use prediction error as the 
+resulting model will be used.  In addition, we use prediction error as the 
 score (i.e., mean squared error for regression and accuracy percentage for classification) 

### 2019-02-03 related_work.tex
mz - comments on related work
A number of minor fixes to improve clarity and some spelling fixes.

@@
 implementations~\cite{ref:jonas2017occupy,ref:onesteptwostep, ref:baldini2017,ref:lin2018tracking}.
-The authors in \cite{ref:onesteptwostep} evaluates the cost and performance of using
+The authors in \cite{ref:onesteptwostep} evaluate the cost and performance of using
 serverless for data-intensive computing.  They identify some key weaknesses in AWS
@@
 %\cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
-including whether or not functions should be stateless. PyWren~\cite{ref:jonas2017occupy} provides us 
-a new perspective of stateless function being a natural fit for distributed computing models, because it 
+%including whether or not functions should be stateless. 
+PyWren~\cite{ref:jonas2017occupy} provides us a new perspective of stateless function being a natural fit for distributed computing models, because it 
 abstracts away cluster management overhead and is ideal for embarrassingly parallel jobs. 

### 2019-02-03 results.tex
A number of minor fixes to improve clarity and some spelling fixes.

@@
 the quality of the application's output (for a given dataset) is dramatically
-affected by hyperparameter settings.  Perdictably the default settings are
+affected by hyperparameter settings.  Predictably the default settings are
 near the ``good'' end of the spectrum, but as both Table~\ref{tab:mse} and
@@
 Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost
-(classification), SVC, and NN applications, respectively.  Verses
+(classification), SVC, and NN applications, respectively.  Compared to
 the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%,
@@
 improves tuning performance over the default and worst case configurations for 
-XGBoost and SVC while generating only a small improvement over default for NN.
+XGBoost and SVC while generating only a small improvement over the
+default for NN.
 
@@
 
-We next analyze the monetary cost effects introduced by Seneca.  To do so, we
+We next analyze the monetary costs incurred by Seneca.  To do so, we
 use Seneca to find the hyperparameterization that optimizes application output
 quality (lowest MSE for regression, highest accuracy for classification).
-However note that trying all possible hyperparameterizations incurs a cost.
-Further, because Seneca uses AWS Lambda, the amount of memory it uses during
-tuning affects this cost.
+For each hyperparameteriyation that Seneca evaluates, it incurs a
+cost. Furthermore, the amount of memory used by Seneca during memory
+tuning also influeces overall cost.
 
-Thus we compare two Seneca execution configurations.  In the first
+Thus, instead of trying out all possible settings,  we compare two
+Seneca execution configurations.  In the first 
 we configure each lambda function to
@@
 quality and optimizing the cost of producing that output, it is doing so at
-the expense of execution performance (time to solution).
-Such penalty is expected due to the proportional CPU power to allocated memory.
-However, Seneca optimizer is able to find the optimal memory configuration to minimize such penalty.
-In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has the same execution time (0.91 minutes).
+the expense of execution performance (time to solution). Such a penalty
+is expected due to the proportional CPU power to allocated
+memory. However, the Seneca optimizer is able to find the optimal
+memory configuration to minimize that  penalty. In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has the same execution time (0.91 minutes).
 % The source of this execution performance penalty is not clear.  We hypothesize

### 2019-02-03 results.tex
mz - hyphenation
minor

@@
 \label{tab:svc_para}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}
@@
 %logorithm
-of Payton Manning's wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
+of Peyton Manning's Wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
 The dataset exhibits both seasonality and a holiday effect (e.g. around the super bowl games). 
@@
 
-In the results that follow, we evaluate \textit{default} parameteterizations (that come with 
+In the results that follow, we evaluate \textit{default} parameterizations (that come with 
 the application or that are defined by the application developer) for each application.  
@@
 Multi-Regression is a regression application 
-from an IoT project~\cite{iot-cpu} that was developed by the authors
-to predict outdoor temperature from the processor 
+from an IoT project~\cite{iot-cpu} that was developed (and extended
+from linear regression described in the citation, 
+to multiple linear regression) by the authors.
+The application predicts outdoor temperature from the processor 
 temperature of single board computers (SBCs).  
@@
 and make decisions from patterns in an input dataset. For this application, 
-we use a feedforward multilayer perceptron model~\cite{ref:feedforward_nn} 
+we use a feed-forward multi-layer perceptron model~\cite{ref:feedforward_nn} 
 for the classification task.
@@
 features (those with an absolute value of the Pearson correlation coefficient
-greater than 0.8). The dataset has also been balanced by downsampling one
+greater than 0.8). The dataset has also been balanced by down-sampling one
 target whose number greatly exceeds other ones. The resulting dataset contains
@@
 a regression algorithm). The first row indicates the number of
-different hyperparameter settings Senica considered.  Rows 3 through 5 show
+different hyperparameter settings Seneca considered.  Rows 3 through 5 show
 the MSE generated by the default hyperparameter settings, the best (lowest
@@
 quality (lowest MSE for regression, highest accuracy for classification).
-For each hyperparameteriyation that Seneca evaluates, it incurs a
+For each hyperparameterization that Seneca evaluates, it incurs a
 cost. Furthermore, the amount of memory used by Seneca during memory
-tuning also influeces overall cost.
+tuning also influences overall cost.
 
@@
 cost of these probes
-(denoted ``Optimizer Cost'') must be taken intio account as well.
+(denoted ``Optimizer Cost'') must be taken into account as well.
 %Because memory impacts both
@@
 
-% \textcolor{blue}{It would be good here in the Seneca case to also run the applications in the minumum amount of memory discovered by Seneca (ie if we were to run Seneca ahead of time, taking the max memory used by any of the functions per application) -- to show what Seneca is missing.
+% \textcolor{blue}{It would be good here in the Seneca case to also run the applications in the minimum amount of memory discovered by Seneca (i.e., if we were to run Seneca ahead of time, taking the max memory used by any of the functions per application) -- to show what Seneca is missing.
 this assumes you are doing the memory optimization WHILE you are doing the tuning -- if you are not, you can leave this out, but we need to remind the reader at this point how the memory optimization is done by Seneca (we should do this in this paragraph, either way).}
@@
 %\textcolor{red}{Add analysis here on what the columns are showing -- discuss
-%any anomalies (ie why is prophet optimization cost more than the others; why
+%any anomalies (i.e., why is prophet optimization cost more than the others; why
 %mult-regression difference is greater than the others). provide a summary for

### 2019-02-03 Seneca.tex
mz - spell check

@@
 that uses distributed message passing. Celery workers are processes 
-that take tasks from the queue, execute the tasks with the auguments specified, 
+that take tasks from the queue, execute the tasks with the arguments specified, 
 and store the result that is returned 

### 2019-02-03 abstract.tex
mz - update abstract
mz - spell check

@@
 possible hyperparameter options.  It automatically constructs an AWS Lambda
-handler that invokes the application, ingresses and splits the dataset into training
+handler that ingresses and splits the dataset into training
 and testing portions, and constructs, tests, and evaluates (i.e. scores) a machine
@@
 this execution in parallel for all possible combinations of the hyperparameters specified.
-It then returns the configuration (and model) that results in the best score 
+It then returns the configuration (or model) that results in the best score 
 to the user.
@@
 We present the design and implementation of Seneca and introduce an extension to the
-system that automaticallly optimizes memory use by the functions.  
+system that automatically optimizes memory use by the functions.  
 Our empirical evaluation using

### 2019-02-03 conclusion.tex
mz - small tweaks and typos
A number of minor fixes to improve clarity and some spelling fixes.
mz - spell check

@@
 We present the design, implementation, and cost optimization for Seneca.
-The optimization automaticallly optimizes function memory use to reduce the cost
+The optimizer automatically optimizes function memory use to reduce the cost
 of AWS Lambda use.  Our empirical evaluation using
 multiple applications for regression and classification (using
-the models for prediction and not explanitory value), shows that Seneca is able to quickly
+the models for prediction and not explanatory value), shows that Seneca is able to quickly
 identify the best performing model for the applications and datasets that we consider.  

### 2019-02-03 intro.tex
mz - spell check

@@
 implementations of enterprise services, such as
-object storage, databases, queuing systems, and web and application servers.
-The reason for this is that it is very
+object storage, databases, queuing systems, and web application servers.
+The reason is that it is very
 challenging, even for expert users, to configure complex
@@
 systems automatically configure, manage, and scale applications
-to significantly simplify and broaden participation in (by less expert
-users) the use of cloud systems.
+to significantly simplify and broaden participation (by less expert
+users) in the use of cloud systems.
 %xxx: http://shivaram.org/publications/pywren-socc17.pdf
@@
 function should be triggered.  Functions are invoked (triggered)
-automatically by the cloud in response to updates to other cloud services
+automatically by the cloud in response to external events or updates to other cloud services
 (e.g. storage, queues, notification services, among others). They
@@
 machine learning models is challenging given the large number of configuration
-options, i.e., hyperparameters, typical of models today.
+options (i.e. hyperparameters) typical for models today.
 Hyperparameters govern the learning process of machine learning applications.
@@
 machine learning applications as stateless functions to AWS Lambda.
-It then orchestrates exhaustive evaluation of hyperparameter settings
+It then orchestrates exhaustive evaluation of specified hyperparameter settings
 to identify the best performing model (for a given dataset) by

### 2019-02-03 related_work.tex
mz - spell check

@@
 and overhead. The cloud infrastructure provisioning framework Terraform~\cite{ref:terraform} 
-also provides automated deployment of functions to serverless platforms, but it does not simulate the AWS Lamdba runtime to create the deployment package (doing so on a non-Linux system will result in Lambda errors and failures at execution time).
+also provides automated deployment of functions to serverless platforms, but it does not simulate the AWS Lambda runtime to create the deployment package (doing so on a non-Linux system will result in Lambda errors and failures at execution time).
 In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous integration and delivery pipeline for serverless architectures, but it also introduces monetary cost overhead

### 2019-02-03 results.tex
mz - spell check

@@
 a classification application in this evaluation.  
-The hyperparmeters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{ref:xgboostparams}.
+The hyperparameters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{ref:xgboostparams}.
 %xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
@@
 based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
-The hyperparmeters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{ref:svcparams}.
+The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{ref:svcparams}.
 %xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
@@
 for the classification task.
-The hyperparmeters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{ref:nnparams}.
+The hyperparameters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}.
+A definition for each hyperparameter can be found at~\cite{ref:nnparams}.
 %nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html
@@
 Table~\ref{tab:accuracy} presents the accuracy percentage (higher is
-better) reported by each application (3 right-most columns) for the default,
+better) reported by each application (3 rightmost columns) for the default,
 worst, and best hyperparameter tuning configurations reported by Seneca.

### 2019-02-25 conclusion.tex
mz - pass after 30 execution time

@@
 the models for prediction and not explanatory value), shows that Seneca is able to quickly
-identify the best performing model for the applications and datasets that we consider.  
+identify the best performing hyperparameter setting for the applications and datasets that we consider.  
 We also show that Seneca memory optimization reduces the cost of using

### 2019-02-25 results.tex
mz - pass after 30 execution time

@@
 \centering
-%\scriptsize
-%\resizebox{\columnwidth}{!}{
-\begin{tabular}{|l|l|} \hline
-\textbf{Application}& \textbf{Description}\\
-\hline
-Prophet& Time series decomposition and prediction\\ 
-\hline
-Multi-Regression& Multiple linear regression/prediction of time series\\
-\hline
-XGBoost& Regression and classification by gradient boosting\\
-\hline
-SVC & Classification based on support vector machine\\
-\hline
-NN& Classification by layered artificial neural network\\
-\hline
-\end{tabular}
-%}
+\input{tables/application-tab}
 \caption{Machine learning applications used as benchmarks
@@
 we evaluate Seneca in terms of performance, monetary cost, 
-and hyperparameter tuning time (latency), 
+and hyperparameter tuning execution time, 
 for different machine learning applications.
@@
 \centering
-\scriptsize
-%\resizebox{\columnwidth}{!}{
-\begin{tabular}{|l|l|l|} 
-\hline
-\textbf{Hyperparameter}& \textbf{Default} & \textbf{Tuning options}\\
-\hline
-grow & linear & [linear, logistic] \\
-\hline
-changepoint prior scale & 0.05 & [0.05, 0.5] \\
-\hline
-holidays prior scale & 10 & [1, 5, 10] \\
-\hline
-seasonality prior scale & 0.5 & [0.1, 0.5] \\
-\hline
-fourier order & 10 & [5, 10, 15, 20] \\
-\hline
-seasonality mode & additive & [additive, multiplicative] \\
-\hline
-interval width & 0.8 & [0.5, 0.8] \\
-\hline
-\end{tabular}
-%}
+\input{tables/hparams-prophet-tab}
 \caption{The hyperparameters that Seneca considers for Prophet. 
@@
 \scriptsize
-\input{hparams-xgboost-tab}
+\input{tables/hparams-xgboost-tab}
 \caption{The hyperparameters that Seneca considers for XGBoost. 
@@
 \scriptsize
-\input{hparams-svc-tab}
+\input{tables/hparams-svc-tab}
 \caption{The hyperparameters that Seneca considers for SVC. 
@@
 \scriptsize
-\input{hparams-nn-tab}
+\input{tables/hparams-nn-tab}
 \caption{The hyperparameters that Seneca considers for NN.
@@
 the application or that are defined by the application developer) for each application.  
-The default parameters and tuning options for Prophet are listed in the table~\ref{tab:prophet_para}.
+The default parameters and tuning options for Prophet are listed in the Table~\ref{tab:prophet_para}.
 For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points.
@@
 features (those with an absolute value of the Pearson correlation coefficient
-greater than 0.8). The dataset has also been balanced by down-sampling one
-target whose number greatly exceeds other ones. The resulting dataset contains
+greater than 0.8). The dataset has also been balanced by down-sampling and the resultant dataset contains
 33926 rows (individual fruit) distributed evenly to 5 targets and each row has
@@
 
-To evaluate Seneca, we measure tuning performance, application execution time,
+To evaluate Seneca, we measure tuning performance, application execution time and memory use,
 and monetary cost.  For tuning performance, we use mean squared error (MSE)
@@
 the maximum allocatable memory size to the performance and cost when run with
-Seneca's automatically determined memory size.  Note that this comparison
-assume that the memory size used by each benchmark does not depend on
-hyperparameter settings.  We have verified that this assumption holds for the
-benchmarks and datasets we consider and plan to consider applications for
-which hyperparameter settings require different maximum amounts of memory as
-part of future work.
+Seneca's automatically determined memory size.
+Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we have verified the optimized allocated memory allows all hyperparameter settings run successfully.
+
+% Note that this comparison assumes that the memory size used by each benchmark does not depend on hyperparameter settings.
+We have verified that this assumption holds for the benchmarks and datasets we consider and plan to consider applications for which hyperparameter settings require different maximum amounts of memory as part of future work.
 
@@
 \centering
-\begin{tabular}{|c|c|c|c|}
-\hline
-& Prophet & Multi-Regression & XGBoost\\
-\hline
-\# of Combinations & 384 & 255 & 768\\
-\hline
-\hline
-Default MSE & 0.284 & 11.446 & 0.119 \\
-\hline
-Worst MSE & 1.266 & 43.752 & 8.98 \\
-\hline
-Best MSE (Seneca) & 0.220 & 9.621 & 0.044 \\
-\hline
-%percent difference between default and best 26.07%, 15.94%, 67.30%
-%percent difference between worst and best 82.63%, 78.01%, 95.52%
-%\begin{figure}[t] \centering 
-%\includegraphics[scale=0.4]{mse}
-\end{tabular}
+\input{tables/mse-tab}
 \caption{Combination count and MSE for the default, best (Seneca's recommendation), and worst hyperparameter configurations for the three regression applications. 
@@
 \label{tab:mse}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}
@@
 Compared to the default hyperparameter settings,
-Seneca reduces MSE by 26\%, 16\%, and 63\%, for Prophet, Multi-Regression, and XGBoost,
-respectively, for the datasets and training methodologies that we consider.
-Verses the worst case, Seneca reduces MSE by 83\%, 78\%, and 99\%, respectively.
+Seneca reduces MSE by 22.56\%, 15.94\%, and 62.69\%, for Prophet, Multi-Regression, and XGBoost, respectively, for the datasets and training methodologies that we consider.
+Verses the worst case, Seneca reduces MSE by 82.62\%, 78.01\%, and 99.51\%, respectively.
 
@@
 using an 80/20 (train/test) percent split,
-Seneca increases accuracy by 3.43\%, 62.52\%, and 0.53\%, for XGBoost
+Seneca increases accuracy by 2.46\%, 19.04\%, and 3.79\%, for XGBoost
 (classification), SVC, and NN applications, respectively.  Compared to
-the worst case, Seneca improves accuracy by 99.13\%, 75.75\%, and 65.57\%,
+the worst case, Seneca improves accuracy by 98.11\%, 26.74\%, and 63.92\%,
 respectively.
@@
 \centering
-\begin{tabular}{|l|c|c|c|}
-\hline
-\textbf{80\%-20\%} & XGBoost & SVC & NN\\
-\hline
-\hline
-Default Accuracy & 95.70\% & 21.77\% & 84.23\%\\
-\hline
-Worst Accuracy&0.00\%&7.53\% & 19.19\%\\
-\hline
-Best Accuracy (Seneca) &99.13\% & 83.29\% & 84.76\%\\
-\hline
-%\hline
-%\hline
-%\textbf{20\%-80\%} & XGBoost & SVC & NN\\
-%\hline
-%Default Accuracy & 95.07\% & 21.31\% & 55.44\%\\
-%\hline
-%Worst Accuracy&0.00\% & 9.42\% & 19.55\%\\
-%\hline
-%Best Accuracy (Seneca) & 98.68\% & 43.61\% & 60.89\%\\
-%\hline
-%\hline
-%\textbf{0.1\%-99.9\%} & XGBoost & SVC & NN\\
-%\hline
-%Default Accuracy & 86.37\% & 20.02\% & 20.00\%\\
-%\hline
-%Worst Accuracy & 0.00\% & 19.99\% & 19.79\%\\
-%\hline
-%Best Accuracy (Seneca) & 89.14\% & 55.79\% & 29.99\%\\
-%\hline
-
-%percent difference between default and best 83.65%, 83.84%, 79.83%
-%percent difference between worst and best 86.07%, 85.73%, 84.63%
-%\begin{figure}[t] \centering 
-%\includegraphics[scale=0.38]{accuracy}
-\end{tabular}
+\input{tables/accu-tab}
 \caption{The Accuracy reported for the 
@@
 the user uses the 80-20 split ``rule'' when measuring accuracy. In this case,
-Seneca's improvement over the default parameterizations varies from less than
-1\% for the Neural Network (NN) application (column 4), to 61.5\% for SVC
-(best versus default in column 3).
+Seneca's improvement over the default parameterizations varies from 2.46\% for XGBoost application (column 2), to 19.04\% for SVC
+(column 3).
 
@@
 For both types of applications (regression and classification), Seneca significantly
-improves tuning performance over the default and worst case configurations for 
-XGBoost and SVC while generating only a small improvement over the
-default for NN.
+improves tuning performance over the default and worst case configurations for SVC while generating a relatively small improvement over the default for XGBoost and Neural Network.
+This is because powerful classifiers, like XGBoost and Neural Network, can achieve fairly good accuracy by default setting, whereas weaker classifier, like SVC, requires more tuning to reach high accuracy.
+
+\begin{table}[t]
+\centering
+\scriptsize
+\input{tables/exec-time-memory-tab}
+\caption{The mean (stdev) values of execution time and memory use, and best accuracy across 30 executions of three classification benchmarks running against two random states.
+It verifies data split does not have major impact to execution metrics and scores.
+\label{tab:exec_memory}}
+%\vspace{-0.2in}
+\end{table}
+
+In order to investigate the potential impact from data split, we split the data for three classification applications by two random states, run Seneca 30 times and obtain execution time, memory use and best accuracy from AWS CloudWatch logs.
+As showed in Table~\ref{tab:exec_memory}, different data split has no major impact to these three values.
+It does not only mean the execution time and monetary cost are consistent given various data splits, but also indicates users do not have to run Seneca repetitively in the inference phase when new data are generated.
+
+% \begin{table}
+% \centering
+% \input{tables/speedup-tab}
+% \caption{The execution time of tuning in seconds by using Seneca and EC2 instance (Serial) and respective speedup. 
+% \label{tab:accuracy}}
+% \vspace{-0.2in}
+% \end{table}
+
+Finally in this section, we contrast the execution time of Seneca with serial hyperparameter tuning process on EC2 instance across five applications.
+Since library compilation issue, we use t2.medium on Prophet and t2.micro on other 4 applications.
+As a result, Seneca achieves at least 4x speedup for IO-bound application (SVC) and 21x speedup for CPU-bound application (XGBoost).
+It confirms Seneca can execute tuning within a more reasonable period of time, comparing to executing serially on EC2 instance.
 
@@
 
-We next analyze the monetary costs incurred by Seneca.  To do so, we
-use Seneca to find the hyperparameterization that optimizes application output
-quality (lowest MSE for regression, highest accuracy for classification).
-For each hyperparameterization that Seneca evaluates, it incurs a
-cost. Furthermore, the amount of memory used by Seneca during memory
-tuning also influences overall cost.
+% To do so, we use Seneca to find the hyperparameterization that optimizes application output
+% quality (lowest MSE for regression, highest accuracy for classification).
+% For each hyperparameterization that Seneca evaluates, it incurs a
+% cost. Furthermore, the amount of memory used by Seneca during memory
+% tuning also influences overall cost.
 
-Thus, instead of trying out all possible settings,  we compare two
+We next analyze the monetary costs incurred by Seneca. Instead of trying out all possible settings,  we compare two
 Seneca execution configurations.  In the first 
@@
 executions.
-Second, we
-employ Seneca's memory optimization which automatically detects and configures
+Second, we employ Seneca's memory optimization which automatically detects and configures
 the amount of memory needed by each function.  This optimization requires
@@
 
-\begin{table}
-\centering
-\begin{tabular}{|l|c|c|c|c|c|}
-\hline
-& Prophet & MR & XGBoost & SVC & NN\\
-\hline
-\hline
-Exec time (minutes)& 24.96 & 4.18 & 17.48 & 0.91 & 2.49 \\
-\hline
-Seneca Cost (\$) & 0.722 & 0.121 & 0.5 & 0.023 & 0.072 \\
-\hline
-\end{tabular}
-\caption{Monetary cost of using Seneca for hyperparameter tuning when configured to use the maximum amount of memory (3008 MB) possible for each function invocation. 
-\label{tab:cost_max_memory}}
-%\vspace{-0.2in}
-\end{table}
+Tables~\ref{tab:cost_optimized} shows the results with and without 
+the Seneca memory optimization, respectively.
+The five columns identify the benchmark applications and the first row is the total execution time in minutes and the second row is total cost of tuning when Seneca's lambda functions are configured to use the maximum amount of memory (3008 MB).
+For optmized memory configuration, fourth row shows the cost of the memory optimizer in the
+second row, Seneca's cost using the optimization in the fifth row, and total cost on sixth row.
+Finally, in the seventh and eighth rows of Table~\ref{tab:cost_optimized} we show the
+savings that memory optimization introduces over using the maximum memory in dollar cost and as a percentage respectively.
 
@@
 \centering
-\begin{tabular}{|l|c|c|c|c|c|}
-\hline
-& Prophet & MR & XGBoost & SVC & NN\\
-\hline
-\hline
-Exec time (minutes)& 38.7 & 8.72 & 29.07 & 0.91 & 3.17 \\
-\hline
-Optimizer Cost (\$) &0.033 & 0.014 & 0.003 & 0.010 & 0.008 \\
-\hline
-Seneca Cost (\$) &0.62 & 0.086 & 0.354 & 0.007 & 0.056 \\
-\hline
-Total Cost (\$) &0.653 & 0.1 & 0.357 & 0.016 & 0.064 \\
-\hline
-\hline
-Savings (\$) & 0.07 & \$0.02 & 0.15 & 0.007 & 0.008\\
-\hline
-Savings (\%) & 10\% & 17\% & 30\% & 30\% & 11\%\\
-\hline
-\end{tabular}
-\caption{Seneca Memory Optimization:  The  monetary  cost  of using Seneca for hyperparameter tuning when the amount of memory  used  for  each  function  invocation  is  automatically inferred and set by Seneca.
+\input{tables/seneca-mem-opt-tab.tex}
+\caption{Seneca Memory Optimization: First two rows show the execution time and  monetary cost of using Seneca at max memory (3008 MB).
+Row 3-6 show the execution time and cost when the amount of memory used for each function invocation is automatically inferred and set by Seneca.
+Row 7-8 show savings by dollar and percentage.
 \label{tab:cost_optimized}}
@@
 
-Tables~\ref{tab:cost_max_memory} and~\ref{tab:cost_optimized} show the results with and without 
-the Seneca memory optimization, respectively. In both tables, the five columns identify the 
-benchmark applications and the first row is the total execution time in minutes for 
-Seneca's hyperparameter tuning for the corresponding application.  
-In Table~\ref{tab:cost_max_memory}, the second row is total cost of tuning when Seneca's 
-lambda functions are configured to use the maximum amount of memory (3008 MB). 
-Table~\ref{tab:cost_optimized} shows the cost of the memory optimizer in the
-second row, Seneca's cost using the optimization in the third row, and total cost on fourth row.
-Finally, in the fifth and six rows of Table~\ref{tab:cost_optimized} we show the
-savings that memory optimization introduces over using the maximum memory in
-dollar cost and as a percentage respectively.
-
-These tables illustrate two important cost features of Seneca.  First, using
+Table~\ref{tab:cost_optimized} illustrates two important cost features of Seneca.  First, using
 AWS Lambda, full hyperparameter space exploration is not expensive in 
 \textit{absolute} dollar cost terms.  Even using the maximum memory available
-for almost 25 minutes of execution time (cf Prophet in Table~\ref{tab:cost_max_memory}), the
+for almost 25 minutes of execution time (cf Prophet in Table~\ref{tab:cost_optimized}), the
 total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
@@
 execution) for some of the applications.  That is, the
-execution times for all applications except SVC increase when Seneca chooses
+execution times for all applications increase when Seneca chooses
 a memory size.  Thus while Seneca is finding the best application output
@@
 memory. However, the Seneca optimizer is able to find the optimal
-memory configuration to minimize that  penalty. In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has the same execution time (0.91 minutes).
+memory configuration to minimize that  penalty.
+In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has almost the same execution time (1.91 vs 1.95 minutes).
 % The source of this execution performance penalty is not clear.  We hypothesize
@@
 Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.
+
+To corroborate the cost-effectiveness of Seneca, we analyzed the total cost of five benchmarks in 30 executions from last section.
+We observe the reported \textit{billed duration} and \textit{max memory used} oscillate that leads to different total cost across 30 executions and we assume it is because the pagination and memory sampling method used by different AWS Lambda host servers.
+However, even taking fluctuation into account, the highest cost of execution under optimized memory is still cheaper than the lowest cost of execution under maximum memory in all five benchmarks.
+We believe Seneca's optimizer is economical despite the locality of lambda container and application.
+
 % \textcolor{blue}{AWS announces the proportional CPU power to memory which is the source of penalty}

### 2019-02-25 Seneca.tex
chandras pass

@@
 
-To facilitate model optimization on serverless architecture, we have developed Seneca, 
-a framework for tuning the hyperparameters for machine learning applications 
+To facilitate model search and selection using the serverless architecture, 
+we have developed Seneca, 
+a framework for tuning the hyperparameters of machine learning applications 
 in AWS Lambda. 
-The Seneca pipeline consists of packaging, deployment, serverless 
+The Seneca pipeline consists of packaging, deployment, 
 function optimization, and hyperparameter tuning. Figure~\ref{fig:seneca} 
@@
 application expects.  Seneca uses this configuration to construct
-the hyperparameter search space.  The dataset URL is a link to a
-valid dataset stored in S3.
+the hyperparameter search space.  The dataset URL refers to a
+valid dataset stored in AWS S3.
 
@@
 to AWS Lambda using the
-AWS Command line Interface~\cite{ref:awscli}.
+AWS Command line Interface\footnote{\url{https://aws.amazon.com/cli/}} 
+and the developers credentials.
 
@@
 The AWS Lambda pricing model is determined by the execution duration 
-and memory. The cost of a function instance is referred to as 
-\texttt{compute charge}, and is calculated as the amount of 
-allocated memory multiplied by the
+and memory of each invoked function. The cost of a function instance is referred to as 
+the \texttt{compute charge}, which is the allocated memory 
+multiplied by the
 billed duration (execution time rounded up to the 
-nearest 100ms)~\cite{ref:pricing}.
+nearest 100ms)~\footnote{\url{https://aws.amazon.com/lambda/pricing/}}.
 %https://aws.amazon.com/lambda/pricing/
@@
 Currently, allocated memory for a Lambda function can be set
-between 128MB and 3008MB using increments of 64MB.
-AWS documentation~\cite{ref:lambdalimits} states that Lambda 
-allocates CPU to functions in way that is proportional to allocated memory size,
-in the same way as is done for general purpose Amazon EC2 instance types.
+from 128MB to 3008MB in increments of 64MB.
+AWS documentation~\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/resource-model.html}} 
+states that Lambda 
+allocates CPU in a way that is proportional to allocated memory size,
+as is done for general purpose AWS EC2 instance types.
 
@@
 
-To verify that assertion, we conduct an experiment in which
-we increase of CPU power and memory for a compute-bound 
-AWS Lambda function (a microbenchmark that performs 3-D matrix multiplication~\cite{ref:matrix}).
+To evaluate the impact of memory and CPU allocation on application cost,
+we analyze a 3-D matrix multiple serverless benchmark~\cite{ref:matrix} using AWS Lambda.
 We configure function instances to use the 46 possible allocated 
-memory increments, invoke them, and record the billed duration and memory
-use of each.
-Figure~\ref{fig:memory} shows the relationship between allocated memory (x-axis) and reciprocal of billed duration (y-axis). 
-Figure ~\ref{fig:compute_charge} shows the relationship between memory 
+memory increments, invoke them, and record the billed duration and memory used by each.
+Figure~\ref{fig:memory} shows the relationship between allocated memory 
+(x-axis) and reciprocal of billed duration (y-axis). 
+Figure~\ref{fig:compute_charge} shows the relationship between memory 
 size (x-axis) and compute charge (y-axis). 
-We observe that for this simple benchmark,
+We observe that for this benchmark,
 the CPU power plateaus after 1600 MB. 
@@
 
-These findings show that CPU does not proportionally increase with
+These findings show that CPU does not increase proportionally with
 an increase in allocated memory.  We use this relationship within
@@
 which it uses as its starting point.
-Seneca then defines two double-end queues 
+Seneca then defines two double-ended queues 
 (deque) of length N, to store 
@@
 allocated memory is less than or equal to 3008 MB, 
-the optimizer continues reconfigures and invokes the function 
+the optimizer reconfigures and invokes the function 
 using the next increment for memory allocation.  It 
@@
 We employ two exit conditions.  The first is when the 
-compute charge monotonically increases across the length of deque. 
+compute charge monotonically increases across the deque. 
 The second is when the increase in slope is greater than a threshold. 
@@
 In addition, this optimization can be turned on or off via a command line
-flag when starting Seneca.
+argument to Seneca.
 
@@
 and store the result that is returned 
-in a database (we use Redis~\cite{ref:redis} in our prototype).
+in a database (we use Redis~\footnote{\url{https://redis.io/}} in our prototype).
 
 Based on the configuration file, Seneca creates a list of 
-payloads (function arguments) that contains values of 
-hyperparameters.  The complete list contains all combinations of the
-specified parameter
+payloads (function arguments) with
+hyperparameter values.  
+The complete list contains all combinations of the specified parameter
 settings.  Seneca places the list on the queue and celery 
@@
 Upon function
-termination, the work records the evaluation score (and serialized model)
+termination, the worker records the evaluation score (and serialized model)
 in the database with the hyperparameter configuration from the payload.

### 2019-02-25 abstract.tex
chandras pass

@@
 handler that ingresses and splits the dataset into training
-and testing portions, and constructs, tests, and evaluates (i.e. scores) a machine
-learning model for a given set of hyperparameter values.  Seneca orchestrates
-this execution in parallel for all possible combinations of the hyperparameters specified.
+and testing subsets, and constructs, tests, and evaluates (i.e. scores) a machine
+learning model for a given set of hyperparameter values.  Seneca concurrently invokes
+functions for all combinations of the hyperparameters specified.
 It then returns the configuration (or model) that results in the best score 
@@
 system that automatically optimizes memory use by the functions.  
-Our empirical evaluation using
-multiple machine learning applications for regression and classification (using
-the models for prediction and not explanatory value), shows that Seneca is able to quickly
-identify the best performing model,
-for the datasets and algorithms that we study. 
-Moreover, our memory optimization reduces the cost of using
-Seneca by 10-30\% for the applications studied.
+Our empirical evaluation using multiple predictive machine learning applications 
+for regression and classification shows that Seneca is able to quickly
+identify the best performing model for the programs and datasets that we consider.
+Moreover, its memory optimization reduces the cost of using Seneca 
+by 10-30\% for the applications studied.
 

### 2019-02-25 intro.tex
chandras pass

@@
 agreements (SLAs). Uniquely, cloud systems can be configured 
-to add and remove resources and services,
-automatically and on-demand, based on load 
-or as required by executing applications.
+to add and remove (i.e. auto-scale) resources and services
+automatically, based on the ``elastic'' resource requirements and service needs 
+of executing applications.
 
-To date however, cloud use has been limited to large-scale 
-implementations of enterprise services, such as
-object storage, databases, queuing systems, and web application servers.
-The reason is that it is very
-challenging, even for expert users, to configure complex
+To date however, clouds are used more for
+enterprise services (object stores, databases, application servers, etc.)
+than for elastic applications.
+The reason for this is that it is challenging to configure complex
 distributed systems for application use, 
-and to leverage the elasticity (auto-scaling) that
+and to leverage the auto-scaling that
 clouds offer. To address this challenge, cloud providers 
-have started to offer cloud programming and execution environments
-under the moniker of \textit{serverless} 
-computing~\cite{ref:jonas2017occupy, ref:onesteptwostep, ref:peeking}.  Serverless
-systems automatically configure, manage, and scale applications
-to significantly simplify and broaden participation (by less expert
-users) in the use of cloud systems.
+have started to offer programming and execution environments
+that preclude the need for server configuration,
+under the \textit{serverless} moniker~\cite{ref:jonas2017occupy,ref:onesteptwostep,ref:peeking}.  
+Serverless platforms automatically configure, manage, and scale applications
+to significantly simplify cloud use.
+%and broaden participation (by less expert
+%users) in the use of cloud systems.
 %xxx: http://shivaram.org/publications/pywren-socc17.pdf
@@
 
-Using the serverless model, applications developers upload 
+Using the serverless model, application developers upload 
 arbitrary computations in high level languages
-as stateless functions to these cloud-hosted services, along with a
-specification conditions under which each
-function should be triggered.  Functions are invoked (triggered)
-automatically by the cloud in response to external events or updates to other cloud services
-(e.g. storage, queues, notification services, among others). They
+as stateless functions to cloud-hosted, serverless platforms.
+Functions are invoked (i.e. triggered)
+automatically by the cloud in response to updates to other cloud services
+(e.g. storage, queues, notification services, and API gateways, among others), which 
+the developer configures. Serverless functions
 communicate, persist, and access data only 
-via their inputs or shared, remote storage.  
+through their inputs or via shared, storage services.  
 As a result, serverless applications are inherently elastic and can 
@@
 source for private cloud systems, 
-AWS Lambda~\cite{ref:awslambdadg} was the first and is now the 
-most popular and most advanced serverless public cloud service 
-available today.
+Amazon Web Services (AWS) Lambda\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf}} %~\cite{ref:awslambdadg} 
+was the first and is the most widely used
+serverless public cloud platform.
 %awslambda: https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf
@@
 for tuning machine learning applications.
-To date, Lambda has not be heavily used for training and evaluating
+To date, Lambda is not widely used for training and evaluating
 machine learning models because of a concern that 
@@
 To investigate this potential, its overhead, and to simplify the 
-use of Lambda for training, testing, and evaluation machine learning models, 
+use of Lambda for training, testing, and evaluation of machine learning models, 
 we design and develop a new system and toolset called \textit{Seneca}.
 
-Specifically, Seneca implements, packages, and deploys 
+Seneca implements, packages, and deploys 
 machine learning applications as stateless functions to AWS Lambda.
@@
 to identify the best performing model (for a given dataset) by
-comparing the error and accuracy across models.  We consider
+comparing error and accuracy across models.  We consider
 prediction accuracy (as opposed to explanatory power) as the
 scoring metric (mean squared error for regression 
-and accuracy percent for classification), to avoid overfitting.
+and accuracy percentage for classification), to avoid overfitting.
 Users present Seneca with their application, a range of values for 
@@
 the set of parameters (or the model itself) that produces
-the best cross-validation score (e.g. lowest squared error or highest
-accuracy) for the dataset. Users can employ this model for other datasets
+the best cross-validation score.
+Users can employ this model for other datasets
 (with Seneca if desired) without retraining the model to amortize the cost
@@
 and memory use for six machine learning applications and datasets. We 
-find that Seneca is effective for quickly training these
-models and identifying the best performing hyperparameter setting for 
-these applications. We also find 
-Seneca to be very low cost and able to automatically 
-identify the 
-best memory configuration for each application further lowering its 
+find that Seneca is fast, inexpensive, and effective for model 
+construction and comparison. Seneca is also able to identify
+automatically the
+best memory configuration for each application, further lowering its cost
 by 10-30\%.
-As such, Seneca greatly simplifies model construction and comparison and 
-does so with very low latency and at very low cost.
-We intend to make Seneca and the applications available as open source
+We intend to make Seneca, its applications, and their datasets publicly available
 when/if this paper is accepted for publication.  In the sections

### 2019-02-25 results.tex
chandras pass

@@
 \label{tab:bmarks}}
-\vspace{-0.2in}
+%\vspace{-0.2in}
 \end{table}
-
-In this section,
-we evaluate Seneca in terms of performance, monetary cost, 
-and hyperparameter tuning execution time, 
-for different machine learning applications.
-We first overview these applications and our empirical methodology. 
-We then present our experimental results.
 
@@
 \centering
-\scriptsize
+%\scriptsize
 \input{tables/hparams-xgboost-tab}
@@
 \centering
-\scriptsize
+%\scriptsize
 \input{tables/hparams-svc-tab}
@@
 \centering
-\scriptsize
+%\scriptsize
 \input{tables/hparams-nn-tab}
@@
 \end{table}
+
+In this section,
+we evaluate Seneca in terms of performance, monetary cost, 
+and hyperparameter tuning execution time, 
+for different machine learning applications.
+We first overview these applications and our empirical methodology. 
+We then present our experimental results.
 
@@
 For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points.
-Then the application returns the average MSE of all cross validation.
-Based on the model trained by default parameter setting, this average MSE metric is 0.284.
+Then the application returns the average MSE across cross validations.
+%Based on the model trained by default parameter setting, this average MSE metric is 0.284.
 
-Multi-Regression is a regression application 
-from an IoT project~\cite{iot-cpu} that was developed (and extended
+Multi-Regression is a regression application developed as part of
+an Internet-of-Things (IoT) project~\cite{iot-cpu} (and extended
 from linear regression described in the citation, 
-to multiple linear regression) by the authors.
+to multiple linear regression by the authors of this prior work).
 The application predicts outdoor temperature from the processor 
@@
 series of processor temperature measurements,
-to predict outdoor microclimate temperatures without using a temperature sensor.
+to predict outdoor microclimate temperatures. % without using a temperature sensor.
 %(e.g. for use in 
@@
 a classification application in this evaluation.  
-The hyperparameters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{ref:xgboostparams}.
+The hyperparameters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found in~\cite{ref:xgboostparams}.
 %xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
+
 Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
 based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
-The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{ref:svcparams}.
+The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found in~\cite{ref:svcparams}.
 %xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
+
 Neural network (NN)~\cite{ref:neural_network} is a machine learning framework that learns 
-and make decisions from patterns in an input dataset. For this application, 
+and makes decisions from patterns in an input dataset. For this application, 
 we use a feed-forward multi-layer perceptron model~\cite{ref:feedforward_nn} 
 for the classification task.
-The hyperparameters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}.
-A definition for each hyperparameter can be found at~\cite{ref:nnparams}.
+The hyperparameters and their defaults for NN are listed in Table~\ref{tab:nn_para}. 
+A definition for each hyperparameter can be found in~\cite{ref:nnparams}.
 %nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html
 
-For these applications (XGBoost, SVC, and NN), we use a labeled
-dataset for training, testing, and evaluation from this
-project~\cite{iot-cpu}. The dataset contains measurements from individual
+For the classification applications (XGBoost, SVC, and NN), we use a labeled
+dataset for training, testing, and evaluation from an IoT 
+project~\cite{blind}. The dataset contains measurements from individual
 citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a fruit sorting
@@
 features) include size, shape, weight, color, diameter, flatness, among other
-characteristics, for each fruit.  The label indicates which field the fruit
-was harvested from.  The applications train a model on a subset of the
+characteristics, for each fruit.  
+The dataset has been filtered to remove correlated
+features (those with an absolute value of the Pearson correlation coefficient
+greater than 0.8). The dataset has also been balanced by down-sampling and the resulting 
+dataset contains 33926 rows (individual fruit) distributed evenly to 5 targets and each row has
+18 features.  The label indicates which field the individual fruit was harvested from.  
+The application trains a model on a subset (80\%) of the
 data.  They then use this model to predict the field
-from which each fruit originates. For this study we use the same random 80\%
-subset of the dataset as the training dataset.  We use the remaining 20\% as the
-testing dataset.
+from which each fruit originates (for the remaining 20\%).
 
-These applications compute classification accuracy score
+The classification applications compute a classification accuracy score
 as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
@@
 is the indicator function. XGBoost also computes MSE for its regression task
-on the same datasets. The dataset has been filtered to remove correlated
-features (those with an absolute value of the Pearson correlation coefficient
-greater than 0.8). The dataset has also been balanced by down-sampling and the resultant dataset contains
-33926 rows (individual fruit) distributed evenly to 5 targets and each row has
-18 features.
+on the same datasets.
 

### 2019-02-26 intro.tex
minor

@@
 automatically by the cloud in response to updates to other cloud services
-(e.g. storage, queues, notification services, and API gateways, among others), which 
-the developer configures. Serverless functions
+(e.g. storage, queues, notification services, and API gateways, 
+among others), which 
+the developer configures. Serverless functions must execute in under
+a time bound (e.g. 15 minutes) and use less than a maximum memory size 
+(e.g. 3GB) or else the platform will terminate the function.
 communicate, persist, and access data only 

### 2019-02-26 results.tex
minor

@@
 the maximum allocatable memory size to the performance and cost when run with
-Seneca's automatically determined memory size.
-Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we have verified the optimized allocated memory allows all hyperparameter settings run successfully.
+Seneca's automatically determined memory size. Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we 
+have verified that the optimized allocated memory allows all 
+hyperparameter settings complete successfully.
 

### 2019-02-26 Seneca.tex
chandras pass

@@
 the hyperparameter search space.  The dataset URL refers to a
-valid dataset stored in AWS S3.
+valid dataset stored in the AWS Simple Storage 
+Service (S3)\footnote{\url{https://aws.amazon.com/s3/}}.
 
@@
 Seneca then defines two double-ended queues 
-(deque) of length N, to store 
+(\texttt{deque}) of length N, to store 
 allocated memory and compute charge data of different
@@
 We employ two exit conditions.  The first is when the 
-compute charge monotonically increases across the deque. 
+compute charge monotonically increases across \texttt{deque}. 
 The second is when the increase in slope is greater than a threshold. 
 Once the optimizer finds that both conditions hold, 
-it pops the left-most value from deque and configures 
+it pops the left-most value from \texttt{deque} and configures 
 the function to use that value for allocated memory for all future invocations.
@@
 \KwResult{Optimal allocated memory}
-Find memory used by payload as start point\;
-Define deques for allocated memory \& compute charge\;
+Find memory used by payload as starting point\;
+Define deque for allocated memory \& compute charge\;
  \While{allocated memory $\leq$ 3008 MB}{
 
-  \eIf{compute charge monotonically increase in deque \& slope $\geq$ 1}{
-   Popleft from deques\;
+  \eIf{compute charge monotonically increases in deque \& slope $\geq$ 1}{
+   Popleft from deque\;
    Configure allocated memory of function\; 
@@
    Probe lambda function\;
-   Append allocated memory and compute charge to deques\;
+   Append allocated memory and compute charge to deque\;
   }

### 2019-02-26 conclusion.tex
chandras pass

--- 2019-02-03 conclusion.tex
@@
 and selection for machine learning models.  
-Users provide Seneca with the application code and libraries, 1+ datasets, and the list 
+Users provide Seneca with the application code and 
+libraries, 1+ datasets, and the list 
 of possible hyperparameter settings.  
-%Seneca uses this 
-%information to automatically construct models using parallel functions in AWS Lambda. 
-%an AWS Lambda function that
-%that invokes the application, imports and splits the dataset into training
-%and testing datasets, and constructs, tests, and evaluates (i.e. scores) a machine
-%learning model for a particular configuration of hyperparameter settings.  
-Seneca uses this information to orchestrate parallel execution of these functions for all possible 
-combinations of hyperparameter values specified and returns the best scoring model
+Seneca uses this information to automatically
+configure and deploy these functions in parallel for all possible 
+combinations of hyperparameter values specified. Seneca
+returns the best scoring model
 and configuration to the user (for future use on other datasets).
@@
 of AWS Lambda use.  Our empirical evaluation using
-multiple applications for regression and classification (using
-the models for prediction and not explanatory value), shows that Seneca is able to quickly
-identify the best performing model for the applications and datasets that we consider.  
+multiple applications for regression and classification,
+shows that Seneca is able to quickly
+identify the best performing hyperparameter setting 
+for the applications and datasets that we consider.  
 We also show that Seneca memory optimization reduces the cost of using

### 2019-02-26 related_work.tex
mz - pass after 30 execution time
chandras pass

@@
-In this section, we overview related work. We discuss contributions that focus
-on serverless computing and machine learning model optimization.
+We next overview related work. We discuss contributions that focus
+on serverless computing, automatic packaging, 
+and machine learning (ML) model optimization.
 
@@
 serverless programming model and 
-implementations~\cite{ref:jonas2017occupy,ref:onesteptwostep, ref:baldini2017,ref:lin2018tracking}.
-The authors in \cite{ref:onesteptwostep} evaluate the cost and performance of using
-serverless for data-intensive computing.  They identify some key weaknesses in AWS
-Lambda for this application domain including the inability to effectively train models.
-Our work show that it is possible for the subset of machine learning applications that we 
-consider, to train models in a cost effective ways.
+implementations~\cite{ref:jonas2017occupy,ref:onesteptwostep,ref:baldini2017,ref:lin2018tracking}.
+%The authors in \cite{ref:onesteptwostep} evaluate the cost and performance of using
+%serverless for data-intensive computing.  
+They identify some weaknesses in AWS
+Lambda for data-intensive computing, including the inability to 
+effectively train models.
+Our work shows that it is possible and cost effective to use
+AWS Lambda to train models for the subset of ML applications that we 
+consider.
 
-%\cite{ref:baldini2017} identifies multiple open research questions surrounding serverless,
-%including whether or not functions should be stateless. 
-PyWren~\cite{ref:jonas2017occupy} provides us a new perspective of stateless function being a natural fit for distributed computing models, because it 
-abstracts away cluster management overhead and is ideal for embarrassingly parallel jobs. 
-ExCamera~\cite{ref:encoding} presents a 
+PyWren~\cite{ref:jonas2017occupy} shows that stateless functions
+are a natural fit for distributed computing models. The technique
+abstracts away cluster management overhead and is ideal for 
+embarrassingly parallel jobs.  ExCamera~\cite{ref:encoding} presents a 
 framework for running general-purpose parallel tasks (encoding 4K video) 
 on a commercial serverless platform using multithreading. 
+Cirrus~\cite{ref:jonas2019cloud} attempts to train ML models 
+using a parameter server and serverless functions. 
 An empirical comparison of resource utilization and performance isolation
@@
 Azure Functions, and Google Cloud Functions.
-%to discuss the resource utilization and performance isolation efficiency of 
-%three platforms. Besides efficacy and efficiency, there are challenges serverless architecture are facing in terms of 
-%application monitoring and distributed storage. GammaRay~\cite{ref:lin2018tracking} proposes a cloud service that extracts
-%causal dependencies across serverless functions and cloud services without programmer intervention. Such monitoring and 
-%debugging tool simplifies the development and maintenance of serverless applications. Pocket~\cite{ref:ephemeral} provides 
-%an elastic and economical distributed data store for severless analytic applications. We expect more contributions to toolchain 
-%and distributed storage of serverless in upcoming years.
 
-%please also discuss and cite these papers - you may need a second paragraph
-%http://www.cs.ucsb.edu/~ckrintz/papers/ic2e18.pdf
-%http://shivaram.org/publications/pywren-socc17.pdf
-%S.
-Fouladi, R.
-S.
-Wahby, B.
-Shacklett, K.
-V.
-Balasubramaniam, W.
-Zeng, R.
-Bhalerao, A.
-Sivaraman, G.
-Porter, and K., Winstein.
-“Encoding, Fast and Slow: Low-Latency Video Pro- cessing Using Thousands of Tiny Threads”.
-In: NSDI.
-Boston, MA: USENIX Association, 2017, pp.
-363–376.
-%A.
-Klimovic, Y.
-Wang, C.
-Kozyrakis, P.
-Stuedi, J.
-Pfefferle, and A.
-Trivedi.
-“Understanding Ephemeral Storage for Serverless Analytics”.
-In: USENIX ATC.
-Boston, MA: USENIX Associa- tion, 2018, pp.
-789–794.
-%. Wang, M. Li, Y. Zhang, T. Ristenpart, and M. Swift. “Peek- ing Behind the Curtains of Serverless Platforms”. In: USENIX ATC. Boston, MA: USENIX Association, 2018, pp. 133–146.
+The serverless framework~\cite{ref:serverless_framework} provides
+automated packaging and deployment for serverless functions across clouds. 
+The serverless framework uses CloudFormation\footnote{\url{https://aws.amazon.com/cloudformation/}} for deployment in AWS Lambda, which introduces additional cost. 
+The cloud infrastructure provisioning 
+framework Terraform\footnote{\url{https://www.terraform.io/}}
+also provides automated deployment of functions to serverless platforms
+(however, without replicating the Lambda runtim, introducing deployment errors).
+Seneca uses a local docker container to avoid this cost and overhead. 
+%In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous integration and delivery pipeline for serverless architectures, but it also introduces monetary cost overhead to do so.
 
-The serverless framework~\cite{ref:serverless_framework} contributes an 
-automated packaging and deployment toolset for serverless functions across clouds. 
-The serverless framework uses Cloudformation~\cite{ref:cloudformation} to package and deploy Lambda function, which introduces additional cost. Seneca uses local docker container to avoid this cost
-and overhead. The cloud infrastructure provisioning framework Terraform~\cite{ref:terraform} 
-also provides automated deployment of functions to serverless platforms, but it does not simulate the AWS Lambda runtime to create the deployment package (doing so on a non-Linux system will result in Lambda errors and failures at execution time).
-In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous integration and delivery pipeline for serverless architectures, but it also introduces monetary cost overhead
-to do so.
-
-Automated hyperparameter optimization has been researched and developed 
-in numerous projects. Google Vizier~\cite{ref:vizier} provides a service for 
+Automated hyperparameter optimization is the focus of
+many projects. Google Vizier~\cite{ref:vizier} provides a service for 
 black-box optimization. Optunity~\cite{ref:claesen2014hyperparameter} 
-proposes a Python library for hyperparameter tuning. 
-This can be considered as precursory work of Hyperopt~\cite{ref:hyperopt}, 
-which is a more advanced Python library for serial and parallel hyperparameter 
-optimization over awkward search space. Hyperas~\cite{ref:hyperas} adds another 
-abstraction layer to hyperopt and facilitates the hyperparameter tuning for 
-Keras~\cite{ref:keras}. However, no extant work of which we are aware leverages
-serverless to perform hyperparameter tuning in parallel.
+and Hyperopt\footnote{\url{http://hyperopt.github.io/hyperopt/}}
+provide a Python library for hyperparameter tuning. 
+%This can be considered as precursory work of Hyperopt~\cite{ref:hyperopt}, 
+%which is a more advanced Python library for serial and parallel hyperparameter 
+%optimization over awkward search space. 
+Hyperas\footnote{\url{http://maxpumperla.com/hyperas/}} adds another 
+abstraction layer to hyperopt to facilitate hyperparameter tuning for 
+Keras~\footnote{\url{https://keras.io/}}. However, no extant work of which we are aware leverages
+serverless to perform hyperparameter tuning and memory optimization in parallel 
+for ML applications.

### 2019-02-26 results.tex
chandras pass

--- 2019-02-25 results.tex
@@
 are shown in Table~\ref{tab:bmarks}, each with 
-a brief description.
+a brief description.  Prophet, Multi-Regression, and XGBoost are regression
+applications; XGBoost, SVC, and NN are classification applications (XGBoost 
+implements both regression and classification tasks).
+
 Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
@@
 of Peyton Manning's Wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
-The dataset exhibits both seasonality and a holiday effect (e.g. around the super bowl games). 
-We use the first 6 years as the training set and the last 2 years as the testing set.
-We use a cross-validation horizon (sliding window) of 1-year, 
+The dataset exhibits both seasonality and a holiday effect (e.g. around 
+super bowl games). 
+We use the first 6 years as the training set and the last 2 years as the testing set.  We use a cross-validation horizon (sliding window) of 1-year, 
 and a period (sliding pace) 
-of 180 days.  As such, Seneca performs three cross-validations for each 2-year testing range.
+of 180 days.  As such, Seneca performs three cross-validations for each 2-year test range.
 
@@
 Multi-Regression is a regression application developed as part of
-an Internet-of-Things (IoT) project~\cite{iot-cpu} (and extended
-from linear regression described in the citation, 
+an Internet-of-Things (IoT) project~\cite{iot-cpu} (which has been
+extended from linear regression described in the citation 
 to multiple linear regression by the authors of this prior work).
@@
 series of processor temperature measurements,
-to predict outdoor microclimate temperatures. % without using a temperature sensor.
-%(e.g. for use in 
-%precision agriculture applications such as irrigation control and frost protection).
-The training dataset consists of eight input time series (one per SBC, each containing 
+to predict outdoor microclimate temperatures. 
+The training dataset consists of eight input time 
+series (one per SBC, each containing 
 5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.
 
-A hyperparameter configuration for this application is a subset of input SBC time series.
+A hyperparameter configuration for this application is 
+a subset of input SBC time series.
 Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
 For this application,
-we assume the default parameterization is the full set of input time series (8 in this case).
-The test dataset for this application is a time series of the outdoor temperature (ground truth) 
-over the same period.  The application makes predictions for each of these outdoor temperatures
+we assume the default parameterization is the 
+full set of input time series (8 in this case).
+The test dataset for this application is a time 
+series of the outdoor temperature (ground truth) 
+over the same period.  The application makes 
+predictions for each of these outdoor temperatures
 using the regression coefficients constructed from the training set
-and computes the mean square error between predicted and ground truth value pairs.
+and computes and returns the MSE between predicted 
+and ground truth value pairs.
 
-XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
-performs both regression and classification. We consider it a regression application and
-a classification application in this evaluation.  
-The hyperparameters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found in~\cite{ref:xgboostparams}.
+XGBoost~\cite{ref:xgboost-web} is an open source 
+framework for gradient boosting, which 
+performs both regression and classification. 
+The hyperparameters and the default values that Seneca uses 
+in this study are listed in Table~\ref{tab:xgboost_para}. 
+A definition for each hyperparameter can be found in~\cite{ref:xgboostparams}.
 %xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
 
-Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
-based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
-The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found in~\cite{ref:svcparams}.
-%xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
+Support vector classification (SVC)~\cite{ref:svc} 
+is an implementation of a classification algorithm 
+that is based on support vector machines that is part of the
+libsvm~\cite{ref:libsvm} library.
+The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found in
+%svcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
+\footnote{\url{https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html}}.
 
-Neural network (NN)~\cite{ref:neural_network} is a machine learning framework that learns 
+Neural network (NN)~\cite{ref:neural_network} is a machine 
+learning framework that learns 
 and makes decisions from patterns in an input dataset. For this application, 
@@
 for the classification task.
-The hyperparameters and their defaults for NN are listed in Table~\ref{tab:nn_para}. 
+The hyperparameters and their defaults for NN 
+are listed in Table~\ref{tab:nn_para}. 
 A definition for each hyperparameter can be found in~\cite{ref:nnparams}.
@@
 features (those with an absolute value of the Pearson correlation coefficient
-greater than 0.8). The dataset has also been balanced by down-sampling and the resulting 
-dataset contains 33926 rows (individual fruit) distributed evenly to 5 targets and each row has
-18 features.  The label indicates which field the individual fruit was harvested from.  
-The application trains a model on a subset (80\%) of the
-data.  They then use this model to predict the field
+greater than 0.8). The dataset has also been balanced by 
+down-sampling and the resulting 
+dataset contains 33926 rows (individual fruit) 
+distributed evenly across 5 targets. Each row has
+18 features.  The label identifies the field from which the 
+individual fruit was harvested.
+
+The applications train a model on a subset (80\%) of the
+data.  Each then uses this model to predict the field
 from which each fruit originates (for the remaining 20\%). 
-
-The classification applications compute a classification accuracy score
+The applications compute a classification accuracy score
 as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
-prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
-is the indicator function. XGBoost also computes MSE for its regression task
-on the same datasets.
+prediction class, $Y_i$ is the true class, 
+$n$ is the number of samples, and 1(x)
+is the indicator function. The applications return the accuracy percentage
+upon completion. As mentioned above, in addition to returning
+classification accuracy for its classification task, XGBoost also returns 
+MSE for its regression task.
 
@@
 
-To evaluate Seneca, we measure tuning performance, application execution time and memory use,
-and monetary cost.  For tuning performance, we use mean squared error (MSE)
-for regression tasks and percentage accuracy for classification tasks (i.e. we score
-model prediction accuracy and not explanatory power).  Because we use the same 
-total number of hyperparameters for each model, the penalty function in terms of 
-Bayesian Information Criteria, is the same. Thus, we can compare models using
-this score.
+To evaluate Seneca, we measure tuning performance, application execution time, 
+memory use, and monetary cost.  For tuning performance, 
+we use mean squared error (MSE)
+for regression tasks and percentage accuracy for classification 
+tasks (i.e. we score model prediction accuracy and not explanatory power).  
+Seneca is able to compare models for each type of application using 
+these scores because it uses the same
+total number of hyperparameters for each model.  Thus, the
+the penalty function in terms of 
+Bayesian Information Criteria is the same.
 
@@
 above.  We report results for the default, best (Seneca's recommendation), and
-worst performing configurations.  Seneca computes all possible combinations of
+worst performing hyperparameter configurations for each application type.  
+Seneca computes all possible combinations of
 the hyperparameter settings specified in the configuration to extract each of
@@
 
-To evaluate the cost savings introduced by Seneca, we deploy the applications
-on Amazon Web Services (AWS) Lambda~\cite{ref:awslambda} and extract
+To evaluate the  savings introduced by Seneca, we deploy the applications
+on Amazon Web Services (AWS) Lambda and extract
 execution time and memory use from AWS CloudWatch~\cite{ref:awscloudwatch} logs.  
-We then compute monetary cost
-using the AWS Lambda pricing model~\cite{ref:pricing}.
+Seneca extracts execution time and memory use from AWS CloudWatch logs\footnote{\url{https://aws.amazon.com/cloudwatch/}}.
+We compute monetary cost
+using the AWS Lambda pricing model\footnote{\url{https://aws.amazon.com/lambda/pricing/}}.
 %awslambdapricing: https://aws.amazon.com/lambda/pricing/
 Each function downloads the training and testing dataset 
-of the application from AWS Simple Storage Service (S3)~\cite{ref:awss3} upon function invocation. 
-We do not consider the cost of dataset storage in our cost computations (it is very small).
+of the application from AWS S3 upon function invocation. 
+We do not consider the cost of dataset storage 
+in our cost computations (it is very small).
 
@@
 the maximum allocatable memory size to the performance and cost when run with
-Seneca's automatically determined memory size.
-Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we have verified the optimized allocated memory allows all hyperparameter settings run successfully.
+Seneca's automatically determined memory size. Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we 
+have verified that the optimized allocated memory is sufficient for all 
+hyperparameter configurations to complete successfully.
 
@@
 IQR)$}. The data points beyond the whiskers are considered outliers and are
-plotted as colored diamonds. The red notch identifies the MSE that results
+plotted as colored diamonds.
+
+The red notch identifies the MSE that results
 from training the model using the default settings of hyperparameter. The
@@
 through the use of Seneca. From the location of red notch, we can see the MSE
-metrics from default configuration in three applications are close to the
-first quartile value in all three cases (slightly greater that Q1 for Prophet
-and Multi-regression and slight less for XGBoost). However, Seneca's MSE
-performance is congruent with the end of the lower whisker.  Overall, however,
-the quality of the application's output (for a given dataset) is dramatically
-affected by hyperparameter settings.  Predictably the default settings are
+metrics from default configuration in three applications are similar to those
+in the first quartile for all applications.
+This data shows that the quality of the
+output generated by each application (for a given dataset) is dramatically
+affected by hyperparameter settings.  Predictably, the default settings are
 near the ``good'' end of the spectrum, but as both Table~\ref{tab:mse} and
@@
 
-The 80-20 case represents the typical usage of these classification
-applications. Often, when evaluating the accuracy of a specific classifier,
-the user uses the 80-20 split ``rule'' when measuring accuracy. In this case,
-Seneca's improvement over the default parameterizations varies from 2.46\% for XGBoost application (column 2), to 19.04\% for SVC
-(column 3).
+%not sure what this paragraph is adding, seems to a repetition of what
+%is already said above...
+%The 80-20 case represents the typical usage of these classification
+%applications. Often, when evaluating the accuracy of a specific classifier,
+%the user uses the 80-20 split ``rule'' when measuring accuracy. In this case,
+%Seneca's improvement over the default parameterizations varies from 2.46\% for XGBoost application (column 2), to 19.04\% for SVC
+%(column 3).
 
@@
 Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
-for the entire hyperparameter search space for each classification
-application.
-The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}.
+for the entire hyperparameter search space as a box plot for each classification
+application.  The placement of the rectangle and whiskers is the same
+as in Figure~\ref{fig:box_plot_mse}. 
+%The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. 
 The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
-For both types of applications (regression and classification), Seneca significantly
-improves tuning performance over the default and worst case configurations for SVC while generating a relatively small improvement over the default for XGBoost and Neural Network.
-This is because powerful classifiers, like XGBoost and Neural Network, can achieve fairly good accuracy by default setting, whereas weaker classifier, like SVC, requires more tuning to reach high accuracy.
+Again, Seneca significantly
+improves tuning performance over the default and worst case configurations for SVC while generating a smaller improvement for XGBoost and Neural Network versus the default.
+This is because XGBoost and NN use a well tuned default parameter
+set that works well for most datasets.  SVC benefits more from Seneca tuning
+that the others.
 
@@
 \input{tables/exec-time-memory-tab}
-\caption{The mean (stdev) values of execution time and memory use, and best accuracy across 30 executions of three classification benchmarks running against two random states.
+\caption{The mean and standard deviation (in parentheses) values of execution time and memory use, and best accuracy across 30 executions of three classification benchmarks running against two random states.
 It verifies data split does not have major impact to execution metrics and scores.
@@
 
-In order to investigate the potential impact from data split, we split the data for three classification applications by two random states, run Seneca 30 times and obtain execution time, memory use and best accuracy from AWS CloudWatch logs.
-As showed in Table~\ref{tab:exec_memory}, different data split has no major impact to these three values.
-It does not only mean the execution time and monetary cost are consistent given various data splits, but also indicates users do not have to run Seneca repetitively in the inference phase when new data are generated.
+To investigate the potential impact of the 80-20 data split for the classification
+applications, we next evaluate the quality of the output generated from 
+each when we consider different 80-20 random splits.
+To enable this, we run Seneca 30 times to obtain execution time, memory use, 
+and best accuracy score. 
+Table~\ref{tab:exec_memory} shows the mean and standard deviation of these 
+metrics across runs for two different random splits.  The Seneca score
+is similar across splits.  As a result, users can employ the models
+(for the selected hyperparameter settings) that Seneca recommends
+repeatedly for inference to amortize the cost of using Seneca.
 
@@
 
-Finally in this section, we contrast the execution time of Seneca with serial hyperparameter tuning process on EC2 instance across five applications.
-Since library compilation issue, we use t2.medium on Prophet and t2.micro on other 4 applications.
-As a result, Seneca achieves at least 4x speedup for IO-bound application (SVC) and 21x speedup for CPU-bound application (XGBoost).
+Finally, we compare Seneca to AWS EC2 use.
+We measure the execution time of Seneca and hyperparameter tuning 
+using the least expensive EC2 instance type in which the application
+will run (t2.micro for SVC and NN, t1.medium for the rest).  End to end, Seneca's
+concurrency facilitates in a 4x -- 17x (9x on average) speedup
+and \$0.01--\$0.34 (\$0.13) additional cost over serialized execution in EC2.
+EC2 trades off monetary cost for programmer productivity, i.e. the developer 
+must setup, deploy, and manage the applications manually. Moreover, the EC2
+pricing model is imposed on hour boundaries. Moreover, Seneca and 
+AWS Lambda impose no cost when no execution is occuring (EC2 instances must
+stay idle in between runs). As part of future work, we will compare Seneca
+to the AWS Elastic Container Service.
+%\textcolor{blue}{FIX THIS: State the results (speed up) per application and 
+%also state the cost analysis for 1 hour of computation.  Clarify that this
+%is due to the 1-hour pricing model of EC2.}
+
+%We use instance type t2.medium
+%for Prophet (since it cannot be built
+%process on EC2 instance across five applications. Since library compilation issue, we use t2.medium on Prophet and t2.micro on other 4 applications. 
+%As a result, Seneca achieves at least 4x speedup for IO-bound application (SVC) and 21x speedup for CPU-bound application (XGBoost).
 It confirms Seneca can execute tuning within a more reasonable period of time, comparing to executing serially on EC2 instance.
@@
 
-% To do so, we use Seneca to find the hyperparameterization that optimizes application output
-% quality (lowest MSE for regression, highest accuracy for classification).
-% For each hyperparameterization that Seneca evaluates, it incurs a
-% cost. Furthermore, the amount of memory used by Seneca during memory
-% tuning also influences overall cost.
+We next analyze the monetary cost incurred by Seneca with and without 
+Seneca's memory optimization.
+We consider the use of the maximum allocatable memory (3GB) and Seneca's 
+automatic detection and configuration of allocated memory.
+This optimization requires
+that Seneca intelligently probe to determine the best memory size 
+to use.  We report the cost of these probes as \texttt{Optimizer Cost}.
 
-We next analyze the monetary costs incurred by Seneca. Instead of trying out all possible settings,  we compare two
-Seneca execution configurations.  In the first 
-we configure each lambda function to
-use the maximum amount of memory allowed by AWS Lambda (3008 MB) for all
-executions.
-Second, we employ Seneca's memory optimization which automatically detects and configures
-the amount of memory needed by each function.  This optimization requires
-Seneca to ``probe'' to determine the best memory size to use.  The
-cost of these probes
-(denoted ``Optimizer Cost'') must be taken into account as well.
-%Because memory impacts both
-%cost and execution time (total latency of Seneca hyperparameter tuning), we
-%present empirically evaluate both in this subsection.  
-Note that XGBoost's performance profile is identical when used for regression
-or classification so we include its measurements only once in the following
-analysis.
-%For each, we only
-%include XGBoost once since its performance profile is the same regardless of
-%whether we are using regression or classification.
+Table~\ref{tab:cost_optimized} shows the results with and without
+the Seneca memory optimization. 
+The five columns identify the benchmark applications.
+Because the performance profile of XGBoost is the same for regression
+or classification, we include its metrics once.
+The first two rows show the results when we use the maximum allocated memory 
+for the Lambda functions. We present execution time in minutes (row 1) and 
+monetary cost (row 2).
 
-Tables~\ref{tab:cost_optimized} shows the results with and without 
-the Seneca memory optimization, respectively.
-The five columns identify the benchmark applications and the first row is the total execution time in minutes and the second row is total cost of tuning when Seneca's lambda functions are configured to use the maximum amount of memory (3008 MB).
-For optmized memory configuration, fourth row shows the cost of the memory optimizer in the
-second row, Seneca's cost using the optimization in the fifth row, and total cost on sixth row.
-Finally, in the seventh and eighth rows of Table~\ref{tab:cost_optimized} we show the
-savings that memory optimization introduces over using the maximum memory in dollar cost and as a percentage respectively.
+Rows 3--6 show the performance and cost impact of using Seneca's memory optimization.
+is the execution time in minutes 
+\texttt{Exec time opt} is the execution time in minutes.
+\texttt{Optimizer Cost} is monetary cost of Seneca's memory size detector.
+\texttt{Cost opt} is monetary cost of using Seneca and the memory size
+it identifies and recommends.
+\texttt{Total cost} is the sum of \texttt{Optimizer Cost} and \texttt{Cost opt}, i.e., the total cost of using Seneca to perform hyperparameter tuning for these applications and data sets.
+The last two rows show the monetary savings (row 7) and percent savings (row 8) u
+of using Seneca's memory optimization.  Seneca's memory optimization reduces
+the monetary cost of its use from 10--30\% (20\% on average).
 
@@
 \input{tables/seneca-mem-opt-tab.tex}
-\caption{Seneca Memory Optimization: First two rows show the execution time and  monetary cost of using Seneca at max memory (3008 MB).
-Row 3-6 show the execution time and cost when the amount of memory used for each function invocation is automatically inferred and set by Seneca.
-Row 7-8 show savings by dollar and percentage.
+\caption{Seneca Memory Optimization: Rows 1--2 show the execution time and  monetary cost of using Seneca without its memory optimization.
+Rows 3-6 is the execution time and cost, respectively, when Seneca detects and sets allocated memory for the application functions automatically.
+Rows 7-8 show the savings by dollar and percentage.
 \label{tab:cost_optimized}}
@@
 
-Table~\ref{tab:cost_optimized} illustrates two important cost features of Seneca.  First, using
-AWS Lambda, full hyperparameter space exploration is not expensive in 
-\textit{absolute} dollar cost terms.  Even using the maximum memory available
-for almost 25 minutes of execution time (cf Prophet in Table~\ref{tab:cost_optimized}), the
-total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
-optimizations produce a significant percentage savings which, over repeated
-executions, is important.
+Table~\ref{tab:cost_optimized} illustrates two important points.
+First, using AWS Lambda, full hyperparameter space exploration is not expensive in 
+\textit{absolute} dollar cost terms and Seneca's automatic memory size optimization
+decreases this cost further.  Second, this optimization reduces cost but can 
+increase the total execution time for parameter search 
+since the functions must operate under additional memory 
+constraints (versus using the maximum allocated memory).  
+In addition, this cost fluctuates depending on the quality of the Lambda
+execution environment (number of CPUs, Linux container overhead, 
+multitenency, etc.).  We omit the data due to space constraints.
+However, the average absolute difference in cost
+across the five applications (30 runs) is \$0.050. %I use only split 1 for all 5
+%numbers are below
+Moreover, the highest cost of execution under 
+optimized memory is still cheaper than the lowest cost of execution 
+under maximum memory for all five benchmarks.  
+%$	Ave Cost	Highest Cost	Lowest Cost	Diff (High - low)
+%Prophet	0.215	0.294	0.178	0.116
+%Multi_Reg	0.076	0.078	0.075	0.003
+%SVC_1	0.015	0.015	0.015	0.001
+%SVC_2	0.014	0.016	0.013	0.003
+%XGBoost_1	0.586	0.632	0.510	0.122
+%XGBoost_2	0.607	0.630	0.569	0.061
+%NN_1	0.055	0.059	0.051	0.007
+%NN_2	0.058	0.061	0.056	0.005
 
-Note also that Seneca's memory/cost optimization
-introduces at an execution time penalty (relative to the maximum memory
-execution) for some of the applications.  That is, the
-execution times for all applications increase when Seneca chooses
-a memory size.  Thus while Seneca is finding the best application output
-quality and optimizing the cost of producing that output, it is doing so at
-the expense of execution performance (time to solution). Such a penalty
-is expected due to the proportional CPU power to allocated
-memory. However, the Seneca optimizer is able to find the optimal
-memory configuration to minimize that  penalty.
+Overall, given the AWS Lambda cost model and its performance variability, 
+Seneca is still able to find the sweet spot between cost 
+and execution time. Thus Seneca can be used to trade off time-to-solution for
+cost as desired by users.
+
+%Even using the maximum memory available
+%for almost 25 minutes of execution 
+%time (cf Prophet in Table~\ref{tab:cost_optimized}), the
+%total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
+%optimizations produce a significant savings to further reduce its cost.
+%
+%Note that Seneca's memory/cost optimization
+%can introduce an execution time penalty (relative to the maximum memory
+%execution) for some of the applications.  
+%That is, the
+%execution times for all applications increase when Seneca chooses
+%a memory size.  Thus while Seneca is finding the best application output
+%quality and optimizing the cost of producing that output, it is doing so at
+%the expense of execution performance (time to solution). Such a penalty
+%is expected due to the proportional CPU power to allocated
+%memory. However, the Seneca optimizer is able to find the optimal
+%memory configuration to minimize that  penalty.
 In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has almost the same execution time (1.91 vs 1.95 minutes).
@@
 %However regardless of the cause, 
-Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.
+%Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.
 
-To corroborate the cost-effectiveness of Seneca, we analyzed the total cost of five benchmarks in 30 executions from last section.
+%To corroborate the cost-effectiveness of Seneca, we analyzed the total cost of five benchmarks in 30 executions from last section.
 We observe the reported \textit{billed duration} and \textit{max memory used} oscillate that leads to different total cost across 30 executions and we assume it is because the pagination and memory sampling method used by different AWS Lambda host servers.
-However, even taking fluctuation into account, the highest cost of execution under optimized memory is still cheaper than the lowest cost of execution under maximum memory in all five benchmarks.
+However, even taking fluctuation into account, the
+%highest cost of execution under optimized memory is still cheaper than the lowest cost of execution under maximum memory in all five benchmarks.
 We believe Seneca's optimizer is economical despite the locality of lambda container and application.

### 2019-03-01 Seneca.tex
mz - Michael's pass

@@
 \includegraphics[scale=0.08]{Seneca}
-\caption{The architecture of Seneca. 
-User specifies hyperparameter options in the configuration file and provides lambda function.
+\caption{The Seneca Architecture.
+%Users specify hyperparameter options in the configuration file and provides lambda function.
 Seneca automatically package, deploy and optimize lambda function on AWS before completing grid search process and selecting best hyperparameter setting.
 \label{fig:seneca}}
-% \vspace{-0.2in}
+\vspace{-0.2in}
 \end{figure}
@@
 shows the architecture of Seneca.  In the the upper-right-front, we
-show the three inputs that Seneca expects from its users: a hyperparameter
-configuration file, a dataset URL, and the path to 
-the machine learning application.
-The configuration file
-specifies the range of values for each hyperparameter that the 
-application expects.  Seneca uses this configuration to construct
-the hyperparameter search space.  The dataset URL refers to a
-valid dataset stored in the AWS Simple Storage 
-Service (S3)\footnote{\url{https://aws.amazon.com/s3/}}.
+show the three inputs that Seneca expects from its users: (\textit{A}) a hyperparameter
+configuration file, (\textit{B}) a dataset URL, and (\textit{C}) the lambda function of machine learning application.
+The configuration file specifies the range of values for each hyperparameter that the application expects.
+Seneca applies Cartesian product to all options in this configuration to construct the search space.
+The dataset URL refers to a valid dataset stored in the AWS Simple Storage
+Service (S3)~\cite{ref:awss3}.
+%\footnote{\url{https://aws.amazon.com/s3/}}.
 
-Seneca automatically builds and deploys a AWS Lambda application
-from the machine learning application specified.
+Seneca automatically builds and deploys an AWS Lambda application from the machine learning application specified.
 To do so, Seneca launches a docker container that mirrors the
@@
 the machine learning application and any libraries it requires,
-and compresses the application and uploads it to S3 (avoiding
-the AWS Lambda handler size restriction of 10MB).
-Seneca constructs an AWS Lambda handler from a template
-that, when executed, will download and uncompress the application,
-download the dataset and split it into a training and testing set,
-and construct, test, and evaluate a model using the application
+and compresses the application and uploads it to S3 (a work-around
+for the 10MB AWS Lambda function size restriction).
+Seneca constructs an AWS Lambda function from a template
+that, when executed, will download the dataset and split it into a training and testing set, and construct, test, and evaluate a model using the application
 and a set of hyperparameter values passed in by Seneca as arguments.
-Users can specify the train/test split that should be used by Seneca; the
+Users can specify the train/test split ratio that should be used by Seneca; the
 default is 80\%/20\% for classification tasks.
-The handler returns a testing score. 
-Upon completion of this process, the container deploys the handler
+The function returns a testing score. 
+Upon completion of this process, the container deploys the function
 to AWS Lambda using the
-AWS Command line Interface\footnote{\url{https://aws.amazon.com/cli/}} 
+AWS Command Line Interface~\cite{ref:awscli}
+%\footnote{\url{https://aws.amazon.com/cli/}} 
 and the developers credentials.
@@
 
-The AWS Lambda pricing model is determined by the execution duration 
-and memory of each invoked function. The cost of a function instance is referred to as 
-the \texttt{compute charge}, which is the allocated memory 
-multiplied by the
-billed duration (execution time rounded up to the 
-nearest 100ms)~\footnote{\url{https://aws.amazon.com/lambda/pricing/}}.
-%https://aws.amazon.com/lambda/pricing/
-To ensure that we keep the cost of Seneca as low as possible, we investigate
-the impact of this pricing model on application execution and use
-our findings to optimize cost.
+The cost of using AWS Lambda (i.e. \texttt{compute charge}) 
+is the billed duration (execution time rounded up to the
+nearest 100ms)~\cite{ref:pricing}
+%~\footnote{\url{https://aws.amazon.com/lambda/pricing/}}
+multiplied by the allocated memory of each invoked function.
+One goal of our work is to optimize memory use by these
+applications in order to reduce cost, and to investigate
+the trade offs of doing so.
 
@@
 from 128MB to 3008MB in increments of 64MB.
-AWS documentation~\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/resource-model.html}} 
-states that Lambda 
-allocates CPU in a way that is proportional to allocated memory size,
+AWS documentation~\cite{ref:lambdalimits}
+%~\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/resource-model.html}} 
+states that Lambda allocates CPU to functions proportionally to allocated memory size,
 as is done for general purpose AWS EC2 instance types.
@@
 
-To evaluate the impact of memory and CPU allocation on application cost,
-we analyze a 3-D matrix multiple serverless benchmark~\cite{ref:matrix} using AWS Lambda.
-We configure function instances to use the 46 possible allocated 
-memory increments, invoke them, and record the billed duration and memory used by each.
-Figure~\ref{fig:memory} shows the relationship between allocated memory 
+To evaluate the relationship between memory, CPU, and cost, 
+we analyze a 3-D matrix multiplication serverless benchmark~\cite{ref:matrix} using AWS Lambda.
+We configure different functions to use each of the 46 possible allocated memory 
+options.  Figure~\ref{fig:memory} shows the relationship between allocated memory 
 (x-axis) and reciprocal of billed duration (y-axis). 
@@
 size (x-axis) and compute charge (y-axis). 
-We observe that for this benchmark,
-the CPU power plateaus after 1600 MB. 
-Correspondingly, the compute charge declines from 128 MB to 1600 MB 
-and then increases linearly.
+We observe that for this benchmark, billed duration 
+plateaus after 1600 MB, at which point compute charge increases.
+That is, we achieve no further execution time benefit (only cost increase)
+after this point.
 
-These findings show that CPU does not increase proportionally with
-an increase in allocated memory.  We use this relationship within
-Seneca to optimize its cost (compute charge) via an extension
+We use this relationship within
+Seneca to optimize its cost (\texttt{compute charge}) via an extension
 that enables it to automatically identify the appropriate
@@
 However, instead of exhaustively testing all 46 possible 
-memory configurations, which might be costly,  
-Seneca employs the heuristic outlined in
+memory configurations as we did for the matrix benchmark, 
+which may be costly,  Seneca employs the heuristic outlined in
 Algorithm~\ref{algo:optimizer}.
 
-The Seneca optimizer first configures and invokes the function using 
-a user-defined payload.  From this run, Seneca obtains the memory 
-used by function (reported by AWS Cloudwatch), 
+The Seneca optimizer first configures and invokes the function using a user-defined payload.  From this run, Seneca obtains the \texttt{maximum memory used}
+by function reported by AWS Cloudwatch,
 which it uses as its starting point.
 Seneca then defines two double-ended queues 
-(\texttt{deque}) of length N, to store 
-allocated memory and compute charge data of different
-invocations. While the current 
+(\textit{deque}) of length N, to store 
+\texttt{allocated memory} and \texttt{compute charge} data of different invocations. While the current 
 allocated memory is less than or equal to 3008 MB, 
@@
 
-We employ two exit conditions.  The first is when the 
-compute charge monotonically increases across \texttt{deque}. 
+We employ two exit conditions.
+The first is when the  compute charge monotonically increases across \textit{deque}.
 The second is when the increase in slope is greater than a threshold.
-Once the optimizer finds that both conditions hold, 
-it pops the left-most value from \texttt{deque} and configures 
-the function to use that value for allocated memory for all future invocations.
-After extensive experimentation, we find that 
-N=5 and a slope threshold of 1 work well in most cases.
-These values can be changed by users of the system however.
-In addition, this optimization can be turned on or off via a command line
-argument to Seneca.
+When the optimizer finds that both conditions hold, it pops the left-most value from \textit{deque} and configures the function to use that value for allocated memory for all future invocations.
+If these two conditions can not be satisfied through search, the allocated memory will be configured as the memory size that results in minimal compute charge within the \textit{deque}.
+After extensive experimentation, we find that $N=5$ and a slope threshold of 1 work best, but these values are configurable.
+In addition, this optimization can be turned on or off via a command line argument to Seneca.
 
 \begin{algorithm}[]
+\caption{Seneca Optimizer Heuristic}
+\label{algo:optimizer}
 \SetAlgoLined
@@
  \While{allocated memory $\leq$ 3008 MB}{
-
-  \eIf{compute charge monotonically increases in deque \& slope $\geq$ 1}{
-   Popleft from deque\;
-   Configure allocated memory of function\; 
-   Exit\;
+  \eIf{compute charge monotonically increases in deque \& slope $\geq$ threshold}{
+   popleft from deque\;
+   configure allocated memory as optimum\;
+   exit()\;
    }{
-   Increase allocated memory by 64 MB\;
-   Probe lambda function\;
-   Append allocated memory and compute charge to deque\;
+   increase allocated memory by 64 MB\;
+   probe lambda function\;
+   append memory and compute charge to deque\;
   }
  }
- \caption{Seneca Optimizer Heuristic}
- \label{algo:optimizer}
 \end{algorithm}
@@
 
-For parallel function invocation, Seneca integrates 
-Celery~\cite{ref:celery}. Celery is an asynchronous task queue 
+To facilitate parallel function invocation, Seneca integrates 
+Celery~\cite{ref:celery}.
+%\footnote{\url{http://www.celeryproject.org/}}
+Celery is an asynchronous task queue 
 that uses distributed message passing. Celery workers are processes 
@@
 and store the result that is returned 
-in a database (we use Redis~\footnote{\url{https://redis.io/}} in our prototype).
+in a database (we use Redis~\cite{ref:redis}
+%~\footnote{\url{https://redis.io/}} 
+in our prototype).
 
-Based on the configuration file, Seneca creates a list of 
-payloads (function arguments) with
-hyperparameter values.  
-The complete list contains all combinations of the specified parameter
-settings.  Seneca places the list on the queue and celery 
-workers invoke the Lambda handler of the application, passing in the
-payload (hyperparameter values) to the handler to use for model construction.  
-Upon function
-termination, the worker records the evaluation score (and serialized model)
-in the database with the hyperparameter configuration from the payload.
-When the queue is drained and all workers have completed, Seneca
-extracts and reports the best score, configuration, and model from the database.
-Users can then evaluate the prediction power of the models (using Seneca if desired) 
-for other datasets (to amortize the time/cost of Seneca) without retraining.
+Based on the configuration file, Seneca creates and enqueues a list of 
+payloads (function arguments) for each combination of hyperparameter values.  
+The Seneca celery workers invoke the application's Lambda function by each payload for model construction. Upon function termination, the worker records a score for the hyperparemeter configuration
+in the database.
+When the queue is drained and all workers have completed, Seneca extracts and reports the best score, configuration, and model from the database.
+Users can then use the model for inference given other datasets without retraining to amortize the time/cost of Seneca.
+% Users can then evaluate the prediction power of the models (using Seneca if desired) 
+% for other datasets without retraining to amortize the time/cost of Seneca.
 
-We assume that the dataset supplied to Seneca by the user
-is representative of datasets on which the 
+We assume that the dataset supplied to Seneca by the user is representative of 
+datasets on which the 
 resulting model will be used.  In addition, we use prediction error as the 
@@
 As part of future work, we are considering using multiple datasets and a ranges
-of hyperparameter values (versus lists) to preclude the need for users to specify
+of hyperparameter values to preclude the need for users to specify
 them and to consider a wider range of values.

### 2019-03-01 abstract.tex
mz - Michael's pass

@@
 using autoscaled cloud computing systems and services.
-To enable this, we develop an open source system, called Seneca, that leverages
+To enable this, we develop an open source system, Seneca, that leverages
 the serverless programming model and its implementation in Amazon Web Services
@@
 Moreover, its memory optimization reduces the cost of using Seneca 
-by 10-30\% for the applications studied.
+by 10--35\% for the applications studied.
 

### 2019-03-01 conclusion.tex
mz - Michael's pass

@@
 We present a new framework, called Seneca, for simplifying and expediting
-the training and testing of machine learning models
-using low cost cloud services.
-Specifically, Seneca leverages the AWS Lambda for autoscaled
-(elastic) and parallel execution of hyperparameter search 
-and selection for machine learning models.  
+the training and testing of machine learning models in AWS Lambda.
+%using low cost cloud services.
+%Specifically, Seneca leverages the AWS Lambda for autoscaled
+%(elastic) and parallel execution of hyperparameter search 
+%and selection for machine learning models.  
 Users provide Seneca with the application code and 
@@
 Seneca uses this information to automatically
-configure and deploy these functions in parallel for all possible 
+configure and deploy these functions concurrently for all possible 
 combinations of hyperparameter values specified. Seneca
 returns the best scoring model
-and configuration to the user (for future use on other datasets).
+and configuration to the user for future use on other datasets.
 
@@
 for the applications and datasets that we consider.  
-We also show that Seneca memory optimization reduces the cost of using
-Seneca by 10-30\% for the applications studied.
+We also find that Seneca enables average speedups
+of 294x for each additional dollar spent, and
+that its memory optimization reduces the cost of using
+Seneca by 10-35\% for the applications studied.

### 2019-03-01 intro.tex
mz - Michael's pass

--- 2019-02-25 intro.tex
@@
 than for elastic applications.
-The reason for this is that it is challenging to configure complex
+The reason is that it is challenging to configure complex
 distributed systems for application use, 
@@
 to significantly simplify cloud use.
-%and broaden participation (by less expert
-%users) in the use of cloud systems.
-%xxx: http://shivaram.org/publications/pywren-socc17.pdf
-%yyy: http://cidrdb.org/cidr2019/papers/p119-hellerstein-cidr19.pdf
-%zzz: L. Wang, M. Li, Y. Zhang, T. Ristenpart, and M. Swift. “Peek- ing Behind the Curtains of Serverless Platforms”. In: USENIX ATC. Boston, MA: USENIX Association, 2018
 
-Using the serverless model, application developers upload 
-arbitrary computations in high level languages
-as stateless functions to cloud-hosted, serverless platforms.
-Functions are invoked (i.e. triggered)
-automatically by the cloud in response to updates to other cloud services
-(e.g. storage, queues, notification services, and API gateways, among others), which 
-the developer configures. Serverless functions
+Using the serverless model, application developers upload arbitrary computations in high level languages as stateless functions to cloud-hosted, serverless platforms, where functions are triggered automatically by the cloud in response to updates from other cloud services (e.g.
+storage, queues, notification services, and API gateways,
+among others). Serverless functions must execute under a time bound (e.g. 15 minutes) and an allocated memory size 
+(e.g. 3GB) or else the platform will terminate the function. They
 communicate, persist, and access data only 
-through their inputs or via shared, storage services.  
-As a result, serverless applications are inherently elastic and can 
+through their inputs or via shared storage services. As a result, serverless applications are inherently elastic and can 
 implement highly concurrent and parallel tasks.
@@
 source for private cloud systems, 
-Amazon Web Services (AWS) Lambda\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf}} %~\cite{ref:awslambdadg} 
+Amazon Web Services (AWS) Lambda~\cite{ref:awslambdadg}
+%\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf}}
 was the first and is the most widely used
@@
 In this work, we investigate the efficacy of using AWS Lambda
-for tuning machine learning applications.
+for tuning machine learning applications in parallel.
 To date, Lambda is not widely used for training and evaluating
@@
 Users can employ this model for other datasets
-(with Seneca if desired) without retraining the model to amortize the cost
-of Seneca further.
+(with Seneca if desired) without retraining the model to amortize the cost of Seneca further.
 
 We deploy Seneca on AWS Lambda and evaluate its tuning performance, cost,
-and memory use for six machine learning applications and datasets. We 
+and memory use for five machine learning applications and datasets. We 
 find that Seneca is fast, inexpensive, and effective for model 
@@
 best memory configuration for each application, further lowering its cost
-by 10-30\%.
+by 10-35\%. Relative to execution in AWS EC2, Seneca enables average speedups of 294x for each additional dollar 
+spent for the applications and datasets we consider.
 We intend to make Seneca, its applications, and their datasets publicly available
-when/if this paper is accepted for publication.  In the sections
-that follow, we overview our design and implementation of Seneca and then
+when/if this paper is accepted for publication.  
+We next overview our design and implementation of Seneca and then
 present our empirical methodology and results.
-
-\ignore{
-Recent work~\cite{ref:onesteptwostep} argues however that AWS Lambda
-
-Serverless~\cite{ref:serverless} computing is a rising function-based (also known as Functions-as-a-Service~\cite{ref:faas}) programming and deployment paradigm on top of cloud infrastructure, in which programmers manifest business logic without concerning provisioning servers by modular functions that are triggered by incoming events and return computation results in serialized format like XML or JSON.
-Such events include HTTP requests from clients, possibly proxied by API Gateway, or communications between cloud services based on heterogeneous protocols.
-Depending on the supported runtimes from cloud vendors, functions could be written in various high-level languages (i.e.
-NodeJS, Python, Java, etc.) and take advantage of serverless SDK to interact with other cloud services.
-Until recently, the leading serverless platform, Amazon Web Services(AWS) Lambda, expands language support by custom runtime~\cite{ref:customruntime} where software engineers can implement functions by any programming languages.
-
-Primarily, there are four evolutionary advantages that serverless architecture brings to cloud computing.
-First and foremost, it raises the abstraction layer from virtual machines to function containers~\cite{ref:container} that abstracts away the responsibilities of infrastructure management from DevOps~\cite{ref:devops} personnel to the cloud provider, in terms of scaling, patching, provisioning, error-handling and terminating underlying bare metal servers or clusters.
-Such shift allows more agile development life cycle and more product-oriented programming iteration.
-Secondly, the event-driven and paralleled container runtime of serverless function provides more fine-grained computational resource isolation and usage.
-Hence, serverless architecture makes cloud operation more secure and energy-efficient compared to traditional virtual machine instance runtime.
-Thirdly, serverless architecture decomposes monolithic application code base even further from microservices~\cite{ref:microservices} into granular functions, which are easier to be created, maintained and refactored by team or individual programmer.
-Furthermore, Function-as-a-Service applications could be autoscaled independently with respect to modular functions depending on the volume of request.
-This capability also contributes to the energy efficiency and eliminating throttling bottlenecks.
-Lastly, serverless computing provides "Pay-per-execution" pricing model~\cite{ref:pricing}.
-In a real world case study~\cite{ref:serverless_econ}, the server operational cost on serverless platform could be reduced dramatically, given a relatively lower amount of Transactions Per Second (TPS).
-According to these merits, the stateless, event-driven and embarrassingly parallel tasks are potentially cost-effective with lower latency by running on serverless framework.
-}

### 2019-03-01 related_work.tex
mz - Michael's pass

@@
-We next overview related work. We discuss contributions that focus
-on serverless computing, automatic packaging, 
-and machine learning (ML) model optimization.
-
-Multiple researchers have investigated the efficacy and overhead of the
+As related work, we consider recent advances
+in evaluating serverless computing for different application domains, 
+automatic deployment for serverless, and machine learning (ML) model optimization. 
+For the former, much work has investigated the efficacy and overhead of the
 serverless programming model and 
@@
 %serverless for data-intensive computing.  
-They identify some weaknesses in AWS
-Lambda for data-intensive computing, including the inability to 
-effectively train models.
-Our work shows that it is possible and cost effective to use
-AWS Lambda to train models for the subset of ML applications that we 
-consider.
+The authors identify challenges with 
+using AWS Lambda to train machine learning (ML) models.
+Our work however, shows that it is possible to leverage the concurrency 
+and parallelism in AWS Lambda to perform fast grid search for the
+subset of ML applications that we consider.
 
-PyWren~\cite{ref:jonas2017occupy} shows that stateless functions
-are a natural fit for distributed computing models. The technique
-abstracts away cluster management overhead and is ideal for 
-embarrassingly parallel jobs.  ExCamera~\cite{ref:encoding} presents a 
-framework for running general-purpose parallel tasks (encoding 4K video) 
-on a commercial serverless platform using multithreading. 
-Cirrus~\cite{ref:jonas2019cloud} attempts to train ML models 
-using a parameter server and serverless functions. 
-An empirical comparison of resource utilization and performance isolation
-is provided in~\cite{ref:peeking} for AWS Lambda, 
-Azure Functions, and Google Cloud Functions.
+PyWren~\cite{ref:jonas2017occupy} uses serverless for
+different distributed computing models. The technique abstracts away cluster management overhead and is ideal for embarrassingly parallel jobs.
+ExCamera~\cite{ref:encoding} presents a framework for running general-purpose parallel tasks (encoding 4K video) on a commercial serverless platform using multithreading.
+Cirrus~\cite{ref:jonas2019cloud} attempts to train ML models using a parameter server and serverless functions.
+%An empirical comparison of resource utilization and performance isolation
+%is provided in~\cite{ref:peeking} for AWS Lambda, 
+%Azure Functions, and Google Cloud Functions.
 
@@
 automated packaging and deployment for serverless functions across clouds. 
-The serverless framework uses CloudFormation\footnote{\url{https://aws.amazon.com/cloudformation/}} for deployment in AWS Lambda, which introduces additional cost. 
+GammaRay~\cite{gammaray18} does so for AWS Lambda to insert profiling instrumentation.
+The serverless framework uses 
+CloudFormation~\cite{ref:cloudformation} for deployment in AWS Lambda, which introduces additional cost. 
 The cloud infrastructure provisioning 
-framework Terraform\footnote{\url{https://www.terraform.io/}}
-also provides automated deployment of functions to serverless platforms
-(however, without replicating the Lambda runtim, introducing deployment errors).
-Seneca uses a local docker container to avoid this cost and overhead. 
+framework Terraform~\cite{ref:terraform}
+also provides automated deployment of functions to serverless platforms.
+%(however, without replicating the Lambda runtime, introducing deployment errors).
+Seneca uses a local docker container to avoid  cost and overhead (vs these related
+works), which guarantees execution compatibility for AWS Lambda. 
 %In addition, AWS CodeDeploy~\cite{ref:codedeploy} serves as component in the continuous integration and delivery pipeline for serverless architectures, but it also introduces monetary cost overhead to do so.
 
-Automated hyperparameter optimization is the focus of
+Automated hyperparameter tuning is the focus of
 many projects. Google Vizier~\cite{ref:vizier} provides a service for 
 black-box optimization. Optunity~\cite{ref:claesen2014hyperparameter} 
-and Hyperopt\footnote{\url{http://hyperopt.github.io/hyperopt/}}
+and Hyperopt~\cite{ref:hyperopt}
 provide a Python library for hyperparameter tuning. 
@@
 %optimization over awkward search space. 
-Hyperas\footnote{\url{http://maxpumperla.com/hyperas/}} adds another 
+Hyperas~\cite{ref:hyperas} adds another 
 abstraction layer to hyperopt to facilitate hyperparameter tuning for 
-Keras~\footnote{\url{https://keras.io/}}. However, no extant work of which we are aware leverages
+Keras~\cite{ref:keras}. However, no extant work of which 
+we are aware leverages
 serverless to perform hyperparameter tuning and memory optimization in parallel 

### 2019-03-01 results.tex
mz - Michael's pass

@@
 \input{tables/application-tab}
-\caption{Machine learning applications used as benchmarks
+\caption{Machine learning applications used 
 to evaluate Seneca. 
@@
 \label{tab:bmarks}}
-%\vspace{-0.2in}
+\vspace{-0.1in}
 \end{table}
@@
 \input{tables/hparams-prophet-tab}
-\caption{The hyperparameters that Seneca considers for Prophet. 
-The default value and tuning options are listed. 
+\caption{Hyperparameters Seneca considers for \textbf{Prophet}. 
 \label{tab:prophet_para}}
-%\vspace{-0.2in}
+%\vspace{-0.1in}
 \end{table}
@@
 \centering
-%\scriptsize
 \input{tables/hparams-xgboost-tab}
-\caption{The hyperparameters that Seneca considers for XGBoost. 
-The default value and tuning options are listed. 
+\caption{Hyperparameters Seneca considers for \textbf{XGBoost}. 
 \label{tab:xgboost_para}}
-%\vspace{-0.2in}
+\vspace{-0.2in}
 \end{table}
@@
 \input{tables/hparams-svc-tab}
-\caption{The hyperparameters that Seneca considers for SVC. 
-The default value and tuning options are listed. 
+\caption{Hyperparameters Seneca considers for \textbf{SVC}. 
 \label{tab:svc_para}}
@@
 \input{tables/hparams-nn-tab}
-\caption{The hyperparameters that Seneca considers for NN.
-The default value and tuning options are listed. 
+\caption{Hyperparameters Seneca considers for \textbf{NN}.
 \label{tab:nn_para}}
@@
 
-In this section,
-we evaluate Seneca in terms of performance, monetary cost, 
-and hyperparameter tuning execution time, 
-for different machine learning applications.
-We first overview these applications and our empirical methodology. 
-We then present our experimental results.
+In this section, we empirically evaluate Seneca in terms of machine learning (ML) 
+model output quality, performance, and cost.
+We first overview the ML applications 
+that we consider and our experimental methodology. 
+We then present our results.
 
 \subsection{Benchmark Applications and Training/Testing Datasets}
-The machine learning applications that we use to evaluate Seneca 
-are shown in Table~\ref{tab:bmarks}, each with 
-a brief description.  Prophet, Multi-Regression, and XGBoost are regression
-applications; XGBoost, SVC, and NN are classification applications (XGBoost 
+The ML applications that we use to evaluate Seneca 
+are described in Table~\ref{tab:bmarks}.
+Prophet, Multi-Regression, and XGBoost are regression
+applications; 
+XGBoost, SVC, and NN are classification applications (XGBoost 
 implements both regression and classification tasks).
+The regression applications compute the mean square error (MSE) 
+as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, 
+$Y_i$ is model prediction and n is the number of data points. The applications
+return the average MSE across cross validations.
+The classification applications compute and return a classification accuracy 
+percentage, which is calculated
+as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
+prediction class, $\hat{Y_i}$ is the true class, $n$ is the number of samples, and 1(x) is the indicator function.
 
-Prophet~\cite{ref:prophet} is a time series analysis library built and maintained by Facebook and the open-source community. The input dataset is a time series of view counts
-%logorithm
-of Peyton Manning's Wikipedia page from Dec. 10th, 2007 to Jan. 20th, 2016. 
+Prophet~\cite{ref:prophet} is an open source time series analysis library developed
+by Facebook.  The input dataset we consider is a time series of view counts
+of Peyton Manning's Wikipedia page (Dec. 2007--Jan. 2016).
 The dataset exhibits both seasonality and a holiday effect (e.g. around 
-super bowl games). 
-We use the first 6 years as the training set and the last 2 years as the testing set.  We use a cross-validation horizon (sliding window) of 1-year, 
-and a period (sliding pace) 
-of 180 days.  As such, Seneca performs three cross-validations for each 2-year test range.
+super bowl games).  We use the first 6 years as the training set 
+and the last 2 years as the testing set.  We use a cross-validation 
+horizon (sliding window) of 1-year, and a period (sliding pace) 
+of 180 days.  As such, Seneca performs three cross-validations for 2-year test range.
 
-Prophet expects multiple hyperparameters: \textit{growth} specifies linear or logistic trend model growth; \textit{prior scale} indicates the strength of the 
-sparse prior probability~\cite{ref:sparse_prior}. 
+Prophet expects multiple hyperparameters.
+\textit{growth} specifies linear or logistic trend model growth and \textit{prior scale} indicates the strength of the sparse prior probability.
 There are three prior scale hyperparameters for change point, holidays, and seasonality.
-Since Prophet uses a Fourier sum to estimate seasonality, 
-the \textit{fourier order} is the number of terms in the partial Fourier 
-sum. \textit{Seasonality mode} indicates that the effect of seasonality is either 
-multiplicative or additive. Finally, the width of uncertainty intervals 
-is set using \textit{interval width}.
+Since Prophet uses a Fourier sum to estimate seasonality, the \textit{fourier order} is the number of terms in the partial Fourier sum.
+\textit{Seasonality mode} indicates that the effect of seasonality is either multiplicative or additive.
+Finally, the width of uncertainty intervals is set using \textit{interval width}.
 
-In the results that follow, we evaluate \textit{default} parameterizations (that come with 
-the application or that are defined by the application developer) for each application.  
-The default parameters and tuning options for Prophet are listed in the Table~\ref{tab:prophet_para}.
-For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points.
-Then the application returns the average MSE across cross validations.
-%Based on the model trained by default parameter setting, this average MSE metric is 0.284.
+Each application has default hyperparameter settings (i.e.
+default values or those recommended by the application maintainer).
+The hyperparameters, their default and optional values that we consider for Prophet are listed in the Table \ref{tab:prophet_para}.
 
-Multi-Regression is a regression application developed as part of
+Multi-Regression is a regression application developed by others as part of
 an Internet-of-Things (IoT) project~\cite{iot-cpu} (which has been
@@
 to multiple linear regression by the authors of this prior work).
-The application predicts outdoor temperature from the processor 
+The application uses multiple linear regression models
+to predict outdoor temperature from the processor 
 temperature of single board computers (SBCs).  
-The technique uses multiple linear regression models computed from time
-series of processor temperature measurements,
-to predict outdoor microclimate temperatures. 
 The training dataset consists of eight input time 
 series (one per SBC, each containing 
-5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.
+5-minute measurements) from Apr. 5th to Dec. 10th, 2018.
 
-A hyperparameter configuration for this application is 
-a subset of input SBC time series.
+Hyperparameter configuration for Multi-Regression is a subset of input SBC time series.
 Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
-For this application,
-we assume the default parameterization is the 
+For this application, the default parameterization is the 
 full set of input time series (8 in this case).
-The test dataset for this application is a time 
+The test dataset is a time 
 series of the outdoor temperature (ground truth) 
-over the same period.  The application makes 
+over the same period.  
+The application makes 
 predictions for each of these outdoor temperatures
 using the regression coefficients constructed from the training set
-and computes and returns the MSE between predicted 
-and ground truth value pairs.
+for each new value in the test set.
+%and computes and returns the MSE between predicted 
+%and ground truth value pairs.
 
+XGBoost~\cite{ref:xgboost-web}, SVC~\cite{ref:svc}, and NN~\cite{ref:neural_network} 
+are the classification applications that we consider.
 XGBoost~\cite{ref:xgboost-web} is an open source 
@@
 performs both regression and classification. 
-The hyperparameters and the default values that Seneca uses 
-in this study are listed in Table~\ref{tab:xgboost_para}. 
-A definition for each hyperparameter can be found in~\cite{ref:xgboostparams}.
-%xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
+The hyperparameters and their default values 
+are listed in Table~\ref{tab:xgboost_para}, their definitions can be
+found in~\cite{ref:xgboostparams}. SVC uses support vector machines to implement classification as part of the libsvm~\cite{ref:libsvm} library.
+The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para} with definitions
+in~\cite{ref:svcparams}. NN is a machine 
+learning application leveraging neural network to identify patterns from an input dataset. 
+Here we implement a feed-forward multi-layer perceptron model~\cite{ref:feedforward_nn} 
+for classification. The hyperparameters and their defaults for NN are listed in Table~\ref{tab:nn_para} with definitions
+in~\cite{ref:nnparams}. 
+%\footnote{\url{https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html}}.
+%\footnote{\url{https://xgboost.readthedocs.io/en/latest/python/python_api.html\#module-xgboost.sklearn}}
+%\footnote{\url{https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html}}
 
-Support vector classification (SVC)~\cite{ref:svc} 
-is an implementation of a classification algorithm 
-that is based on support vector machines that is part of the
-libsvm~\cite{ref:libsvm} library.
-The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found in
-%svcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
-\footnote{\url{https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html}}.
-
-Neural network (NN)~\cite{ref:neural_network} is a machine 
-learning framework that learns 
-and makes decisions from patterns in an input dataset. For this application, 
-we use a feed-forward multi-layer perceptron model~\cite{ref:feedforward_nn} 
-for the classification task.
-The hyperparameters and their defaults for NN 
-are listed in Table~\ref{tab:nn_para}. 
-A definition for each hyperparameter can be found in~\cite{ref:nnparams}.
-%nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html
-
-For the classification applications (XGBoost, SVC, and NN), we use a labeled
-dataset for training, testing, and evaluation from an IoT 
-project~\cite{blind}. The dataset contains measurements from individual
+For these classification applications, we use a labeled
+dataset for training, testing, and evaluation from another IoT 
+project~\cite{blind}. The dataset contains measurements of individual
 citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a fruit sorting
-and grading device (using a large number of sensors).  The measurements (i.e.
-features) include size, shape, weight, color, diameter, flatness, among other
-characteristics, for each fruit.  
+and grading device using a large number of sensors. The measurements (i.e. features) include size, shape, weight, color, diameter, flatness, among other characteristics, for each fruit.  
 The dataset has been filtered to remove correlated
 features (those with an absolute value of the Pearson correlation coefficient
-greater than 0.8). The dataset has also been balanced by 
+greater than 0.8). The dataset has been balanced by 
 down-sampling and the resulting 
@@
 distributed evenly across 5 targets. Each row has
-18 features.  The label identifies the field from which the 
-individual fruit was harvested.
+18 features.  The label identifies the field from which the individual fruit was harvested.
 
-The applications train a model on a subset (80\%) of the
-data.  Each then uses this model to predict the field
-from which each fruit originates (for the remaining 20\%). 
-The applications compute a classification accuracy score
-as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
-prediction class, $Y_i$ is the true class, 
-$n$ is the number of samples, and 1(x)
-is the indicator function. The applications return the accuracy percentage
-upon completion. As mentioned above, in addition to returning
-classification accuracy for its classification task, XGBoost also returns 
-MSE for its regression task.
-
-%The dataset is from a Compac packline machine~\cite{ref:compac} that sorts and grades fruit using a large number of 
-%measurements (i.e. feature measurements including size, shape, weight, color, diameter, flatness, etc.).  The labels identify the field from which fruit was harvested.
-%The dataset is filtered to remove correlated features (those with an absolute value of the Pearson correlation 
-%coefficient greater than 0.8).
-
-%Seneca downloads the dataset from AWS S3 for each function invocation.
-%It then randomly indexes the dataset and splits it into two.
-
-% For these applications (XGBoost, SVC, and NN), we consider three
-% split scenarios for training and testing: 80\%-20\%, 20\%-80\% and
-% 0.1\%-99.9\%. As the proportion of training data decreases, the performance of
-% classifier degrades accordingly. However we note that using the optimized
-% hyperparameters generated by Seneca, these classifiers are able to achieve
-% accuracy levels similar to those generated from the default parameters, but
-% with significantly less training data.
-
-% and we argue that Seneca is able to eke out
-%improvement even with very limited training data.
-
-%\textcolor{blue}{list them here once we finish the additional results} 
-%This setup also means that each Seneca function
-%considers a different training and testing set during hyperparameter tuning.
-
-%todo in the future -- for a complete tuning, use the same testing and training sets
-%run this multiple times (for the same test/train datasets) and report the average and stdev in the latency (and memory?) results.
-%todo in the future -- repeat the above using different test/train datasets, but keep 
-%them the same for all functions in a single tuning run.  Compare the MSE/accuracy and
-%the configurations that are selected, analyze how they change (if they do)
-
+The applications train a model on a random subset (80\%) of the data.
+Each then uses this model to predict the field from which each fruit originates for the remaining 20\%.
+To study the impact of random data split, we consider multiple 80\%/20\% splits in our evaluation.
 \subsection{Empirical Methodology}
 
-To evaluate Seneca, we measure tuning performance, application execution time, 
-memory use, and monetary cost.  For tuning performance, 
-we use mean squared error (MSE)
-for regression tasks and percentage accuracy for classification 
-tasks (i.e. we score model prediction accuracy and not explanatory power).  
-Seneca is able to compare models for each type of application using 
-these scores because it uses the same
-total number of hyperparameters for each model.  Thus, the
-the penalty function in terms of 
-Bayesian Information Criteria is the same.
+To evaluate Seneca, we measure model output quality, execution time, memory use, and monetary cost.
+For output quality (prediction accuracy) our metrics are mean squared error (MSE) for regression and percentage accuracy for classification as described above.
+We score model prediction accuracy and not explanatory power ($R^2$) to avoid overfitting.
 
-The default configuration that we consider for each application is described
-above.  We report results for the default, best (Seneca's recommendation), and
-worst performing hyperparameter configurations for each application type.  
-Seneca computes all possible combinations of
-the hyperparameter settings specified in the configuration to extract each of
-these results.  The default results represents those that a novice or first
-time user might employ when using these applications as a ``black box.''  The
-worst performing scenario shows how bad the results can be when parameters are
-poorly tuned.  Finally, the best is the upper bound on what is possible from
-tuning the hyperparameters for the values and dataset specified 
-(e.g. using expert knowledge or Seneca).
+\ignore{Seneca is able to compare models for each type of application using these scores because it uses the same total number of hyperparameters for each model.
+Thus, the penalty function in terms of Bayesian Information Criteria is the same.
+comments: BIC is based on parameters, not for hyperparameters.}
 
-To evaluate the  savings introduced by Seneca, we deploy the applications
-on Amazon Web Services (AWS) Lambda and extract
-execution time and memory use from AWS CloudWatch~\cite{ref:awscloudwatch} logs.  
-Seneca extracts execution time and memory use from AWS CloudWatch logs\footnote{\url{https://aws.amazon.com/cloudwatch/}}.
-We compute monetary cost
-using the AWS Lambda pricing model\footnote{\url{https://aws.amazon.com/lambda/pricing/}}.
-%awslambdapricing: https://aws.amazon.com/lambda/pricing/
-Each function downloads the training and testing dataset 
+We compare results for the default, best (Seneca's recommendation), and worst performing hyperparameter configurations for each application type.
+Seneca computes all possible combinations of the hyperparameter settings specified in the configuration to extract each of these results.
+\texttt{default} represents results that a novice or first time user might experience when using these applications as a ``black box.''  The \texttt{worst} shows how bad the results can be when parameters are poorly tuned.
+Finally, the \texttt{best} is the upper bound on what is possible from tuning the hyperparameters for the values and datasets specified  (e.g.
+using expert knowledge or Seneca).
+
+Seneca deploys the applications automatically over AWS Lambda
+and extracts execution time and memory use from 
+AWS CloudWatch~\cite{ref:awscloudwatch} logs.
+We compute monetary cost using the AWS Lambda pricing model~\cite{ref:pricing}.
+Each function downloads the training/testing dataset 
 of the application from AWS S3 upon function invocation. 
@@
 in our cost computations (it is very small).
-
-%We also experiment with different memory configurations for Seneca functions
-%in AWS Lambda.  
-We also investigate Seneca's automatic memory optimization capabilities.  To
-do so we compare the execution performance and cost of the benchmarks using
+%\footnote{\url{https://aws.amazon.com/cloudwatch/}}
+%\footnote{\url{https://aws.amazon.com/lambda/pricing/}}
+We also evaluate Seneca's automatic memory optimization capabilities.  To
+do so we compare the execution performance and cost of the applications using
 the maximum allocatable memory size to the performance and cost when run with
-Seneca's automatically determined memory size. Though memory size used reported by AWS CloudWatch fluctuates throughout the tuning process, we 
+Seneca's automatically determined memory size. Even though \texttt{maximum memory used} reported by AWS CloudWatch can fluctuate, we 
 have verified that the optimized allocated memory is sufficient for all 
-hyperparameter configurations to complete successfully.
-
-% Note that this comparison assumes that the memory size used by each benchmark does not depend on hyperparameter settings.
-We have verified that this assumption holds for the benchmarks and datasets we consider and plan to consider applications for which hyperparameter settings require different maximum amounts of memory as part of future work.
+hyperparameter configurations to complete successfully.  We have also verified
+that the memory requirements across hyperparemeter settings do not vary 
+significantly. We plan to consider applications for which hyperparameter settings require
+different maximum memory sizes as part of future work.
 
 \subsection{Application Efficacy}
-
-We begin by evaluating Seneca's effect on application efficacy.
-That is, we detail the effect on the quality of the output generated by each
-application when Seneca determines the hyperparameter settings.
 
@@
 \input{tables/mse-tab}
-\caption{Combination count and MSE for the default, best (Seneca's recommendation), and worst hyperparameter configurations for the three regression applications. 
+\caption{Hyperparameter configuration count and MSE for the default, 
+best (Seneca's recommendation), and worst configurations for the three regression applications. 
 For the MSE  values (rows 3-5), lower is better.
 \label{tab:mse}}
-%\vspace{-0.2in}
+\vspace{-0.2in}
 \end{table}
@@
 \begin{figure}[t] \centering 
-\vspace{-0.2in}
-\includegraphics[scale=0.36]{box_plot_mse_2}
-\vspace{-0.4in}
-\caption{The box plot of MSE metric from three regression applications in the entire hyperparameter tuning search space.
-The red notch shows the MSE from the default settings.
+\vspace{-0.5in}
+\includegraphics[scale=0.36]{box_plot_mse}
+\caption{Box plot of MSE from the three regression applications across the 
+hyperparameter tuning search space. The red notch shows the MSE from the default settings. 
 The colored diamonds are outliers beyond two interquartile ranges. 
+Seneca selects the points indicated by blue triangle.
 Lower MSE values are better. 
@@
 
-%using the three regression applications: 
-%Prophet, Multi-Regression, and XGBoost (regression task). 
-Table~\ref{tab:mse} shows the effect of Seneca on the quality of the
-regressions generated by Prophet, Multi-regression, and XGBoost (when used as
-a regression algorithm). The first row indicates the number of
-different hyperparameter settings Seneca considered.  Rows 3 through 5 show
-the MSE generated by the default hyperparameter settings, the best (lowest
-MSE) Seneca was able to find, and the worst (largest MSE) that Seneca tested
-for each regression algorithm and dataset.
+We first evaluate the quality of the output generated by each
+ML applications when Seneca determines the hyperparameter settings. We
+first show the results for the regression applications in
+Table~\ref{tab:mse}.
+The first row of data is the number of hyperparameter 
+configurations that Seneca considers for each.
+The last three rows show the MSE for the default, worst, and best performing (Seneca's recommendation)
+hyperparameter configuation (lower is better).
+Seneca reduces MSE by 22.56\%, 15.94\%, and 44.88\%, for Prophet, Multi-Regression, and XGBoost,
+respectively, for the datasets and training methodologies that we consider.
+Verses the worst case, Seneca reduces MSE by 82.62\%, 78.01\%, and 99.28\%, respectively.
 
-%s mentioned previously, the table shows regression
-%quality in terms of MSE. 
-%
-%size of the hyperparameter search space (number of configurations
-%considered) and the mean squared error (MSE)
-%for each of the regression applications that we consider (columns 3-5).
-%The first row of data is 
-% the number of hyperparameter configurations in the search space of each. 
-%The last three rows show the MSE for the default, worst, and best performing 
-%hyperparameter configuation reported by Seneca (lower is better).
+Figure~\ref{fig:box_plot_mse} shows the MSE box plot for the hyperparameter search space for these applications (lower is better). 
+The central rectangle covers the interquartile range (IQR),
+which is defined as the range of data
+points from first quartile to third quartile \texttt{$(Q3 - Q1)$}.
+The upper whisker extends to the last datum less
+than \texttt{$(Q3 + 2 * IQR)$} and the lower whisker extends to the first datum greater
+than \texttt{$(Q1 - 2 * IQR)$}. The data points beyond the whiskers are considered outliers
+and are plotted as colored diamonds. The red notch identifies the MSE that results from training
+the model using the default settings of hyperparameter.
+The blue triangle identifies the MSE of Seneca.
+The difference between red notch and blue triangle
+is the improvement brought about by the use of Seneca, over 
+using the default parameter setting.
+The plot also shows
+that Prophet and Multi-Regression have a significant number of outliers,
+indicating that a comprehensive search is critical to finding the best configurations.
 
-%Note that Seneca's recommendation is the best performing configuration.
-Compared to the default hyperparameter settings,
-Seneca reduces MSE by 22.56\%, 15.94\%, and 62.69\%, for Prophet, Multi-Regression, and XGBoost, respectively, for the datasets and training methodologies that we consider.
-Verses the worst case, Seneca reduces MSE by 82.62\%, 78.01\%, and 99.51\%, respectively.
-
-Figure~\ref{fig:box_plot_mse} provides a box plot of MSE (lower is better) for
-these applications for the entire hyperparameter search space. The central
-rectangle covers the interquartile range (IQR), which is defined as the range
-of data points from first quartile to third quartile (Q3 - Q1).  The upper
-whisker extends to the last datum less than \texttt{$(Q3 + 2 * IQR)$} and the
-lower whisker extends to the first datum greater than \texttt{$(Q1 - 2 *
-IQR)$}. The data points beyond the whiskers are considered outliers and are
-plotted as colored diamonds.
-
-The red notch identifies the MSE that results
-from training the model using the default settings of hyperparameter. The
-difference between red notch of lowest data point is improvement brought about
-through the use of Seneca. From the location of red notch, we can see the MSE
-metrics from default configuration in three applications are similar to those
-in the first quartile for all applications.
-This data shows that the quality of the
-output generated by each application (for a given dataset) is dramatically
-affected by hyperparameter settings.  Predictably, the default settings are
-near the ``good'' end of the spectrum, but as both Table~\ref{tab:mse} and
-Figure~\ref{fig:box_plot_mse} indicate, Seneca is able to find
-parameterization that improves output quality over the default settings
-in each case.
-%Thus for Prophet
-%and Multi-Regression, Seneca 
-%, meaning the potential room for improvement is about 75\%
-%over the range of MSE metric. The box plot also illustrates that the best MSE
-%of Prophet and multivariate regression are among outliers, where a
-%comprehensive search is very critical to find the best configurations. 
-%\textcolor{blue}{Add more analysis here to discuss the variance in the MSE
-%for the range of configurations and how they change across applications.
-%Include any insights that the boxplots add.}
-
-%%%%%%%%%%%%%%%%%%%%% classification apps - tuning performance
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-We next empirically evaluate the tuning performance of Seneca for the three
-classification applications: XGBoost (classification), SVC, and NN.
-Table~\ref{tab:accuracy} presents the accuracy percentage (higher is
-better) reported by each application (3 rightmost columns) for the default,
-worst, and best hyperparameter tuning configurations reported by Seneca.
-using an 80/20 (train/test) percent split,
-Seneca increases accuracy by 2.46\%, 19.04\%, and 3.79\%, for XGBoost
-(classification), SVC, and NN applications, respectively.  Compared to
-the worst case, Seneca improves accuracy by 98.11\%, 26.74\%, and 63.92\%,
-respectively.
-
+%%%%%%%%%%%%%%%%%%%%% classification apps - ML model output quality %%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}
@@
 \input{tables/accu-tab}
-\caption{The Accuracy reported for the 
+\caption{Accuracy for the 
 default, best (Seneca's recommendation), and worst hyperparameter configurations for 
 the three classification applications using 80\% of the data to train and 20\%
-of the data as a test set. 
-%under three train/test split scenarios.  
-For the accuracy values in the table, higher is better.
+of the data as a test set. Higher accuracy is better.
 \label{tab:accuracy}}
-\vspace{-0.2in}
-%\end{figure}
+\vspace{-0.1in}
 \end{table}
 
-%not sure what this paragraph is adding, seems to a repetition of what
-%is already said above...
-%The 80-20 case represents the typical usage of these classification
-%applications. Often, when evaluating the accuracy of a specific classifier,
-%the user uses the 80-20 split ``rule'' when measuring accuracy. In this case,
-%Seneca's improvement over the default parameterizations varies from 2.46\% for XGBoost application (column 2), to 19.04\% for SVC
-%(column 3).
-
 \begin{figure}[t] \centering 
+\vspace{-0.1in}
 \includegraphics[scale=0.36]{box_plot_Accuracy_20}
 \vspace{-0.4in}
-\caption{The box plot of accuracy metric from three classification applications for the entire hyperparameter tuning search space.
-The red notch indicates the accuracy metric from the trained model using default settings.
-The colorful diamonds are outliers beyond two interquartile ranges.
-Higher accuracy values are better.
+\caption{Box plot of accuracy reported for three classification applications across 
+the hyperparameter search space. The red notch indicates the accuracy that results
+from default hyperparameter values.
+The diamonds are outliers beyond two interquartile ranges. 
+Seneca selects the points indicated by blue triangle. 
+Higher accuracy is better. 
 \label{fig:box_plot_accuracy}}
-\vspace{-0.1in}
+\vspace{-0.2in}
 \end{figure}
-
-Figure~\ref{fig:box_plot_accuracy} presents the accuracy (higher is better) 
-for the entire hyperparameter search space as a box plot for each classification
-application.  The placement of the rectangle and whiskers is the same
-as in Figure~\ref{fig:box_plot_mse}. 
-%The central rectangle covers from first quartile to third quartile (Q3 - Q1) and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}. 
-The red notch indicates the accuracy metric from the model trained by default settings and colored diamonds are outliers beyond whiskers.
-Again, Seneca significantly
-improves tuning performance over the default and worst case configurations for SVC while generating a smaller improvement for XGBoost and Neural Network versus the default.
-This is because XGBoost and NN use a well tuned default parameter
-set that works well for most datasets.  SVC benefits more from Seneca tuning
-that the others.
 
@@
 \input{tables/exec-time-memory-tab}
-\caption{The mean and standard deviation (in parentheses) values of execution time and memory use, and best accuracy across 30 executions of three classification benchmarks running against two random states.
-It verifies data split does not have major impact to execution metrics and scores.
+\caption{The mean and standard deviation (in parentheses) for execution time and memory use 
+(across 30 runs),
+and best accuracy score for the classification applications using two different random splits. 
 \label{tab:exec_memory}}
-%\vspace{-0.2in}
+\vspace{-0.1in}
 \end{table}
 
-To investigate the potential impact of the 80-20 data split for the classification
+We next empirically evaluate Seneca's model output quality for the three
+classification applications: XGBoost (classification), SVC, and NN.
+Table~\ref{tab:accuracy} presents the accuracy percentage (higher is better)
+for each application (3 right-most columns)
+for the default, worst, and best (Seneca's recommendation) hyperparameter tuning
+configurations (data rows 2-4).
+The first row 
+reports the number of configurations that Seneca considers in its search space.
+Using a random 80/20 (train/test) percent split,
+Seneca increases accuracy by 2.46\%, 19.04\%, and 3.79\%, for XGBoost
+(classification), SVC, and NN applications, respectively.  
+Because XGBoost and NN use a well-tuned default parameter set that works well for most datasets, Seneca provides only modest improvements.
+Compared to the worst case however, Seneca improves accuracy by 98.11\%, 26.74\%, and 64.17\%,
+respectively.
+
+Figure~\ref{fig:box_plot_accuracy} presents the accuracy box plot across the hyperparameter search space for these applications (higher is better).  
+The central rectangle covers the first-third quartile
+\texttt{$(Q3 - Q1)$} and the whiskers span from \texttt{$(Q3 + 2 * IQR)$} to \texttt{$(Q1 - 2 * IQR)$}.
+The red notch indicates the accuracy metric from the model trained using the default
+settings and colored diamonds show outliers beyond the whiskers.
+The blue triangle at the top identifies the accuracy percentage reported by Seneca.
+
+The model output quality results across applications, show that prediction
+accuracy (for a given dataset) is dramatically
+affected by hyperparameter settings.  Predictably, the default settings are
+near the ``good'' end of the spectrum, however, Seneca is able to find the
+parameterization that improves output quality over the default settings
+in each case.
+
+To investigate the potential impact of Seneca's 80/20 percent data split for the classification
 applications, we next evaluate the quality of the output generated from 
-each when we consider different 80-20 random splits.
+each when we consider different 80/20 random splits.
 To enable this, we run Seneca 30 times to obtain execution time, memory use, 
-and best accuracy score. 
-Table~\ref{tab:exec_memory} shows the mean and standard deviation of these 
-metrics across runs for two different random splits.  The Seneca score
-is similar across splits.  As a result, users can employ the models
-(for the selected hyperparameter settings) that Seneca recommends
-repeatedly for inference to amortize the cost of using Seneca.
-
-% \begin{table}
-% \centering
-% \input{tables/speedup-tab}
-% \caption{The execution time of tuning in seconds by using Seneca and EC2 instance (Serial) and respective speedup. 
-% \label{tab:accuracy}}
-% \vspace{-0.2in}
-% \end{table}
-
-Finally, we compare Seneca to AWS EC2 use.
-We measure the execution time of Seneca and hyperparameter tuning 
-using the least expensive EC2 instance type in which the application
-will run (t2.micro for SVC and NN, t1.medium for the rest).  End to end, Seneca's
-concurrency facilitates in a 4x -- 17x (9x on average) speedup
-and \$0.01--\$0.34 (\$0.13) additional cost over serialized execution in EC2.
-EC2 trades off monetary cost for programmer productivity, i.e. the developer 
-must setup, deploy, and manage the applications manually. Moreover, the EC2
-pricing model is imposed on hour boundaries. Moreover, Seneca and 
-AWS Lambda impose no cost when no execution is occuring (EC2 instances must
-stay idle in between runs). As part of future work, we will compare Seneca
-to the AWS Elastic Container Service.
-%\textcolor{blue}{FIX THIS: State the results (speed up) per application and 
-%also state the cost analysis for 1 hour of computation.  Clarify that this
-%is due to the 1-hour pricing model of EC2.}
-
-%We use instance type t2.medium
-%for Prophet (since it cannot be built
-%process on EC2 instance across five applications. Since library compilation issue, we use t2.medium on Prophet and t2.micro on other 4 applications. 
-%As a result, Seneca achieves at least 4x speedup for IO-bound application (SVC) and 21x speedup for CPU-bound application (XGBoost).
-It confirms Seneca can execute tuning within a more reasonable period of time, comparing to executing serially on EC2 instance.
+and best accuracy score. We report the
+mean and standard deviation (in parentheses) 
+for execution time and memory use across runs,
+and the best accuracy score in
+Table~\ref{tab:exec_memory}. Each pair of rows shows the results for two different random splits.
+Our earlier results use input 1; this table adds results for a second, 80/20 
+random split of the input (we also considered other random splits, which we omit for brevity, 
+and the results are similar).  The performance and Seneca score is similar across splits. 
+This result indicates that for these applications, 
+users can repeatedly employ the recommended models for inference on other datasets or splits,
+to amortize the cost of using Seneca.
 
@@
 Table~\ref{tab:cost_optimized} shows the results with and without
-the Seneca memory optimization. 
-The five columns identify the benchmark applications.
-Because the performance profile of XGBoost is the same for regression
-or classification, we include its metrics once.
+the Seneca memory optimization for each of the five applications.
 The first two rows show the results when we use the maximum allocated memory 
 for the Lambda functions. We present execution time in minutes (row 1) and 
-monetary cost (row 2).
-
-Rows 3--6 show the performance and cost impact of using Seneca's memory optimization.
-is the execution time in minutes 
+monetary cost in cents (row 2). 
+Rows 3--6 show the performance and cost when using Seneca's memory optimization.
 \texttt{Exec time opt} is the execution time in minutes.
-\texttt{Optimizer Cost} is monetary cost of Seneca's memory size detector.
-\texttt{Cost opt} is monetary cost of using Seneca and the memory size
-it identifies and recommends.
-\texttt{Total cost} is the sum of \texttt{Optimizer Cost} and \texttt{Cost opt}, i.e., the total cost of using Seneca to perform hyperparameter tuning for these applications and data sets.
-The last two rows show the monetary savings (row 7) and percent savings (row 8) u
+\texttt{Optimizer Cost} is monetary cost in cents of Seneca's memory size detector.
+\texttt{Cost opt} is monetary cost in cents of using Seneca's memory optimizer.
+\texttt{Total cost} is the overall cost of using Seneca to perform hyperparameter 
+tuning for these applications and datasets (sum of Optimizer Cost and Cost opt).
+The last two rows show the monetary savings in cents (row 7) and percent savings (row 8)
 of using Seneca's memory optimization.  Seneca's memory optimization reduces
-the monetary cost of its use from 10--30\% (20\% on average).
+the monetary cost of its use from 10--35\% (25\% on average).
 
@@
 \input{tables/seneca-mem-opt-tab.tex}
-\caption{Seneca Memory Optimization: Rows 1--2 show the execution time and  monetary cost of using Seneca without its memory optimization.
-Rows 3-6 is the execution time and cost, respectively, when Seneca detects and sets allocated memory for the application functions automatically.
-Rows 7-8 show the savings by dollar and percentage.
+\caption{Seneca Memory Optimization: Rows 1--2 show the execution time and  monetary cost 
+of using Seneca without its memory optimization (allocated memory = 3G). 
+Rows 3-6 is the execution time and cost, 
+respectively, when using the Seneca memory optimizer. 
+Rows 7-8 show the savings in cents and percentage, respectively.
 \label{tab:cost_optimized}}
-\vspace{-0.2in}
+%\vspace{-0.1in}
 \end{table}
@@
 Table~\ref{tab:cost_optimized} illustrates two important points.
-First, using AWS Lambda, full hyperparameter space exploration is not expensive in 
+First, using AWS Lambda, full hyperparameter space exploration is inexpensive in
 \textit{absolute} dollar cost terms and Seneca's automatic memory size optimization
-decreases this cost further.  Second, this optimization reduces cost but can 
+decreases this cost further.  Second, memory optimization reduces cost but can 
 increase the total execution time for parameter search 
@@
 execution environment (number of CPUs, Linux container overhead, 
-multitenency, etc.).  We omit the data due to space constraints.
-However, the average absolute difference in cost
-across the five applications (30 runs) is \$0.050. %I use only split 1 for all 5
+multitenency, etc.).  We omit this data due to space constraints but analyze it here.
+The average absolute difference in cost
+across the five applications (30 runs) is \$0.05. %I use only split 1 for all 5
 %numbers are below
-Moreover, the highest cost of execution under 
-optimized memory is still cheaper than the lowest cost of execution 
-under maximum memory for all five benchmarks.  
+Moreover, we have verified that the highest cost of execution under 
+optimized memory is still cheaper than the lowest cost of execution under maximum 
+memory for all five applications.
 %$	Ave Cost	Highest Cost	Lowest Cost	Diff (High - low)
@@
 
-Overall, given the AWS Lambda cost model and its performance variability, 
+\begin{table}
+\centering
+\input{tables/yield-tab-corrected.tex}
+\caption{Seneca VS EC2 cost analysis. Execution time (mins) and cost (cents) for
+executing the applications serially in EC2 (t2.medium).  
+Rows 3--4 show yield -- the additional speedup that
+Seneca can achieve for each additional dollar spent for these applications.
+Yield for SVC is 0 (infinite) because Seneca costs less than EC2 in this case.
+Ideal yield shows the yield when we execute the applications in parallel (assuming
+2x perfect parallelism).
+\label{tab:yield}}
+\vspace{-0.1in}
+\end{table}
+
+Finally, we compare the cost of Seneca to AWS Elastic Compute Cloud (EC2) use. 
+We measure the execution time of Seneca using the
+least expensive EC2 instance type in which the applications will run
+(t2.medium, which has 2 multi-tenant cores and 4GB of memory). 
+Note that EC2 instances are charged for by the hour; Lambda charges 
+are only imposed when functions execute. We execute the applications serially
+using the instance.  For this setting, Seneca enables a speedup over EC2 
+of 3.72x -- 12.38x (6.51x on average). Doing so, however, imposes an additional 
+cost of \$0.01--\$0.15 over EC2 for all but SVC. 
+Seneca costs \$0.03 less than EC2 for SVC (because SVC runs in significantly less than
+the next hour boundary).
+
+To further understand the relationship between Seneca speedup and cost when Seneca
+is more expensive (but faster) than using EC2, we define \texttt{yield} as 
+$Y=\frac{T_{ec}}{T_{sc}}/({C_{sc} - C_{ec}}) \,|\ if \,C_{sc} > C_{ec}$ where $T_{ec}$ and $T_{sc}$ are the execution time, $C_{ec}$ and $C_{sc}$ are the total cost of EC2 instance 
+and Seneca, respectively.
+For applications for which Seneca is cheaper (e.g. SVC), we report \texttt{yield} 
+as $0.00$.  This metric reveals the amount of speed up that Senence can achieve 
+for each additional dollar spent.  To understand the yield if we were to 
+parallelize the EC2 deployment (perhaps a more ``fair'' comparison), 
+we also estimate yield for perfect parallelism (2x in our case for 
+the t2.medium).
+
+We present results for this yield metric in Table~\ref{tab:yield} for each of the applications.
+Rows 1 and 2 show the average execution time (in minutes) and cost (in cents) 
+from using EC2 for each.
+Rows 3 and 4 show the Seneca yield (speedup/\$).
+Row 3 shows yield for serialized execution in EC2 (t2.medium
+instance) and row 4 shows estimated yield if we were to achieve perfect parallelism
+(i.e. 2x) using the EC2 instance. On average across the four applications for which
+EC2 is cheaper, Seneca achieves yield of 294 (assuming perfect parallelism in EC2). 
+That is, Seneca is able to provide a speedup
+of 294x on average, for each additional dollar spent for these applications.
+We plan to compare Seneca cost and performance 
+to other EC2 instances and the AWS Elastic Container Service
+as part of future work.
+
+Overall, given the AWS Lambda pricing model and its Lambda performance variability, 
 Seneca is still able to find the sweet spot between cost 
-and execution time. Thus Seneca can be used to trade off time-to-solution for
-cost as desired by users.
-
-%Even using the maximum memory available
-%for almost 25 minutes of execution 
-%time (cf Prophet in Table~\ref{tab:cost_optimized}), the
-%total dollar cost is approximately 73 cents.  Secondly, Seneca's memory
-%optimizations produce a significant savings to further reduce its cost.
-%
-%Note that Seneca's memory/cost optimization
-%can introduce an execution time penalty (relative to the maximum memory
-%execution) for some of the applications.  
-%That is, the
-%execution times for all applications increase when Seneca chooses
-%a memory size.  Thus while Seneca is finding the best application output
-%quality and optimizing the cost of producing that output, it is doing so at
-%the expense of execution performance (time to solution). Such a penalty
-%is expected due to the proportional CPU power to allocated
-%memory. However, the Seneca optimizer is able to find the optimal
-%memory configuration to minimize that  penalty.
-In the case of SVC, Seneca saves 30\% compared to max memory execution (\$0.016 vs \$0.023) but has almost the same execution time (1.91 vs 1.95 minutes).
-% The source of this execution performance penalty is not clear.  We hypothesize
-% that when requesting a large memory for AWS Lambda, Amazon chooses a machine
-% that also has fast processors so the Lambda functions execute more quickly.
-% If this supposition is true, then the AWS Lambda pricing model correctly
-% weights the cost of additional memory (in light of the reduced execution time)
-% because the large-memory executions are still more expensive.
-%However regardless of the cause, 
-%Even in the worst case of CPU-bound application, the Seneca memory optimizer still provides a way to trade off time to solution for cost when the highest possible application output quality is desired.
-
-%To corroborate the cost-effectiveness of Seneca, we analyzed the total cost of five benchmarks in 30 executions from last section.
-We observe the reported \textit{billed duration} and \textit{max memory used} oscillate that leads to different total cost across 30 executions and we assume it is because the pagination and memory sampling method used by different AWS Lambda host servers.
-However, even taking fluctuation into account, the
-%highest cost of execution under optimized memory is still cheaper than the lowest cost of execution under maximum memory in all five benchmarks.
-We believe Seneca's optimizer is economical despite the locality of lambda container and application.
-
-% \textcolor{blue}{AWS announces the proportional CPU power to memory which is the source of penalty}
-% \textcolor{blue}{See my notes to fix the tables in the caption of these figures.}
-
-% \textcolor{blue}{It would be good here in the Seneca case to also run the applications in the minimum amount of memory discovered by Seneca (i.e., if we were to run Seneca ahead of time, taking the max memory used by any of the functions per application) -- to show what Seneca is missing.
-this assumes you are doing the memory optimization WHILE you are doing the tuning -- if you are not, you can leave this out, but we need to remind the reader at this point how the memory optimization is done by Seneca (we should do this in this paragraph, either way).}
-
-% \textcolor{blue}{Comments: The minimum amount of memory is the "max memory used" value.
-I tried that out and the execution time increases dramatically at the minimum memory case.
-I will explore the idea of simultaneous optimization and tuning later}
-
-%\begin{figure}[t] \centering 
-%\includegraphics[scale=0.36]{Cost_analysis_2}
-%\caption{The cost analysis of Seneca automatics memory optimization. 
-%By reducing the memory use of each, Seneca reduces the monetary cost of hyperparameter tuning by 
-%an average of 20\% over using the maximum memory allocatable.\label{fig:cost_analysis}}
-%\vspace{-0.2in}
-%\end{figure}
-
-%\begin{figure}[t] \centering 
-%\includegraphics[scale=0.36]{Latency_analysis_2}
-%\caption{Latency of Seneca with (Opt) and without (No Opt) memory optimization, for each application.
-As Seneca reduces memory use (and cost), it also extends the execution time of the functions (and thus total tuning time, i.e., the latency of Seneca) by Y\% on average across applications \textcolor{blue}{compute and fill in Y here.}
-%\textcolor{blue}{Change the legend as follows: change "Optimized Memory" to "Opt"; change "Maximum Memory" to "No Opt"; Make sure that Opt stays green and change No Opt to be red (same as above graph)}
-%\label{fig:latency_analysis}}
-%\vspace{-0.2in}
-%\end{figure}
-
-%Figure~\ref{fig:cost_analysis} presents the breakdown in the monetary cost of
-%using Seneca (performing hyperparameter tuning) with and without its automatic
-%memory optimization.  We plot bar graphs for each application across the
-%x-axis; the y-axis is monetary cost in US dollars. The stacked column is the
-%total cost of tuning by Seneca Memory Optimization, and the green and red
-%segments represent the cost of tuning and function optimization respectively.
-%The red column at the right-hand side of each application is the total cost of
-%tuning by using lambda function at maximum memory. For computation intensive
-%applications like Prophet, they generate higher costs, which depend on the
-%duration and memory usage on AWS Lambda. %The difference between two costs
-
-%\textcolor{red}{Add analysis here on what the columns are showing -- discuss
-%any anomalies (i.e., why is prophet optimization cost more than the others; why
-%mult-regression difference is greater than the others). provide a summary for
-%that states the average difference between each pair of bars across
-%applications.}
-
-%By reducing the amount of memory used, Seneca reduces its cost.  However by
-%doing so, Seneca also increases the total time it requires to perform
-%hyperparameter tuning (latency) as shown in Figure~\ref{fig:latency_analysis}
-%(due to the memory constraints place on execution).  The x-axis shows two bars
-%per application, one with memory optimization (Opt) and one without (No Opt).
-%The y-axis is Seneca's total latency, on average, to perform hyperparameter
-%tuning.  On average, the Seneca memory optimization increases latency by X\%
-%on average across applications.  \textcolor{red}{Compute and fill in X here.}
-%\textcolor{blue}{Add analysis here to discuss why the performance difference
-%is different for different applications (some more sensitive to memory
-%restrictions and why), and anything else you can pull out that is interesting
-%in these numbers.}
+and execution time. Thus Seneca can be used to trade off time-to-solution 
+for cost as desired by users, to automatically evaluate the impact of hyperparameter settings for ML models.

### 2019-03-01 Seneca.tex
Markus' pass. A bunch of minor tweaks.

@@
 
-To facilitate model search and selection using the serverless architecture, 
-we have developed Seneca, 
-a framework for tuning the hyperparameters of machine learning applications 
-in AWS Lambda. 
-The Seneca pipeline consists of packaging, deployment, 
-function optimization, and hyperparameter tuning. Figure~\ref{fig:seneca} 
-shows the architecture of Seneca.  In the the upper-right-front, we
-show the three inputs that Seneca expects from its users: (\textit{A}) a hyperparameter
-configuration file, (\textit{B}) a dataset URL, and (\textit{C}) the lambda function of machine learning application.
-The configuration file specifies the range of values for each hyperparameter that the application expects.
-Seneca applies Cartesian product to all options in this configuration to construct the search space.
-The dataset URL refers to a valid dataset stored in the AWS Simple Storage
-Service (S3)~\cite{ref:awss3}.
+To facilitate model search and selection using the serverless
+architecture, we have developed Seneca, a framework for tuning the
+hyperparameters of machine learning applications in AWS Lambda.  The
+Seneca pipeline consists of packaging, deployment, function
+optimization, and hyperparameter tuning. Figure~\ref{fig:seneca} shows
+the architecture of Seneca.  In the the upper-right-front, we show the
+three inputs that Seneca expects from its users: (\textit{A}) a
+hyperparameter configuration file, (\textit{B}) a dataset URL, and
+(\textit{C}) the lambda function of the machine learning
+application. The configuration file specifies a set of values for
+each hyperparameter that the application expects. Seneca creates the
+Cartesian product of all options in this configuration as
+the search space. The dataset URL refers to a valid dataset stored in
+the AWS Simple Storage Service (S3)~\cite{ref:awss3}.
 %\footnote{\url{https://aws.amazon.com/s3/}}.
 
-Seneca automatically builds and deploys an AWS Lambda application from the machine learning application specified.
-To do so, Seneca launches a docker container that mirrors the
-AWS Lambda execution environment, checks and installs
-the machine learning application and any libraries it requires,
-and compresses the application and uploads it to S3 (a work-around
-for the 10MB AWS Lambda function size restriction).
-Seneca constructs an AWS Lambda function from a template
-that, when executed, will download the dataset and split it into a training and testing set, and construct, test, and evaluate a model using the application
-and a set of hyperparameter values passed in by Seneca as arguments.
-Users can specify the train/test split ratio that should be used by Seneca; the
-default is 80\%/20\% for classification tasks.
-The function returns a testing score. 
-Upon completion of this process, the container deploys the function
-to AWS Lambda using the
-AWS Command Line Interface~\cite{ref:awscli}
+Based on the specified machine learning application, Seneca
+automatically builds and deploys an AWS Lambda application by
+launching a Docker container that mirrors the AWS Lambda execution
+environment, checks and installs the machine learning application and
+any libraries it requires, compresses the application and uploads it
+to S3 (a
+work-around for the 10MB AWS Lambda function size restriction).
+Seneca constructs an AWS Lambda function from a template that, when
+executed, will download the dataset and split it into a training and
+testing set, and construct, test, and evaluate a model using the
+application and a set of hyperparameter values passed in by Seneca as
+arguments.  Users can specify the train/test split ratio that should
+be used by Seneca; the default is 80\%/20\%.  The function returns a
+testing score.  Upon completion of this process, the container deploys
+the function to AWS Lambda using the AWS Command Line
+Interface~\cite{ref:awscli}
 %\footnote{\url{https://aws.amazon.com/cli/}} 
@@
 multiplied by the allocated memory of each invoked function.
-One goal of our work is to optimize memory use by these
+One goal of our work is to optimize memory use of these
 applications in order to reduce cost, and to investigate
-the trade offs of doing so.
+the trade-offs of doing so.
 
@@
 %~\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/resource-model.html}} 
-states that Lambda allocates CPU to functions proportionally to allocated memory size,
+states that Lambda allocates CPU to functions  corresponding to allocated memory size,  
 as is done for general purpose AWS EC2 instance types.
@@
 The Seneca optimizer first configures and invokes the function using a user-defined payload.  From this run, Seneca obtains the \texttt{maximum memory used}
-by function reported by AWS Cloudwatch,
-which it uses as its starting point.
+by the function as reported by AWS Cloudwatch,
+and uses it as the starting point in its search.
 Seneca then defines two double-ended queues 
@@
 When the optimizer finds that both conditions hold, it pops the left-most value from \textit{deque} and configures the function to use that value for allocated memory for all future invocations.
-If these two conditions can not be satisfied through search, the allocated memory will be configured as the memory size that results in minimal compute charge within the \textit{deque}.
+If these two conditions can not be satisfied during search, the allocated memory will be configured as the memory size that results in minimal compute charge within the \textit{deque}.
 After extensive experimentation, we find that $N=5$ and a slope threshold of 1 work best, but these values are configurable.
@@
 Based on the configuration file, Seneca creates and enqueues a list of
-payloads (function arguments) for each combination of hyperparameter values.  
-The Seneca celery workers invoke the application's Lambda function by each payload for model construction. Upon function termination, the worker records a score for the hyperparemeter configuration
-in the database.
-When the queue is drained and all workers have completed, Seneca extracts and reports the best score, configuration, and model from the database.
-Users can then use the model for inference given other datasets without retraining to amortize the time/cost of Seneca.
+payloads (function arguments) for each combination of hyperparameter
+values.  The Seneca celery workers invoke the application's Lambda
+function by each payload for model construction. Upon function
+termination, the worker records a score for the hyperparemeter
+configuration in the database.  When the queue is drained and all
+workers have completed, Seneca extracts and reports the best score,
+configuration, and model from the database. Users can then use the
+model for inference given other datasets without retraining to
+amortize the time/cost of Seneca.
 % Users can then evaluate the prediction power of the models (using Seneca if desired) 

### 2019-03-01 intro.tex
Markus' pass. A bunch of minor tweaks.

@@
 to add and remove (i.e. auto-scale) resources and services
-automatically, based on the ``elastic'' resource requirements and service needs 
+automatically, based on the dynamic resource requirements and service needs 
 of executing applications.
@@
 have started to offer programming and execution environments
-that preclude the need for server configuration,
+that obviate the need for server configuration,
 under the \textit{serverless} moniker~\cite{ref:jonas2017occupy,ref:onesteptwostep,ref:peeking}.  
@@
 automatically the
-best memory configuration for each application, further lowering its cost
+best memory configuration for each application, further lowering its
+cost
 by 10-35\%. Relative to execution in AWS EC2, Seneca enables average speedups of 294x for each additional dollar 

### 2019-03-01 related_work.tex
Markus' pass. A bunch of minor tweaks.

@@
 %(however, without replicating the Lambda runtime, introducing deployment errors).
-Seneca uses a local docker container to avoid  cost and overhead (vs these related
+Seneca uses a local Docker container to avoid  cost and overhead (vs these related
 works), which guarantees execution compatibility for AWS Lambda. 
@@
 abstraction layer to hyperopt to facilitate hyperparameter tuning for 
-Keras~\cite{ref:keras}. However, no extant work of which 
-we are aware leverages
-serverless to perform hyperparameter tuning and memory optimization in parallel 
-for ML applications.
+Keras~\cite{ref:keras}. However, we are not aware of any work that
+leverages serverless to perform hyperparameter tuning and memory
+optimization in parallel for ML applications.

### 2019-03-01 results.tex
Markus' pass. A bunch of minor tweaks.

@@
 horizon (sliding window) of 1-year, and a period (sliding pace) 
-of 180 days.  As such, Seneca performs three cross-validations for 2-year test range.
+of 180 days.  As such, Seneca performs three cross-validations for a 2-year test range.
 
-Prophet expects multiple hyperparameters.
-\textit{growth} specifies linear or logistic trend model growth and \textit{prior scale} indicates the strength of the sparse prior probability.
+Prophet expects multiple hyperparameters: \textit{growth} specifies linear or logistic trend model growth and \textit{prior scale} indicates the strength of the sparse prior probability.
 There are three prior scale hyperparameters for change point, holidays, and seasonality.
@@
 Hyperparameter configuration for Multi-Regression is a subset of input SBC time series.
-Seneca considers all \texttt{$2^N - 1$} potential subsets (for $N$ input time series).
+Seneca considers all \texttt{$2^N - 1$} non-emtpy potential subsets (for $N$ input time series).
 For this application, the default parameterization is the 
@@
 Each then uses this model to predict the field from which each fruit originates for the remaining 20\%.
-To study the impact of random data split, we consider multiple 80\%/20\% splits in our evaluation.
+To study the impact of random data split, we consider multiple (30 in our experiments) 80\%/20\% splits in our evaluation.
 \subsection{Empirical Methodology}
@@
 We do not consider the cost of dataset storage 
-in our cost computations (it is very small).
+in our cost computations (it is very small, under X cents).
 %\footnote{\url{https://aws.amazon.com/cloudwatch/}}
@@
 respectively, for the datasets and training methodologies that we consider.
-Verses the worst case, Seneca reduces MSE by 82.62\%, 78.01\%, and 99.28\%, respectively.
+Compared to the worst case, Seneca reduces MSE by 82.62\%, 78.01\%, and 99.28\%, respectively.
 
@@
 each when we consider different 80/20 random splits.
-To enable this, we run Seneca 30 times to obtain execution time, memory use, 
+For that purpose, we run Seneca 30 times to obtain execution time, memory use, 
 and best accuracy score. We report the

### 2019-03-01 results.tex
mz - michael pass

@@
 Each then uses this model to predict the field from which each fruit originates for the remaining 20\%.
-To study the impact of random data split, we consider multiple (30 in our experiments) 80\%/20\% splits in our evaluation.
+To study the impact of random data split, we consider multiple 80\%/20\% splits in our evaluation.
 \subsection{Empirical Methodology}
@@
 We do not consider the cost of dataset storage 
-in our cost computations (it is very small, under X cents).
+in our cost computations, because it is very small. For XGBoost that makes most S3 requests among others, the cost is under 2.5 cents for storage and request combined in a month.
 %\footnote{\url{https://aws.amazon.com/cloudwatch/}}

### 2019-03-01 Seneca.tex
mz - michael pass
Rich makes a pass

@@
 arguments.  Users can specify the train/test split ratio that should
-be used by Seneca; the default is 80\%/20\%.  The function returns a
+be used by Seneca; the default is 80\%/20\% for classification tasks.  The function returns a
 testing score.  Upon completion of this process, the container deploys
@@
 datasets on which the 
-resulting model will be used.  In addition, we use prediction error as the 
-score (i.e., mean squared error for regression and accuracy percentage for classification) 
-instead of $R^2$, which describes explanatory power, to avoid overfitting.
+resulting model will be used.  
+%In addition, we use prediction error as the 
+%score (i.e., mean squared error for regression and accuracy percentage for classification) 
+%instead of $R^2$, which describes explanatory power, to avoid overfitting.
 As part of future work, we are considering using multiple datasets and a ranges

### 2019-03-01 intro.tex
Rich makes a pass

@@
 prediction accuracy (as opposed to explanatory power) as the
-scoring metric (mean squared error for regression 
-and accuracy percentage for classification), to avoid overfitting.
+scoring metric (mean squared prediction error for regression 
+and accuracy percentage for classification).
 Users present Seneca with their application, a range of values for 
@@
 cost
-by 10-35\%. Relative to execution in AWS EC2, Seneca enables average speedups of 294x for each additional dollar 
-spent for the applications and datasets we consider.
+by 10-35\%. Relative to execution in AWS EC2, we observe a benefit/cost
+ratio (computed as speedup/(dollar cost) cost of 294 on the average
+in the experiments we consider.
 We intend to make Seneca, its applications, and their datasets publicly available

### 2019-03-01 results.tex
Rich makes a pass

@@
 \label{tab:bmarks}}
-\vspace{-0.1in}
+\vspace{-0.2in}
 \end{table}
@@
 
-To evaluate Seneca, we measure model output quality, execution time, memory use, and monetary cost.
-For output quality (prediction accuracy) our metrics are mean squared error (MSE) for regression and percentage accuracy for classification as described above.
-We score model prediction accuracy and not explanatory power ($R^2$) to avoid overfitting.
+To evaluate Seneca, we measure model output quality, execution time, memory
+use, and monetary cost.  For output quality (prediction accuracy) our metrics
+are mean squared prediction error (MSE) for regression and percentage accuracy for
+classification as described above. 
+%We score model prediction accuracy and not
+%explanatory power ($R^2$) to avoid overfitting.
 
@@
 \includegraphics[scale=0.36]{box_plot_mse}
+\vspace{-0.4in}
 \caption{Box plot of MSE from the three regression applications across the 
@@
 \label{fig:box_plot_mse}}
-\vspace{-0.2in}
+\vspace{-0.1in}
 \end{figure}
@@
 The last three rows show the MSE for the default, worst, and best performing (Seneca's recommendation)
-hyperparameter configuation (lower is better).
+hyperparameter configuration (lower is better).
 Seneca reduces MSE by 22.56\%, 15.94\%, and 44.88\%, for Prophet, Multi-Regression, and XGBoost,
@@
 \begin{figure}[t] \centering 
-\vspace{-0.1in}
+\vspace{-0.3in}
 \includegraphics[scale=0.36]{box_plot_Accuracy_20}
@@
 \label{fig:box_plot_accuracy}}
-\vspace{-0.2in}
+\vspace{-0.1in}
 \end{figure}
@@
 \input{tables/yield-tab-corrected.tex}
-\caption{Seneca VS EC2 cost analysis. Execution time (mins) and cost (cents) for
+\caption{Seneca VS EC2 cost analysis. Execution time (mins) and cost (dollars) for
 executing the applications serially in EC2 (t2.medium).  
@@
 
-Finally, we compare the cost of Seneca to AWS Elastic Compute Cloud (EC2) use. 
+Finally, we compare the cost of Seneca to the cost of using AWS Elastic Compute Cloud (EC2). 
 We measure the execution time of Seneca using the
@@
 Note that EC2 instances are charged for by the hour; Lambda charges 
-are only imposed when functions execute. We execute the applications serially
-using the instance.  For this setting, Seneca enables a speedup over EC2 
-of 3.72x -- 12.38x (6.51x on average). Doing so, however, imposes an additional 
-cost of \$0.01--\$0.15 over EC2 for all but SVC. 
-Seneca costs \$0.03 less than EC2 for SVC (because SVC runs in significantly less than
-the next hour boundary).
+are only imposed when functions execute, but Lambda \textit{may} execute
+the functions concurrently. 
+For this comparison, Seneca (because Lambda's automatic exploitation of
+concurrency) enables a speedup over EC2 (where we execute the parameter sweep
+sequentially) 
+of 3.72x -- 12.38x (6.51x on average). This speedup comes at an additional 
+cost of \$0.01--\$0.15 over EC2 for all but SVC (which executes for
+significantly less than an hour). 
+%Seneca costs \$0.03 less than EC2 for SVC (because SVC runs in significantly less than
+%the next hour boundary).
 
@@
 For applications for which Seneca is cheaper (e.g. SVC), we report \texttt{yield} 
-as $0.00$.  This metric reveals the amount of speed up that Senence can achieve 
-for each additional dollar spent.  To understand the yield if we were to 
-parallelize the EC2 deployment (perhaps a more ``fair'' comparison), 
-we also estimate yield for perfect parallelism (2x in our case for 
-the t2.medium).
+as $0.00$ since there is no positive benefit/cost ratio.  This metric captures
+the amount of speed up that Seneca can achieve 
+for each additional dollar spent.  To make the comparison ``fair''
+we also explore yield for theoretically perfect parallelism in EC2 using 2
+cores (e.g. in a t2.medium).
 
 We present results for this yield metric in Table~\ref{tab:yield} for each of the applications.
-Rows 1 and 2 show the average execution time (in minutes) and cost (in cents) 
+Rows 1 and 2 show the average execution time (in minutes) and cost (in dollars) 
 from using EC2 for each.
@@
 of 294x on average, for each additional dollar spent for these applications.
-We plan to compare Seneca cost and performance 
-to other EC2 instances and the AWS Elastic Container Service
+It is tempting to attribute this effect to the EC2 full-hour charge for short
+running applications, but XGBoost runs for almost 6 hours and the yield is
+still 41.86 assuming best-case EC2 execution.  We plan to study this
+benefit/cost ratio for Seneca and Lambda applications 
 as part of future work.

### 2019-03-01 results.tex
mz - spell check

@@
 Hyperparameter configuration for Multi-Regression is a subset of input SBC time series.
-Seneca considers all \texttt{$2^N - 1$} non-emtpy potential subsets (for $N$ input time series).
+Seneca considers all \texttt{$2^N - 1$} non-empty potential subsets (for $N$ input time series).
 For this application, the default parameterization is the 
@@
 We do not consider the cost of dataset storage 
-in our cost computations, because it is very small. For XGBoost that makes most S3 requests among others, the cost is under 2.5 cents for storage and request combined in a month.
+in our cost computations, because it is very small. For XGBoost that makes most S3 requests among others, the cost is less than 2.5 cents for storage and request combined in a month.
 %\footnote{\url{https://aws.amazon.com/cloudwatch/}}
@@
 hyperparameter configurations to complete successfully.  We have also verified
-that the memory requirements across hyperparemeter settings do not vary 
+that the memory requirements across hyperparameter settings do not vary 
 significantly. We plan to consider applications for which hyperparameter settings require
@@
 execution environment (number of CPUs, Linux container overhead, 
-multitenency, etc.).  We omit this data due to space constraints but analyze it here.
+multitenancy, etc.).  We omit this data due to space constraints but analyze it here.
 The average absolute difference in cost
